### 2016-12-12 Literature/paper_summary.tex
Introductory steps to start with the project.

Huggett (1993)

Central question of the paper: Why has the average real risk-free interest rate been less than one percent? 
	Previous papers fail to explain this as they tend to predict a to high risk-free rate and an equity premium that is too small (i.e. the work of Mehra and Prescott(1985))

How to solve the above issue?
	Including market imperfections, i.e. idiosyncratic shocks and incomplete insurance.

A first simple explanation:
	" With a credit limit, agents are restricted in the level of their indebtedness. However, agents are not restricted from accumulating large balances. A low risk-free rate is needed to persuade agents not to accumulate large credit balances so that the credit market can clear."

The model:
	Each agent wants to smooth consumption by holding a single asset, which can be interpreted as a credt balance with a central credit authority or as a one-period-ahead sure claim on consumption goods.

	The period budget constraint
		c + a'q ≤ a + e where c ≥ 0 and a' ≥ a_  (note: a_ is the credit limit)

	The probability measure used to describe the heterogeneity as well as the price, depending on the aggregates of the economy, remain unchanged in this setting, since the question concerns the average interest rate and not the dynamic properties of interest rates. 
		The reason for focusing on a stationary equilibrium is that general methods for characterizing equilibria of the more general kind do not exist at this time -> russel&smith?
	See Lucas (1980) for more info on stationary recursive equilibrium structure

	Definition of a stationary equilibrium for this economy is (c(x), a(x), q, psi) satisfying
		(1) c(x) and a(x) are optimal decision rules, given q.
			agents optimize
		(2) Markets clear: (i) integral s c(x)dpsi =... see paper 
			consumption and endowment averaged over the population are equal and that credit balances averaged over the population are zero
		(3) psi is a stationary probability measure: psi(B) = ... see paper 
			the distribution of agents over states is unchanging

Aiyagari (1994)

General remarks of concerning this type of models:

Special feature of models whose aggregate behavior is the result of market interaction among a large number of agents subject to idiosyncratic shocks is, that the individual dynamics, uncertainty, and asset trading  are the main mechanism by which individuals attempt to smooth consumption, while aggregate variables are unchanging. 
	-> as opposed to representative agent models (complete market models) in which individual dynamics and uncertainty coincide with aggregate dynamics and uncertainty!

The model include a role for uninsured idiosyncratic risk and liquidity/borrowing constraints
	-> this is modeled by having a large number of agents who receive idiosyncratic labor endowment shocks that are uninsured
		-> the result of the market incompleteness in combination with the possibility of being borrowing constrained in future periods, agents accumulate excess capital in order to smooth consumption in the face of uncertain individual labor incomes.

The study of the paper:

The broader context of this paper is the debate concerning the sources of aggregate capital accumulation, in particular the suggestion that precautionary saving may be a quantitatively important component of aggregate saving.

Results: 
- the quantitative results of this paper suggest that the contribution of uninsured idiosyncratic risk to aggregate saving is quite modest, at least for moderate and empirically plausible values of risk aversion, variability, and persistence in earnings. (ASK MARKUS)
- the distributions are positively skewed, wealth distribution is much more disperse than the income distribution, and inequality as measured by the Gini coefficient is significantly higher for wealth than for income

- further they show as Hugget (1993) that in equilibrium the interest rate will be lower with uninsured risk and average household assets are extremely sensitive to slight variations in the interest rate when it is close to (but below) the rate of time preference (this makes a case for general equilibrium, r is determined endogenously, vs partial equilibrium analysis)

For the interpretation

Steady State: 
- consumers face a constant interest rate as shocks are purely idiosyncratic ->> no aggregate uncertainty 
- the per capita amount of capital must equal the per capita asset holdings of consumers
- interest rate must equal the net marginal product of capital (as determined by a standard neoclassical production function)

the consequence of the three points above:
	- explain why the interest rate is necessarily less than the time preference rate (the agent wants to borrow) and, hence, the aggregate capital stock and the saving rate are necessarily greater than under certainty (complete markets) 
	-> as seen in hinermaiers course time preference rate = interest rate in equilibrium (elaborate)
	- as a consequence the per capita capital is higher than the modified golden rule capital (hintermaier)

Evidence backing up the model
- individual consumptions are much more variable than aggregate consumption
- individual wealth holdings appear to be highly volatile
- risky portfolios held by top end of the wealth distribution and risk free portfolios held predominantly by lower end of wealth distribution

The model

Borrowing constraint
- if r < 0 some limit on borrowing is required 
	-> otherwise a max does not exist i.e. the PV of earnings is infinite and individual can run a Ponzi scheme
- if r > 0 a less restrictive alternative to imposing a borrowing limit is to impose present value budget balance  -> lim at/(1+r)^t ≥ 0 
	together with nonnegativity of consumption -> period-by-period borrowing constraint at ≥ -w*lmin/r
	hence, the nonnegativity of consumption automatically imposes a borrowing constraint 
Further explanation in paper on page 9!

- note that r < lambda (rate of time preference)
	-> agent would like to borrow but is limited by the borrowing limit
		-> as total resources get smaller and smaller, the individual borrows more and more in order to maintain current consumption, and his debt approaches the borrowing limit. at some point when total resources are too low, it would be optimal to borrow up to the limit and consumpe all of the total resources.

Effects of varying the borrowing limit b
- when r equals zero, b is not an argument of the asset demand function A(.), hence Eaw decreases one-to-one with increases in b when r is zero (under the above definition, when lm is 0)
	Eaw curve shifts to the left when b increases permitting a higher bottowing limit serves to lower aggregate capital and raise the interest rate toward the time preference rate. 
	-> intutively, when borrowing is permitted individuals need not rely solely on holdings of capital to buffer earnings variation. borrowing can also be used to buffer these shocks and, hence, leads to smaller holdings of capital.
- case where lm > 0, Eaw will tend to (-infinity) as r tends to zero
	itutively, as r becomes smaller, the borrowing limit becomes larger, permitting the individual to carry large amounts of debt. 
	(the main difference between this case and the case of a fixed borrowing limit is that under the present value borrowing constraint there always exists a steady state with a positive interest rate. with a fixed borrowing limit there may be no steady state with a positive interest rate though there does exist a steady state with a negative interest rate)

Alternative Interpretations of the model
- the model of individual optimization can be turned into a pure exchange model with government debt in order to analyze the effects of changing the level of government debt
- the model of individual optimization can also be turned into an "optimum quantity of moeny" model

Model specification
- calibrated to be consistent with features of postwar U.S. economy
- the authors test for three different risk aversion parameters: (1,3,5)
- labor endowmnet shock, Markvo chain specification with seven states to match a first-order autoregressive representation for the logarithm of labor endowment shock
	use tauchen
	for the calibration of the values of the coefficient of variation and the serial correlation coefficient refer to paper page 18-19
	(- they do not allow for the possibility that the reported earnings variabilities contain significant measurement error -> might be an issue)

- they set the borrowing limit b to zero

Computation (just some remarks)
- use bisection method
(- for more info refer to paper)

Results 
- calculate full insurance net return to capital and saving rate refer to page 21 for maths
	- fulor high values of sigma, rho and mu the presence of idiosyncratic risk can raise the saving rate quite significantly by up to seven percentage points (only small difference for small values), in the extreme case up to 14%
- some studies use earnings processes that are difference stationry instead of trend stationary (see page 22 for approx and references)

Variabilities
- show the differences of variables of hh
	-> consumption varies less than income 
	-> savings and assets are much more volatile than income  
- used to show the importance of asset trading

Cross-Section Distributions and Inequality measures
- as long-run distributions for an individual coincide with cross-section distributions for the population, results for variabilities of individual consumption, income, and assets have immediate implications for cross-section distributions. 
- much less dispersion across households in comsumption compared with income and much greater dispersion in wealth compared with income 
- the model generates empirically plausible relative degrees of inequality, but cannot generate the observed degrees of inequality

Krusell, Muko & Sahin (2010)
-> see page 13 for some notes on calculating welfare changes in the Aiyagari-model

### 2016-12-12 main.m

@@ -100,7 +100,7 @@ while d1>1e-6 && iter<50 % loop for aggregate problem
         sim_shock = rand(T,ind_no); % shocks for employment transition
 
         sim_e(1,1:round(L*ind_no))=2; % initial individuals that are employed
-        sim_k(1,:) = K_guess; % initial capital holdings
+        sim_k(1,:) = K_guess; % initial capital holdings, (take equilibrium capital holdings as initial capital holdings) 
 
         for t=2:T
             sim_e(t,sim_e(t-1,:)==1) = 1+(sim_shock(t,sim_e(t-1,:)==1)<=PI(1,2)); % new employment status of previously unemployed

### 2016-12-12 parameters.m

@@ -3,9 +3,9 @@
 beta = 0.99; % discount factor
 sigma = 2; % risk aversion
 mu = 0.3; % replacement rate of unemployed
-k_min = 0.5; % borrowing constraint as share of capital stock
-ind_no = 5000; % number of individuals simulated
-T = 5000; % number of periods simulated
+k_min =  0; % borrowing constraint as share of capital stock
+ind_no = 100; % number of individuals simulated
+T = 100; % number of periods simulated
 
 % firms (production function F(K,L)=z*K^alpha*L^(1-alpha)
 delta = 0.025; % depreciation rate
@@ -14,7 +14,7 @@ z = 1; % productivity
 
 % transition probabilities
 L_target = 0.9;
-PI_UE = 0.3; % chance of getting employed
+PI_UE = 0.1; % chance of getting employed
 PI_EU = PI_UE*(1-L_target)/L_target; % chance of getting unemployed
 
 

### 2016-12-12 aiyagari_solver.m
Finish welfare effects for parameter change

@@ -1,4 +1,4 @@
-function [ k, c, K, sim, store] = aiyagari_solver( par, grid, K, k, func, method, mat )
+function [ k, c, K, sim, store] = aiyagari_solver( par, func, method)
 % AIYAGARI MODEL: Heterogeneous agents model due to idiosyncratic labour
 % shocks. Agents self-sinsure against unemploment by building capital
 % stock.
@@ -14,6 +14,29 @@ function [ k, c, K, sim, store] = aiyagari_solver( par, grid, K, k, func, method
 %   mat = Grid and income for unemployed and employed in one matrice each.
 % 
 % Output variables:
+
+% define grid for individual capital on which to solve
+K.rep = func.K(1/par.beta-1+par.delta);% capital stock of representative agent useful for comparison
+
+grid.k_no = 100; % number of grid points for agents' capital holdings
+grid.k = linspace(par.k_min*K.rep,3*K.rep,grid.k_no); % grid for agents' policy function
+
+grid.dist_no = 1000;
+grid.dist = linspace(grid.k(1),grid.k(end),grid.dist_no); % grid for distribution of agents - use finer grid
+
+% useful matrices
+mat.k = [grid.k',grid.k']; % replicate grid for unemployed and employed
+mat.income = @(K) func.w(K)*repmat([par.mu,1-par.tau],grid.k_no,1); % matrix with income of each agent
+
+K.lims = [K.rep,grid.k(end)]; % initial limits for bisection method
+
+% initial guesses
+k.guess = mat.k; % policy function of agents (1st column unemployed, 2nd column employed)
+if strcmp(method.agg,'bisection')
+    K.guess = (K.lims(1)+K.lims(2))/2;
+else
+    K.guess = K.rep; % aggregate capital stock
+end
 
 d1 = 1;
 iter = 0;

### 2016-12-12 main.m

@@ -2,11 +2,8 @@ clear
 close all
 
 parameters % load paramaters
-method.sim = 'simulation'
-tic % Set timer
-% Solve the Aiyagariy model by fixed-point iteration.
-% Function in- and output are structures.
-[k, c, K, sim, store]= aiyagari_solver(par, grid, K, k, func, method, mat);
+setup % load setup
+%method.sim = 'simulation'
+tic
+[k, c, K, sim, store]= aiyagari_solver(par, func, method);
 toc
-
-[c] = welfare_effects(par, func, sim, store, K, k, method);

### 2016-12-12 parameters.m

@@ -1,6 +1,3 @@
-% clear 
-% close all
-
 %% set parameters
 % consumers
 par.beta = 0.99; % discount factor
@@ -16,48 +13,11 @@ par.z = 1; % productivity
 % transition probabilities
 par.L_target = 0.9;
 par.PI_UE = 0.3; % chance of getting employed
-par.PI_EU = par.PI_UE*(1-par.L_target)/par.L_target; % chance of getting unemployed
 
 
-%% setup
-% build transition matrix of agents
-par.PI = [1-par.PI_UE,par.PI_UE;par.PI_EU,1-par.PI_EU]; % [UU,UE;EU;EE]
-par.L = par.PI(1,2)/(par.PI(1,2)+par.PI(2,1)); % calculate steady state supply of labour
-par.tau = par.mu*(1-par.L)/par.L; % tax rate
 
-% define some useful functions
-func.muc = @(c) c.^(-par.sigma); % marginal utility of consumption
-func.muc_inv = @(muc) muc.^(-1/par.sigma); % inverse of marginal utility of consumption
-func.w = @(K) par.z*(1-par.alpha)*K.^par.alpha*par.L^(-par.alpha); % wage
-func.r = @(K) par.z*par.alpha*K.^(par.alpha-1)*par.L^(1-par.alpha); % rental rate of capital
-func.K = @(r) par.L*(par.z*par.alpha/r).^(1/(1-par.alpha)); % capital stock necessary to yield return r
-func.Y = @(K) par.z*K.^par.alpha*par.L^(1-par.alpha); % output
-func.C = @(K) func.Y(K)-par.delta*K; % consumption
-
-% define grid for individual capital on which to solve
-K.rep = func.K(1/par.beta-1+par.delta);% capital stock of representative agent useful for comparison
-
-grid.k_no = 100; % number of grid points for agents' capital holdings
-grid.k = linspace(par.k_min*K.rep,3*K.rep,grid.k_no); % grid for agents' policy function
-
-grid.dist_no = 1000;
-grid.dist = linspace(grid.k(1),grid.k(end),grid.dist_no); % grid for distribution of agents - use finer grid
-
-% useful matrices
-mat.k = [grid.k',grid.k']; % replicate grid for unemployed and employed
-mat.income = @(K) func.w(K)*repmat([par.mu,1-par.tau],grid.k_no,1); % matrix with income of each agent
 
 %% solve for general equilibrium
[…]

### 2016-12-12 setup.m

@@ -1,0 +1,16 @@
+%% setup
+par.PI_EU = par.PI_UE*(1-par.L_target)/par.L_target; % chance of getting unemployed
+
+% build transition matrix of agents
+par.PI = [1-par.PI_UE,par.PI_UE;par.PI_EU,1-par.PI_EU]; % [UU,UE;EU;EE]
+par.L = par.PI(1,2)/(par.PI(1,2)+par.PI(2,1)); % calculate steady state supply of labour
+par.tau = par.mu*(1-par.L)/par.L; % tax rate
+
+% define some useful functions
+func.muc = @(c) c.^(-par.sigma); % marginal utility of consumption
+func.muc_inv = @(muc) muc.^(-1/par.sigma); % inverse of marginal utility of consumption
+func.w = @(K) par.z*(1-par.alpha)*K.^par.alpha*par.L^(-par.alpha); % wage
+func.r = @(K) par.z*par.alpha*K.^(par.alpha-1)*par.L^(1-par.alpha); % rental rate of capital
+func.K = @(r) par.L*(par.z*par.alpha/r).^(1/(1-par.alpha)); % capital stock necessary to yield return r
+func.Y = @(K) par.z*K.^par.alpha*par.L^(1-par.alpha); % output
+func.C = @(K) func.Y(K)-par.delta*K; % consumption

### 2016-12-12 welfare.m

@@ -2,7 +2,35 @@ clear
 close all
 
 parameters % load paramaters
-method.sim = 'simulation'
+setup % load setup
+% Define function to calculate utility of consumption.
+func.U = @(c) (c.^(1-par.sigma))./(1-par.sigma);
+% method.sim = 'simulation';
+% 
+% tic % Set timer
+% % Solve the Aiyagariy model by fixed-point iteration.
+% % Function in- and output are structures.
+% [k, c, K, sim, store]= aiyagari_solver(par, func, method);
+% toc
+% 
+% % Compare welfare against frictionless model
+% [c, U] = welfare_effects_rep(par, func, sim, store, K, k, method);
+
+%% Welfare effects of two Aiyagari models with different parameters.
+set(0,'DefaultFigureVisible','off'); % Do not display figures when we run the loop
 tic
-[k, c, K, sim, store]= aiyagari_solver(par, grid, K, k, func, method, mat);
+for i=1:2 % Get steady state values for the model with two different parameters
+    if i==1 
+        % e.g. par.k_min = 0.5;
+        [k.one, c.one, K.one, sim.one, store.one]= aiyagari_solver(par, func, method);
+    elseif i==2
+        % and here par.k_min = 0.25;
+        par.z = 0.5;
+        setup % load setup again for new parameter
+        [k.two, c.two, K.two, sim.two, store.two]= aiyagari_solver(par, func, method); % start with s.s. values from first run to speed up convergence
+    end
+end
 toc
+%set(0,'DefaultFigureVisible','on'); % Turn graphical display on again
+
+[c, U] = welfare_effects(par, func, sim, store, K, k, method);

### 2016-12-12 welfare_effects.m

@@ -1,54 +1,47 @@
-function [ c ] = welfare_effects( par, func, sim, store, K, k, method )
+function [ c, U ] = welfare_effects( par, func, sim, store, K, k, method )
 %WELFARE EFFECTS Calculates whether agents prefer a policy change or not
 %   Detailed explanation goes here
-
-    % Define function to calculate utility of consumption.
-    func.U = @(c) (c.^(1-par.sigma))./(1-par.sigma);
 
     if strcmp(method.sim ,'simulation')
 
         ind_no = size(sim.k,2);
         
         % Get utility levels of all agents at all points in time.
-        sim.u = func.U(func.C(sim.k));
-        sim.u(func.C(sim.k)<0) = -Inf; % Make sure consumtion is always positive.
+        sim.one.u = func.U(func.C(sim.one.k));
+        sim.one.u(func.C(sim.one.k)<0) = -Inf; % Make sure consumption is always positive.
+        sim.two.u = func.U(func.C(sim.two.k));
+        sim.two.u(func.C(sim.two.k)<0) = -Inf;
         % Calculate the life time utility when simulation has converged (about half
         % the size of the simulation).
-        lifetime_U = par.beta.^(1:ceil(ind_no/2))*sim.u((ceil(ind_no/2)+1):end,:);
-        lifetime_U_rep = sum(par.beta.^(1:ceil(ind_no/2))*func.U(func.C(K.rep)));
+        U.lifetime_one = par.beta.^(1:ceil(ind_no/2))*sim.one.u((ceil(ind_no/2)+1):end,:);
+        U.lifetime_two = par.beta.^(1:ceil(ind_no/2))*sim.two.u((ceil(ind_no/2)+1):end,:);
 
         %% Calculate the consumption equivalent
-        % If value>1, agents prefer old steady state, if 1>value>0, agents prefer
-        % policy change.
-        % Consumption equivalent tested against frictionless benchmark model.
-        c.equivalent_bench = ((lifetime_U.*(1-par.sigma).*(1-par.beta)+1)...
-            ./(lifetime_U_rep*(1-par.sigma)*(1-par.beta)+1)).^(1/(1-par.sigma)); 
+        % If value > 1, agents prefer steady state one, if 1 > value > 0, agents prefer
+        % policy change ( = steady state two).
+        % Consumption equivalent tested against model with policy change.
+        c.equivalent = ((U.lifetime.two*(1-par.sigma).*(1-par.beta)+1)...
[…]

### 2016-12-12 welfare_effects_rep.m

@@ -1,0 +1,48 @@
+function [ c, U ] = welfare_effects_rep( par, func, sim, store, K, k, method )
+%WELFARE EFFECTS REP Calculates whether agents prefer a frictionless, representative agent model or not
+%   Detailed explanation goes here
+
+    if strcmp(method.sim ,'simulation')
+
+        ind_no = size(sim.k,2);
+     
+        % Calculate the life time utility when simulation has converged (about half
+        % the size of the simulation).
+        U.lifetime = par.beta.^(1:ceil(ind_no/2))*func.U(func.C(sim.k((ceil(ind_no/2)+1):end,:)));
+        U.lifetime_rep = sum(par.beta.^(1:ceil(ind_no/2))*func.U(func.C(K.rep)));
+
+        %% Calculate the consumption equivalent
+        % If value > 1, agents prefer standard model, if 1 > value > 0, agents prefer
+        % Aiyagari model.
+        % Consumption equivalent tested against frictionless benchmark model.
+        c.equivalent_bench = ((U.lifetime_rep.*(1-par.sigma).*(1-par.beta)+1)...
+            ./(U.lifetime.*(1-par.sigma).*(1-par.beta)+1)).^(1/(1-par.sigma)); 
+        figure(6)
+        histogram(c.equivalent_bench)
+        xlabel('Consumption equivalents')
+        % Calculate average and median of consumption equivalent. If this aggregate
+        % >1, there exists a (lump-sum) redistribution which would make everyone
+        % better off.
+        c.equivalent_bench_mean = mean(c.equivalent_bench);
+        c.equivalent_bench_median = median(c.equivalent_bench);
+        
+        % Just to see how consumption looks overall
+        a = func.C(sim.k((ceil(ind_no/2)+1):end,:));
+        figure(7)
+        histogram(a(:),100)
+        
+
+    elseif strcmp(method.sim , 'histogram')
+        
+        U.lifetime = sum(sum(store.distribution.*func.U(func.C(k.k)))); % Aggregate utility
+        U.lifetime_rep = func.U(func.C(K.rep));
+
+        %% Calculate the consumption equivalent
+        % If value > 1, agents prefer standard model, if 1 > value > 0, agents prefer
+        % Aiyagari model.
+        % Consumption equivalent tested against frictionless benchmark model.
[…]

### 2016-12-12 setup.m
Setup in welfare effects has to be the same as for s.s.

@@ -14,3 +14,4 @@ func.r = @(K) par.z*par.alpha*K.^(par.alpha-1)*par.L^(1-par.alpha); % rental rat
 func.K = @(r) par.L*(par.z*par.alpha/r).^(1/(1-par.alpha)); % capital stock necessary to yield return r
 func.Y = @(K) par.z*K.^par.alpha*par.L^(1-par.alpha); % output
 func.C = @(K) func.Y(K)-par.delta*K; % consumption
+func.U = @(c) (c.^(1-par.sigma))./(1-par.sigma); % Utility

### 2016-12-12 welfare.m

@@ -3,9 +3,8 @@ close all
 
 parameters % load paramaters
 setup % load setup
-% Define function to calculate utility of consumption.
-func.U = @(c) (c.^(1-par.sigma))./(1-par.sigma);
-% method.sim = 'simulation';
+
+method.sim = 'simulation';
 % 
 % tic % Set timer
 % % Solve the Aiyagariy model by fixed-point iteration.
@@ -22,15 +21,15 @@ tic
 for i=1:2 % Get steady state values for the model with two different parameters
     if i==1 
         % e.g. par.k_min = 0.5;
-        [k.one, c.one, K.one, sim.one, store.one]= aiyagari_solver(par, func, method);
+        [k.one, c.one, ~, sim.one, store.one]= aiyagari_solver(par, func, method);
     elseif i==2
         % and here par.k_min = 0.25;
         par.z = 0.5;
-        setup % load setup again for new parameter
-        [k.two, c.two, K.two, sim.two, store.two]= aiyagari_solver(par, func, method); % start with s.s. values from first run to speed up convergence
+        setup % refresh setup again for new parameter
+        [k.two, c.two, ~, sim.two, store.two]= aiyagari_solver(par, func, method); % start with s.s. values from first run to speed up convergence
     end
 end
 toc
 %set(0,'DefaultFigureVisible','on'); % Turn graphical display on again
 
-[c, U] = welfare_effects(par, func, sim, store, K, k, method);
+[c, U] = welfare_effects(sim, store, k, method);

### 2016-12-12 welfare_effects.m

@@ -1,14 +1,25 @@
-function [ c, U ] = welfare_effects( par, func, sim, store, K, k, method )
+function [ c, U ] = welfare_effects( sim, store, k, method )
 %WELFARE EFFECTS Calculates whether agents prefer a policy change or not
 %   Detailed explanation goes here
+    
+    % Load parametes again and refresh setup. Remember that the handle
+    % functions need the same setup as when their respective s.s. was
+    % calculated.
+    parameters % load parameters
+    method.sim = 'simulation';
+    setup % load setup
 
     if strcmp(method.sim ,'simulation')
 
-        ind_no = size(sim.k,2);
+        ind_no = size(sim.one.k,2);
         
         % Get utility levels of all agents at all points in time.
+        % Setup the parameters and handle functions as when s.s. was
+        % calculated
         sim.one.u = func.U(func.C(sim.one.k));
         sim.one.u(func.C(sim.one.k)<0) = -Inf; % Make sure consumption is always positive.
+        par.z = 0.5;
+        setup
         sim.two.u = func.U(func.C(sim.two.k));
         sim.two.u(func.C(sim.two.k)<0) = -Inf;
         % Calculate the life time utility when simulation has converged (about half
@@ -20,20 +31,20 @@ function [ c, U ] = welfare_effects( par, func, sim, store, K, k, method )
         % If value > 1, agents prefer steady state one, if 1 > value > 0, agents prefer
         % policy change ( = steady state two).
         % Consumption equivalent tested against model with policy change.
-        c.equivalent = ((U.lifetime.two*(1-par.sigma).*(1-par.beta)+1)...
-            ./(U.lifetime_one*(1-par.sigma)*(1-par.beta)+1)).^(1/(1-par.sigma)); 
-        figure(6)
-        histogram(c.equivalent)
-        xlabel('Consumption equivalents')
+        c.equivalent_mean = ((mean(U.lifetime_two).*(1-par.sigma).*(1-par.beta)+1)...
+            ./(mean(U.lifetime_one).*(1-par.sigma).*(1-par.beta)+1)).^(1/(1-par.sigma));
+        
+        c.equivalent_median = ((median(U.lifetime_two).*(1-par.sigma).*(1-par.beta)+1)...
+            ./(median(U.lifetime_one).*(1-par.sigma).*(1-par.beta)+1)).^(1/(1-par.sigma)); 
         % Calculate average and median of consumption equivalent. If this aggregate
[…]

### 2016-12-13 aiyagari_solver.m
Implemented plotting function.

@@ -77,13 +77,13 @@ while d1>1e-6 && iter<50 % loop for aggregate problem
         % update policy function
         k.guess = k.guess + 0.5*(k.new-k.guess);
     end
-    figure(1)
-    plot(grid.k,log(k.guess./[grid.k',grid.k']))
-    line([grid.k(1),grid.k(end)],[0,0])
-    legend('unemployed','employed')
-    xlabel('capital this period')
-    ylabel('log(capital next period/capital this period)')
-    title('policy functions')
+%     figure(1)
+%     plot(grid.k,log(k.guess./[grid.k',grid.k']))
+%     line([grid.k(1),grid.k(end)],[0,0])
+%     legend('unemployed','employed')
+%     xlabel('capital this period')
+%     ylabel('log(capital next period/capital this period)')
+%     title('policy functions')
     
     
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@ -180,24 +180,24 @@ disp(['Output:      ',num2str(func.Y(K.guess)),' (',num2str(log(func.Y(K.guess)/
 disp(['Consumption: ',num2str(func.C(K.guess)),' (',num2str(log(func.C(K.guess)/func.C(K.rep))),')'])
 
 
-% Plot convergence of aggregate capital stock
-figure(2)
-plot([store.K_guess;store.K_next]')
-legend('guess','demand')
-xlabel('iteration')
-ylabel('capital stock')
-
-% Plot distribution of agents
-figure(3)
-if strcmp(method.sim,'simulation')
-    temp = sim.k(ceil(T/2):end,:);
-    hist(temp(:),100)
-    legend('number of agents')
-elseif strcmp(method.sim,'histogram')
-    bar(grid.dist,store.distribution,'stacked')
-    legend('unemployed','employed')
-end
-xlabel('capital holdings')
+% % Plot convergence of aggregate capital stock
+% figure(2)
+% plot([store.K_guess;store.K_next]')
+% legend('guess','demand')
+% xlabel('iteration')
+% ylabel('capital stock')
+% 
+% % Plot distribution of agents
+% figure(3)
+% if strcmp(method.sim,'simulation')
+%     temp = sim.k(ceil(T/2):end,:);
+%     hist(temp(:),100)
+%     legend('number of agents')
+% elseif strcmp(method.sim,'histogram')
[…]

### 2016-12-13 parameters.m

@@ -3,10 +3,10 @@
 
 %% set parameters
 % consumers
-beta = 0.99; % discount factor
-sigma = 2; % risk aversion
-mu = 0.3; % replacement rate of unemployed
-k_min =  0; % borrowing constraint as share of capital stock
+par.beta = 0.99; % discount factor
+par.sigma = 2; % risk aversion
+par.mu = 0.3; % replacement rate of unemployed
+par.k_min = 0; % borrowing constraint as share of capital stock
 ind_no = 100; % number of individuals simulated
 T = 100; % number of periods simulated
 
@@ -16,15 +16,11 @@ par.alpha = 0.33; % output elasticity of capital
 par.z = 1; % productivity
 
 % transition probabilities
-<<<<<<< HEAD
-L_target = 0.9;
-PI_UE = 0.1; % chance of getting employed
-PI_EU = PI_UE*(1-L_target)/L_target; % chance of getting unemployed
-=======
+
 par.L_target = 0.9;
 par.PI_UE = 0.3; % chance of getting employed
 par.PI_EU = par.PI_UE*(1-par.L_target)/par.L_target; % chance of getting unemployed
->>>>>>> Yannic
+
 
 
 %% setup

### 2016-12-13 plotting_fct.m

@@ -1,0 +1,35 @@
+%% Analysis of parameters 
+clear 
+close 
+
+parameters % import parameters 
+method.sim = 'histogram' 
+%% Specify the parameter of interest
+% 'Borrowing Constraint' 
+% 'Unemployment insurance'
+% 'Chance to get employed'
+% etc...
+
+%study_parameter = 'Borrowing Constraint'
+
+k_min = [0,0.5,0.9];
+for i =1:3
+    par.k_min = k_min(i);
+% calling the problem solving function 
+    [k,c,K,sim,store]= aiyagari_solver(par, grid, K, k, func, method, mat); 
+
+% Plot distribution of agents
+
+    figure(1)
+    
+    subplot(1,3,i)
+    if strcmp(method.sim,'simulation')
+        temp = sim.k(ceil(T/2):end,:);
+        hist(temp(:),100)
+        legend('number of agents')
+    elseif strcmp(method.sim,'histogram')
+        bar(grid.dist,store.distribution,'stacked')
+        legend('unemployed','employed')
+    end
+
+end

### 2016-12-13 consumption_equivalent.m
Finish welfare analysis for two different parameterizations

@@ -1,0 +1,27 @@
+function [ c ] = consumption_equivalent( U, par, method )
+%WELFARE EFFECTS Summary of this function goes here
+%   Detailed explanation goes here
+    
+    if strcmp(method.sim ,'simulation')
+        % Calculate the consumption equivalent
+        % If value > 1, agents prefer steady state one, if 1 > value > 0, agents prefer
+        % policy change ( = steady state two).
+        % Consumption equivalent tested against model with policy change:
+        c.equivalent_mean = ((mean(U.two).*(1-par.sigma).*(1-par.beta)+1)...
+            ./(mean(U.one).*(1-par.sigma).*(1-par.beta)+1)).^(1/(1-par.sigma));
+
+        c.equivalent_median = ((median(U.two).*(1-par.sigma).*(1-par.beta)+1)...
+            ./(median(U.one).*(1-par.sigma).*(1-par.beta)+1)).^(1/(1-par.sigma)); 
+        % Calculate average and median of consumption equivalent. If this aggregate
+        % >1, there exists a (lump-sum) redistribution which would make everyone
+        % better off.
+    elseif strcmp(method.sim,'histogram')
+        % Calculate the consumption equivalent
+        % If value > 1, agents prefer policy change ( = steady state two), 
+        % if 1 > value > 0, agents prefer steady state one.
+        % Consumption equivalent tested against model with policy change:
+        c.equivalent = ((U.two.*(1-par.sigma).*(1-par.beta)+1)...
+            ./(U.one.*(1-par.sigma).*(1-par.beta)+1)).^(1/(1-par.sigma));
+    end
+end
+

### 2016-12-13 get_utility.m

@@ -1,0 +1,205 @@
+function [ U, c, k, K, sim, store ] = get_utility( par, func, method )
+%GET UTILITY Calculates the lifetime utility of agents in Aiyagari model
+%with this specific parameterization.
+%   Detailed explanation goes here
+    
+   % define grid for individual capital on which to solve
+   K.rep = func.K(1/par.beta-1+par.delta);% capital stock of representative agent useful for comparison
+
+   grid.k_no = 100; % number of grid points for agents' capital holdings
+   grid.k = linspace(par.k_min*K.rep,3*K.rep,grid.k_no); % grid for agents' policy function
+
+   grid.dist_no = 1000;
+   grid.dist = linspace(grid.k(1),grid.k(end),grid.dist_no); % grid for distribution of agents - use finer grid
+
+    % useful matrices
+    mat.k = [grid.k',grid.k']; % replicate grid for unemployed and employed
+    mat.income = @(K) func.w(K)*repmat([par.mu,1-par.tau],grid.k_no,1); % matrix with income of each agent
+
+    K.lims = [K.rep,grid.k(end)]; % initial limits for bisection method
+
+    % initial guesses
+    k.guess = mat.k; % policy function of agents (1st column unemployed, 2nd column employed)
+    if strcmp(method.agg,'bisection')
+        K.guess = (K.lims(1)+K.lims(2))/2;
+    else
+        K.guess = K.rep; % aggregate capital stock
+    end
+
+    d1 = 1;
+    iter = 0;
+    while d1>1e-6 && iter<50 % loop for aggregate problem
+        iter = iter+1;
+        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+        %%%%%    Solve household problem given prices
+        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+        d2 = 1;
+        while d2>1e-10 % loop for household problem
+
+            if strcmp(method.HH,'FP') % Fixed-point iteration     
+                % calculate capital chosen next period, depending on current and
+                % future employment status
+                for i=1:2 % employment this period
+                    for j=1:2 % employment next period
+                        % capital choice next period from policy function
+                        k.next(i,:,j) = interp1(grid.k,k.guess(:,j),k.guess(:,i),'linear','extrap'); 
+                    end
[…]

### 2016-12-13 setup.m

@@ -15,3 +15,6 @@ func.K = @(r) par.L*(par.z*par.alpha/r).^(1/(1-par.alpha)); % capital stock nece
 func.Y = @(K) par.z*K.^par.alpha*par.L^(1-par.alpha); % output
 func.C = @(K) func.Y(K)-par.delta*K; % consumption
 func.U = @(c) (c.^(1-par.sigma))./(1-par.sigma); % Utility
+
+%%
+   

### 2016-12-13 welfare.m

@@ -4,8 +4,12 @@ close all
 parameters % load paramaters
 setup % load setup
 
-method.sim = 'simulation';
-% 
+% Change simulation method to simulation if you want, it takes much longer
+% though.
+%method.sim = 'simulation';
+
+%% Welfare analysis against frictionless representative agent model
+
 % tic % Set timer
 % % Solve the Aiyagariy model by fixed-point iteration.
 % % Function in- and output are structures.
@@ -16,20 +20,26 @@ method.sim = 'simulation';
 % [c, U] = welfare_effects_rep(par, func, sim, store, K, k, method);
 
 %% Welfare effects of two Aiyagari models with different parameters.
-set(0,'DefaultFigureVisible','off'); % Do not display figures when we run the loop
+
+% Default parameterization is set by the calibration of Markus Riegler. If
+% you change parameters type "par.<parameter> =" and then "setup" before
+% you call the function. If you want to compare one steady state with the
+% default one, change parameters for i=2 and leave i=1 as the default one.
+% Do not change beta or sigma!
+
 tic
-for i=1:2 % Get steady state values for the model with two different parameters
+for i=1:2 % Get steady state utility for the model with two different parameters
     if i==1 
-        % e.g. par.k_min = 0.5;
-        [k.one, c.one, ~, sim.one, store.one]= aiyagari_solver(par, func, method);
+        [ U.one, c.one, k.one, K.one, sim.one, store.one ] = get_utility( par, func, method );
     elseif i==2
-        % and here par.k_min = 0.25;
         par.z = 0.5;
         setup % refresh setup again for new parameter
-        [k.two, c.two, ~, sim.two, store.two]= aiyagari_solver(par, func, method); % start with s.s. values from first run to speed up convergence
+        [ U.two, c.two, k.two, K.two, sim.two, store.two ] = get_utility( par, func, method );
     end
 end
 toc
-%set(0,'DefaultFigureVisible','on'); % Turn graphical display on again
 
-[c, U] = welfare_effects(sim, store, k, method);
+% Calculate the consumption equivalent for the two steady states. If c > 1,
+% agents prefer the second steady state. If 1 > c > 0, agents prefer the
+% first steady state.
+[ c ] = consumption_equivalent( U, par, method );

### 2016-12-13 welfare_effects.m

@@ -1,58 +1,0 @@
-function [ c, U ] = welfare_effects( sim, store, k, method )
-%WELFARE EFFECTS Calculates whether agents prefer a policy change or not
-%   Detailed explanation goes here
-    
-    % Load parametes again and refresh setup. Remember that the handle
-    % functions need the same setup as when their respective s.s. was
-    % calculated.
-    parameters % load parameters
-    method.sim = 'simulation';
-    setup % load setup
-
-    if strcmp(method.sim ,'simulation')
-
-        ind_no = size(sim.one.k,2);
-        
-        % Get utility levels of all agents at all points in time.
-        % Setup the parameters and handle functions as when s.s. was
-        % calculated
-        sim.one.u = func.U(func.C(sim.one.k));
-        sim.one.u(func.C(sim.one.k)<0) = -Inf; % Make sure consumption is always positive.
-        par.z = 0.5;
-        setup
-        sim.two.u = func.U(func.C(sim.two.k));
-        sim.two.u(func.C(sim.two.k)<0) = -Inf;
-        % Calculate the life time utility when simulation has converged (about half
-        % the size of the simulation).
-        U.lifetime_one = par.beta.^(1:ceil(ind_no/2))*sim.one.u((ceil(ind_no/2)+1):end,:);
-        U.lifetime_two = par.beta.^(1:ceil(ind_no/2))*sim.two.u((ceil(ind_no/2)+1):end,:);
-
-        %% Calculate the consumption equivalent
-        % If value > 1, agents prefer steady state one, if 1 > value > 0, agents prefer
-        % policy change ( = steady state two).
-        % Consumption equivalent tested against model with policy change.
-        c.equivalent_mean = ((mean(U.lifetime_two).*(1-par.sigma).*(1-par.beta)+1)...
-            ./(mean(U.lifetime_one).*(1-par.sigma).*(1-par.beta)+1)).^(1/(1-par.sigma));
-        
-        c.equivalent_median = ((median(U.lifetime_two).*(1-par.sigma).*(1-par.beta)+1)...
-            ./(median(U.lifetime_one).*(1-par.sigma).*(1-par.beta)+1)).^(1/(1-par.sigma)); 
-        % Calculate average and median of consumption equivalent. If this aggregate
-        % >1, there exists a (lump-sum) redistribution which would make everyone
-        % better off.
-
-    elseif strcmp(method.sim , 'histogram')
-        
[…]

### 2016-12-13 welfare_effects_rep.m

@@ -34,7 +34,7 @@ function [ c, U ] = welfare_effects_rep( par, func, sim, store, K, k, method )
 
     elseif strcmp(method.sim , 'histogram')
         
-        U.lifetime = sum(sum(store.distribution.*func.U(func.C(k.k)))); % Aggregate utility
+        U.lifetime = func.U(sum(sum(store.distribution.*(func.C(k.k))))); % Aggregate utility
         U.lifetime_rep = func.U(func.C(K.rep));
 
         %% Calculate the consumption equivalent

### 2016-12-14 krussel_smith.m
N/A changes

@@ -69,38 +69,38 @@ while dif_B>1e-8 %&& iter<50 % loop for aggregate problem
         % future capital state k''
         k_next_bu=interpn(grid_k,grid_K,k_guess(:,:,1,1),k_guess,K_guess,'cubic');
         % future consumption (c')
-        c_next_bu=max(1e-10,r(K_guess,L(1),z(1)).*k_guess+mat_income(K_guess,L(1),z(1),e(1))-k_next_bu);
+        c_next_bu=max(1e-10,r(K_guess,L(1),z(1)).*k_guess+mat_income(K_guess,L(1),z(1),e(1))+(1-delta).*k_guess-k_next_bu);
         % marginal utility of future consumption
         mu_next_bu=muc_inv(c_next_bu); 
         
         % Bad aggregate state and employed idiosyncratic state
         k_next_be=interpn(grid_k,grid_K,k_guess(:,:,1,2),k_guess,K_guess,'cubic');
-        c_next_be=max(1e-10,r(K_guess,L(1),z(1)).*k_guess+mat_income(K_guess,L(1),z(1),e(2)) - k_next_be);
+        c_next_be=max(1e-10,r(K_guess,L(1),z(1)).*k_guess+mat_income(K_guess,L(1),z(1),e(2))+(1-delta).*k_guess - k_next_be);
         mu_next_be=muc_inv(c_next_be);
         
         % Good aggregate state and unemployed idiosyncratic state
         k_next_gu=interpn(grid_k,grid_K,k_guess(:,:,2,1),k_guess,K_guess,'cubic');
-        c_next_gu=max(1e-10,r(K_guess,L(2),z(2)).*k_guess+mat_income(K_guess,L(2),z(2),e(1))-k_next_gu);
+        c_next_gu=max(1e-10,r(K_guess,L(2),z(2)).*k_guess+mat_income(K_guess,L(2),z(2),e(1))+(1-delta).*k_guess-k_next_gu);
         mu_next_gu=muc_inv(c_next_gu);
         
         % Good aggregate state and employed idiosyncratic state
         k_next_ge=interpn(grid_k,grid_K,k_guess(:,:,2,2),k_guess,K_guess,'cubic');
[…]

### 2016-12-14 parameters.m

@@ -43,7 +43,7 @@ muc = @(c) c.^(-sigma);                                             % marginal u
 muc_inv = @(muc) muc.^(-1/sigma);                                   % inverse of marginal utility of consumption
 w = @(K,L,z) z.*(1-alpha).*(K./(L*l_bar)).^alpha;           % wage
 w_mat = @(K,L,z) repmat(w(K',L,z),100,1,2,2);                       % wage matrix used for aggregate uncertainty
-r = @(K,L,z) (1-delta+z.*alpha.*(K./(L*l_bar)).^(alpha-1));          % rental rate of capital
+r = @(K,L,z) z.*alpha.*(K./(L*l_bar)).^(alpha-1);          % rental rate of capital
 r_mat = @(K,L,z) (1-delta+repmat(r(K',L,z),100,1,2,2));             % interest rate matrix used for aggregate uncertainty
 K = @(L,r,z) L*(z*alpha/r).^(1/(1-alpha));                          % capital stock necessary to yield return r
 Y = @(K,L,z) z*K.^alpha*L^(1-alpha);                                % output

### 2016-12-14 krussel_smith.m
Bug fixing, wealth function, income function

@@ -75,7 +75,7 @@ while dif_B>1e-8 %&& iter<50 % loop for aggregate problem
         
         % Bad aggregate state and employed idiosyncratic state
         k_next_be=interpn(grid_k,grid_K,k_guess(:,:,1,2),k_guess,K_guess,'cubic');
-        c_next_be=max(1e-10,r(K_guess,L(1),z(1)).*k_guess+mat_income(K_guess,L(1),z(1),e(2))+(1-delta).*k_guess - k_next_be);
+        c_next_be=max(1e-10,r(K_guess,L(1),z(1)).*k_guess+mat_income(K_guess,L(1),z(1),e(2))+(1-delta).*k_guess-k_next_be);
         mu_next_be=muc_inv(c_next_be);
         
         % Good aggregate state and unemployed idiosyncratic state
@@ -85,7 +85,7 @@ while dif_B>1e-8 %&& iter<50 % loop for aggregate problem
         
         % Good aggregate state and employed idiosyncratic state
         k_next_ge=interpn(grid_k,grid_K,k_guess(:,:,2,2),k_guess,K_guess,'cubic');
-        c_next_ge=max(1e-10,r(K_guess,L(2),z(2)).*k_guess+mat_income(K_guess,L(2),z(2),e(2)) +(1-delta).*k_guess- k_next_ge);
+        c_next_ge=max(1e-10,r(K_guess,L(2),z(2)).*k_guess+mat_income(K_guess,L(2),z(2),e(2))+(1-delta).*k_guess-k_next_ge);
         mu_next_ge=muc_inv(c_next_ge);
         
         
@@ -97,10 +97,10 @@ while dif_B>1e-8 %&& iter<50 % loop for aggregate problem
         
         c_current = muc_inv(beta*Emuc_next);
         k_new = NaN(100,4,2,2);
-        k_new(:,:,1,1) = (1-delta+repmat(r(grid_K',L(1),z(1)),grid_k_no,1)).*repmat(grid_k,1,grid_K_no)+repmat(mat_income(grid_K',L(1),z(1),e(1)),grid_k_no,1)-c_current(:,:,1,1);
[…]

### 2016-12-14 parameters.m

@@ -74,8 +74,9 @@ grid_K=linspace(K_min,K_max,grid_K_no)'; % generate a grid of grid_K_no points o
 
 % useful matricies
 mat_k = repmat(grid_k,1,4,2,2);                                     % replicate grid for unemployed and employed
-mat_income = @(K,L,z,e) ((1-tau(L))*l_bar*e + mu*(1-e)).*w(K,L,z); % matrix with income of each agent
+mat_income = @(K,L,z,e) (l_bar.*w(K,L,z) - mu.*w(K,L,z).*((1-L)/L))*e + mu*(1-e).*w(K,L,z); % matrix with income of each agent
 income = @(K,L,z,e) ((1-tau(L))*l_bar*e + mu*(1-e)).*w(K,L,z);
+wealth = @(K,k,L,z,e) repmat((1-delta+r(K',L(1),z(1))),grid_k_no,1).*repmat(grid_k,1,4) + repmat(w(K',L,z),grid_k_no,1).*e.*l_bar + mu.*(repmat(w(K',L,z),grid_k_no,1)*(1-e))-mu*(repmat(w(K',L,z),grid_k_no,1)*((1-L)/L))*e;
 
 % Forecasting
 B=[0 1 0 1];    

### 2017-01-17 calculate_cash_equiv.m
cash equiv solved

@@ -1,12 +1,15 @@
-function [ cash_equiv, cash_equiv_agg] = calculate_cash_equiv( mu_n, benchmark, store, name )
+function [ cash_equiv, cash_equiv_agg] = calculate_cash_equiv( mu_n, benchmark, store, sim_e, name )
 %UNTITLED Summary of this function goes here
 %   Detailed explanation goes here
 load(strcat('fixed_parameters_',name,'.mat'));
 
-%ASK HERE
+
 cash_equiv= NaN(1,ind_no);
+elu_bench = expec_lifetime_utility( store(benchmark).k_guess, store(benchmark).K_demand, store(benchmark).mu, name);
+elu_change = expec_lifetime_utility( store(mu_n).k_guess, store(mu_n).K_demand, store(mu_n).mu, name);
 for ind = 1:ind_no
-    cash_equiv(ind) = interp1(store(mu_n).U, grid_k, store(benchmark).U(ind)) - store(benchmark).sim_k(ind);
+    U = interp1(grid_k,elu_bench(sim_e(ind),:),store(benchmark).sim_k(ind),'linear','extrap');
+    cash_equiv(ind) = interp1(elu_change(sim_e(ind),:), grid_k, U) - store(benchmark).sim_k(ind);
 end
 
 cash_equiv_agg = sum(cash_equiv);

### 2017-01-17 calculate_cons_equiv.m

@@ -3,7 +3,7 @@ function [ cons_equiv, cons_equiv_mean, cons_equiv_median ] = calculate_cons_equ
 %   Detailed explanation goes here
 load(strcat('fixed_parameters_',name,'.mat'));
 
-cons_equiv = ((store(mu_n).U*(1-sigma)*(1-betta)+1)./(store(benchmark).U*(1-sigma)*(1-betta)+1)).^(1/(1-sigma));
+cons_equiv = ((store(benchmark).U*(1-sigma)*(1-betta)+1)./(store(mu_n).U*(1-sigma)*(1-betta)+1)).^(1/(1-sigma));
     
 cons_equiv_mean = mean(cons_equiv);
 cons_equiv_median = median(cons_equiv);

### 2017-01-17 main_welfare.m

@@ -1,11 +1,14 @@
-clear
+clear all
 close all
 clc
-name = '350_solutions_riegler';
+name = '40_solutions_riegler';
 
-if exist(strcat('fixed_parameters_',name,'.mat'), 'file') ~= 0
-    return
-end
+% if exist(strcat('fixed_parameters_',name,'.mat'), 'file') == 2 && nn == 1
+%     return
+% else 
+%     fixed_parameters;
+%     save(strcat('fixed_parameters_',name,'.mat'));
+% end
 
 fixed_parameters;
 save(strcat('fixed_parameters_',name,'.mat'));
@@ -17,7 +20,7 @@ period = 5000;
 sim_e = generate_shocks( T, ind_no, L, PI);
 mu_min = 0.30;
 mu_max = 0.99;
-mu_n = 350;
+mu_n = 40;
 grid_mu = linspace(mu_min, mu_max, mu_n);
 store(mu_n).mu = NaN; %prealocate
 for nn = 1:mu_n

### 2017-01-17 parameters.m

@@ -2,7 +2,7 @@
 % consumers
 beta = 0.99; % discount factor
 sigma = 2; % risk aversion
-mu = 0.9; % replacement rate of unemployed
+mu = 0.90; % replacement rate of unemployed
 k_min = 0.5; % borrowing constraint as share of capital stock
 ind_no = 5000; % number of individuals simulated
 T = 5000; % number of periods simulated

### 2017-01-17 per_better.m

@@ -1,0 +1,14 @@
+function [ better ] = per_better( current,last,store )
+%UNTITLED2 Summary of this function goes here
+%   Detailed explanation goes here
+sim_e = sim_e - 1;
+employed_n = sum(sim_e);
+unemployed_n = size(sim_e,2) - employed_n;
+aux = store(current).U - store(last).U;
+aux = aux(sim_e==1);
+aux_unem = aux(sim_e==0);
+em_better = (sum(aux_em(aux_em>0))/employed_n)*100;
+unem_better = (sum(aux_unem(aux_unem>0))/unemployed_n)*100;
+
+end
+

### 2017-01-17 per_better_two_states.m

@@ -1,0 +1,15 @@
+function [ em_better, unem_better, total_better ] = per_better_two_states( current,last,store, sim_e )
+%UNTITLED2 Summary of this function goes here
+%   Detailed explanation goes here
+sim_e = sim_e - 1;
+employed_n = sum(sim_e);
+unemployed_n = size(sim_e,2) - employed_n;
+aux = store(current).U - store(last).U;
+aux_em = aux(sim_e==1);
+aux_unem = aux(sim_e==0);
+em_better = (sum(aux_em>0)/employed_n)*100;
+unem_better = (sum(aux_unem>0)/unemployed_n)*100;
+total_better = (sum(aux>0)/size(sim_e,2))*100;
+
+end
+

### 2017-01-17 plot_welfare_trans.m

@@ -1,42 +1,62 @@
 clear
 close all
-name = '20_solutions_riegler';
+name = '40_solutions_riegler';
 load(name, 'store', 'shocks');
 
+store=store(1:24);
+
 sol_num = size(store,2);
+% sol_num =60;
 store(sol_num).U = [];
 U_mean = NaN(1,sol_num);
 for i = 1:sol_num
     [store(i).U, U_mean(i)] = calculate_welfare( i, store, shocks, name );
 end
 
-% mid = ceil(size(store,2)/2);
-mid = 2;
+bench = ceil(size(store,2)/2);
+% mid = 30;
 store(sol_num).cons_equiv = [];
 cons_mean = NaN(1,sol_num);
 cons_median = NaN(1,sol_num);
-for i = 2:sol_num
-    [store(i).cons_equiv, cons_mean(i), cons_median(i)]  = calculate_cons_equiv( i, i-1, store, name );
+for i = 1:sol_num
+    [store(i).cons_equiv, cons_mean(i), cons_median(i)]  = calculate_cons_equiv( i, bench, store, name );
 end
 
-% store(sol_num).cash_equiv = [];
-% cash_agg = NaN(1,sol_num);
-% for i = 2:sol_num
-%     [store(i).cash_equiv, cash_agg(i)]  = calculate_cash_equiv( i, i-1, store, name );
-% end
+em_better = NaN(1,sol_num);
+unem_better = NaN(1,sol_num);
+total_better = NaN(1,sol_num);
+for i = 2:sol_num
+    [em_better(i), unem_better(i), total_better(i)]  = per_better_two_states( i,1,store, shocks.sim_e(end,:) );
+end
+
+
+
+store(sol_num).cash_equiv = [];
+cash_agg = NaN(1,sol_num);
+for i = 2:sol_num
+    [store(i).cash_equiv, cash_agg(i)]  = calculate_cash_equiv( i, i-1, store,shocks.sim_e(end,:), name );
+end
 
 %% plot
 figure(1)
-plot(1:sol_num, cons_median);
+title('consumption equivalent')
+plot(1:sol_num, cons_median, 1:sol_num, cons_mean);
+legend('median','mean')
 
-figure(2)
-plot(1:sol_num, cons_mean);
+% figure(3)
+% title('Mean utility')
+% plot(1:sol_num, U_mean);
 
-figure(3)
-plot(1:sol_num, U_mean);
+figure(5)
+hold on
[…]

### 2017-01-17 parameters.m
calibration + error in extrapolation

@@ -2,7 +2,7 @@
 % consumers
 par.beta = 0.99; % discount factor
 par.sigma = 2; % risk aversion
-par.mu = 0.3; % replacement rate of unemployed
+par.mu = 0.5; % replacement rate of unemployed
 par.k_min = 0.5; % borrowing constraint as share of capital stock
 
 % firms (production function F(K,L)=z*K^alpha*L^(1-alpha)

### 2017-01-17 welfare_analysis.m

@@ -65,11 +65,11 @@ U.one.extrap = NaN(ceil(T/2),ind_no);
 U.two.extrap = NaN(ceil(T/2),ind_no);
 tic
 for t = ceil((T+1)/2):T % Extrapolated life time utility with transition
-    U.one.extrap(t-2500,sim.two.e(t,:)==1) = interp1(grid.two.k, U.one.lifetime(1,:), sim.two.k(t,sim.one.e(t,:)==1), 'linear', 'extrap');
-    U.one.extrap(t-2500,sim.two.e(t,:)==2) = interp1(grid.two.k, U.one.lifetime(2,:), sim.two.k(t,sim.one.e(t,:)==2), 'linear', 'extrap');
+    U.one.extrap(t-2500,sim.two.e(t,:)==1) = interp1(grid.two.k, U.one.lifetime(1,:), sim.two.k(t,sim.two.e(t,:)==1), 'linear', 'extrap');
+    U.one.extrap(t-2500,sim.two.e(t,:)==2) = interp1(grid.two.k, U.one.lifetime(2,:), sim.two.k(t,sim.two.e(t,:)==2), 'linear', 'extrap');
 
-    U.two.extrap(t-2500,sim.two.e(t,:)==1) = interp1(grid.two.k, U.two.lifetime(1,:), sim.two.k(t,sim.one.e(t,:)==1), 'linear', 'extrap');
-    U.two.extrap(t-2500,sim.two.e(t,:)==2) = interp1(grid.two.k, U.two.lifetime(2,:), sim.two.k(t,sim.one.e(t,:)==2), 'linear', 'extrap');
+    U.two.extrap(t-2500,sim.two.e(t,:)==1) = interp1(grid.two.k, U.two.lifetime(1,:), sim.two.k(t,sim.two.e(t,:)==1), 'linear', 'extrap');
+    U.two.extrap(t-2500,sim.two.e(t,:)==2) = interp1(grid.two.k, U.two.lifetime(2,:), sim.two.k(t,sim.two.e(t,:)==2), 'linear', 'extrap');
 end
 toc
 
@@ -83,4 +83,4 @@ toc
 k.equivalent_mean = mean(mean(k.equivalent));
 k.equivalent_median = median(median(k.equivalent));
 
-save .mat
+%save .mat

### 2017-01-17 welfare_analysis.m
Ready to run

@@ -29,8 +29,6 @@ setup % load setup
 tic
 for i=1:2 % Get steady state utility for the model with two different parameters
     if i==1 
-        par.z = 0.5;
-        setup % refresh setup for new parameter
         [ k.one, c.one, K.one, sim.one, store.one, mat.one, grid.one ] = aiyagari_solver( par, func, method );
         U.one.guess = func.U(c.one.guess);
         U.one.lifetime = zeros(2,grid.one.k_no); %expected life time utility
@@ -42,8 +40,8 @@ for i=1:2 % Get steady state utility for the model with two different parameters
             U.one.lifetime = Unew;
         end
     elseif i==2 
-        parameters;
-        setup;
+        par.mu = 0.6;
+        setup % refresh setup for new parameter
         [ k.two, c.two, K.two, sim.two, store.two, mat.two, grid.two ] = aiyagari_solver( par, func, method );
         U.two.guess = func.U(c.two.guess);
         U.two.lifetime = zeros(2,grid.two.k_no); %expected life time utility
@@ -82,5 +80,6 @@ toc
 [ k ] = cash_equivalent (par, method, grid, sim, U);
 k.equivalent_mean = mean(mean(k.equivalent));
 k.equivalent_median = median(median(k.equivalent));
-
-%save .mat
+keep.c = c;
+keep.k = k;
+save ('baseline_mu_0-6.mat', 'keep');

### 2017-01-17 plot_welfare_trans.m
changing after talking to professor

@@ -34,7 +34,7 @@ end
 store(sol_num).cash_equiv = [];
 cash_agg = NaN(1,sol_num);
 for i = 2:sol_num
-    [store(i).cash_equiv, cash_agg(i)]  = calculate_cash_equiv( i, i-1, store,shocks.sim_e(end,:), name );
+    [store(i).cash_equiv, cash_agg(i)]  = calculate_cash_equiv( i, bench, store,shocks.sim_e(end,:), name );
 end
 
 %% plot

### 2017-01-17 aiyagari_solver.m
welfare analysis done

@@ -100,13 +100,13 @@ while d1>1e-6 && iter<50 % loop for aggregate problem
         % update policy function
         k.guess = k.guess + 0.5*(k.new-k.guess);
     end
-    figure(1)
-    plot(grid.k,log(k.guess./[grid.k',grid.k']))
-    line([grid.k(1),grid.k(end)],[0,0])
-    legend('unemployed','employed')
-    xlabel('capital this period')
-    ylabel('log(capital next period/capital this period)')
-    title('policy functions')
+%     figure(1)
+%     plot(grid.k,log(k.guess./[grid.k',grid.k']))
+%     line([grid.k(1),grid.k(end)],[0,0])
+%     legend('unemployed','employed')
+%     xlabel('capital this period')
+%     ylabel('log(capital next period/capital this period)')
+%     title('policy functions')
     
     
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@ -130,15 +130,15 @@ while d1>1e-6 && iter<50 % loop for aggregate problem
             sim.k(t,sim.e(t,:)==1) = interp1(grid.k,k.guess(:,1),sim.k(t-1,sim.e(t,:)==1),'linear','extrap'); % capital demand of currently unemployed
             sim.k(t,sim.e(t,:)==2) = interp1(grid.k,k.guess(:,2),sim.k(t-1,sim.e(t,:)==2),'linear','extrap'); % capital demand of currently employed
         end
-        figure(4)
-        subplot(1,2,1)
-        plot(sum(sim.k,2)/ind_no) % plot aggregate capital demand
-        xlabel('period')
-        ylabel('capital demand')
-        subplot(1,2,2)
-        plot(sum(sim.e==2,2)/ind_no) % plot aggregate employment
-        xlabel('period')
-        ylabel('employment')    
+%         figure(4)
+%         subplot(1,2,1)
+%         plot(sum(sim.k,2)/ind_no) % plot aggregate capital demand
+%         xlabel('period')
+%         ylabel('capital demand')
+%         subplot(1,2,2)
+%         plot(sum(sim.e==2,2)/ind_no) % plot aggregate employment
+%         xlabel('period')
+%         ylabel('employment')    
 
[…]

### 2017-01-17 welfare_analysis.m

@@ -40,7 +40,7 @@ for i=1:2 % Get steady state utility for the model with two different parameters
             U.one.lifetime = Unew;
         end
     elseif i==2 
-        par.mu = 0.6;
+        par.mu = 0;
         setup % refresh setup for new parameter
         [ k.two, c.two, K.two, sim.two, store.two, mat.two, grid.two ] = aiyagari_solver( par, func, method );
         U.two.guess = func.U(c.two.guess);
@@ -82,4 +82,5 @@ k.equivalent_mean = mean(mean(k.equivalent));
 k.equivalent_median = median(median(k.equivalent));
 keep.c = c;
 keep.k = k;
-save ('baseline_mu_0-6.mat', 'keep');
+keep.U = U;
+save ('baseline_mu_0-3.mat', 'keep');

### 2017-01-18 cash_equivalent.m
calculate cons_equiv for each agent

@@ -9,9 +9,9 @@ function [ k ] = cash_equivalent( par, method, grid, sim, U )
         k.compensated = NaN(ceil(T/2),ind_no);
         tic
         for t = ceil((T+1)/2):T
-            k.compensated(t-2500,sim.two.e(t,:)==1) = interp1(U.one.lifetime(1,:), grid.two.k, U.two.extrap(t-2500,sim.two.e(t,:)==1), 'linear', 'extrap');
-            k.compensated(t-2500,sim.two.e(t,:)==2) = interp1(U.one.lifetime(2,:), grid.two.k, U.two.extrap(t-2500,sim.two.e(t,:)==2), 'linear', 'extrap');
-            k.equivalent(t-2500,:) = k.compensated(t-2500,:) - sim.two.k(t,:);   
+            k.compensated(t-2500,sim.one.e(t,:)==1) = interp1(U.one.lifetime(1,:), grid.one.k, U.two.extrap(t-2500,sim.one.e(t,:)==1), 'linear', 'extrap');
+            k.compensated(t-2500,sim.one.e(t,:)==2) = interp1(U.one.lifetime(2,:), grid.one.k, U.two.extrap(t-2500,sim.one.e(t,:)==2), 'linear', 'extrap');
+            k.equivalent(t-2500,:) = k.compensated(t-2500,:) - sim.one.k(t,:);   
         end
         toc
     elseif strcmp(method.sim, 'histogram')

### 2017-01-18 consumption_equivalent.m

@@ -3,23 +3,20 @@ function [ c ] = consumption_equivalent (par, method, U)
 %   Detailed explanation goes here
     
     if strcmp(method.sim ,'simulation')
-        U.one.mean = mean(mean(U.one.extrap));
-        U.two.mean = mean(mean(U.two.extrap));
-        U.one.median = median(median(U.one.extrap));
-        U.two.median = median(median(U.two.extrap));
  
         % Calculate the consumption equivalent
         % If value > 1, agents prefer steady state one, if 1 > value > 0, agents prefer
         % policy change ( = steady state two).
         % Consumption equivalent tested against model with policy change:
-        c.equivalent_mean = ((U.two.mean.*(1-par.sigma).*(1-par.beta)+1)...
-            ./(U.one.mean.*(1-par.sigma).*(1-par.beta)+1)).^(1/(1-par.sigma));
+        c.equivalent = ((U.two.extrap.*(1-par.sigma).*(1-par.beta)+1)...
+            ./(U.one.extrap.*(1-par.sigma).*(1-par.beta)+1)).^(1/(1-par.sigma));
 
-        c.equivalent_median = ((U.two.median.*(1-par.sigma).*(1-par.beta)+1)...
-            ./(U.one.median.*(1-par.sigma).*(1-par.beta)+1)).^(1/(1-par.sigma)); 
         % Calculate average and median of consumption equivalent. If this aggregate
         % >1, there exists a (lump-sum) redistribution which would make everyone
         % better off.
+        c.equivalent_mean = mean(mean(c.equivalent));
+        c.equivakent_median = median(median(c.equivalent));
+        
     elseif strcmp(method.sim,'histogram')
         % to be done
         

### 2017-01-18 welfare_analysis.m

@@ -40,7 +40,7 @@ for i=1:2 % Get steady state utility for the model with two different parameters
             U.one.lifetime = Unew;
         end
     elseif i==2 
-        par.mu = 0;
+        par.mu = 0.6;
         setup % refresh setup for new parameter
         [ k.two, c.two, K.two, sim.two, store.two, mat.two, grid.two ] = aiyagari_solver( par, func, method );
         U.two.guess = func.U(c.two.guess);
@@ -58,16 +58,16 @@ toc
 U.one.lifetime(U.one.lifetime == -Inf) = -999999; % Get rid of -Inf for negative consumption for extrapolation
 U.two.lifetime(U.two.lifetime == -Inf) = -999999;
 ind_no = size(sim.two.k,2);
-T = size(sim.two.k,1);
+T = size(sim.one.k,1);
 U.one.extrap = NaN(ceil(T/2),ind_no);
 U.two.extrap = NaN(ceil(T/2),ind_no);
 tic
 for t = ceil((T+1)/2):T % Extrapolated life time utility with transition
-    U.one.extrap(t-2500,sim.two.e(t,:)==1) = interp1(grid.two.k, U.one.lifetime(1,:), sim.two.k(t,sim.two.e(t,:)==1), 'linear', 'extrap');
-    U.one.extrap(t-2500,sim.two.e(t,:)==2) = interp1(grid.two.k, U.one.lifetime(2,:), sim.two.k(t,sim.two.e(t,:)==2), 'linear', 'extrap');
+    U.one.extrap(t-2500,sim.one.e(t,:)==1) = interp1(grid.one.k, U.one.lifetime(1,:), sim.one.k(t,sim.one.e(t,:)==1), 'linear', 'extrap');
+    U.one.extrap(t-2500,sim.one.e(t,:)==2) = interp1(grid.one.k, U.one.lifetime(2,:), sim.one.k(t,sim.one.e(t,:)==2), 'linear', 'extrap');
 
-    U.two.extrap(t-2500,sim.two.e(t,:)==1) = interp1(grid.two.k, U.two.lifetime(1,:), sim.two.k(t,sim.two.e(t,:)==1), 'linear', 'extrap');
[…]

### 2017-01-18 cash_equivalent.m
Correct cash equiv

@@ -14,6 +14,8 @@ function [ k ] = cash_equivalent( par, method, grid, sim, U )
             k.equivalent(t-2500,:) = k.compensated(t-2500,:) - sim.one.k(t,:);   
         end
         toc
+        k.equivalent_mean = mean(mean(k.equivalent));
+        k.equivalent_median = median(median(k.equivalent));
     elseif strcmp(method.sim, 'histogram')
         % to be done
 end

### 2017-01-18 consumption_equivalent.m

@@ -15,7 +15,7 @@ function [ c ] = consumption_equivalent (par, method, U)
         % >1, there exists a (lump-sum) redistribution which would make everyone
         % better off.
         c.equivalent_mean = mean(mean(c.equivalent));
-        c.equivakent_median = median(median(c.equivalent));
+        c.equivalent_median = median(median(c.equivalent));
         
     elseif strcmp(method.sim,'histogram')
         % to be done

### 2017-01-18 welfare_analysis.m

@@ -78,10 +78,9 @@ toc
 
 % Calculate the cash equivalent for the to steady states.
 [ k ] = cash_equivalent (par, method, grid, sim, U);
-k.equivalent_mean = mean(mean(k.equivalent));
-k.equivalent_median = median(median(k.equivalent));
+
 keep.c = c;
 keep.k = k;
 keep.K = K;
 %keep.U = U;
-save ('baseline_mu_0-6.mat', 'keep');
+save ('baseline_mu_0-7.mat', 'keep');

### 2017-01-19 presentation/presentation.tex
Add presentation

% Copyright 2004 by Till Tantau <tantau@users.sourceforge.net>.
%
% In principle, this file can be redistributed and/or modified under
% the terms of the GNU Public License, version 2.
%
% However, this file is supposed to be a template to be modified
% for your own needs. For this reason, if you use this file as a
% template and not specifically distribute it as part of a another
% package/program, I grant the extra permission to freely copy and
% modify this file as you see fit and even to delete this copyright
% notice.

\documentclass{beamer}
\usepackage{graphicx}
\usepackage{breqn}
\graphicspath{ {images/} }
\usepackage{amsmath}
\usepackage{dsfont}
% There are many different themes available for Beamer. A comprehensive
% list with examples is given here:
% http://deic.uab.es/~iblanes/beamer_gallery/index_by_theme.html
% You can uncomment the themes below if you would like to use a different
% one:
%\usetheme{AnnArbor}
%\usetheme{Antibes}
%\usetheme{Bergen}
%\usetheme{Berkeley}
\usetheme{Berlin}
%\usetheme{Boadilla}
%\usetheme{boxes}
%\usetheme{CambridgeUS}
%\usetheme{Copenhagen}
%\usetheme{Darmstadt}
%\usetheme{default}
%\usetheme{Frankfurt}
%\usetheme{Goettingen}
%\usetheme{Hannover}
%\usetheme{Ilmenau}
%\usetheme{JuanLesPins}
%\usetheme{Luebeck}
%\usetheme{Madrid}
%\usetheme{Malmoe}
%\usetheme{Marburg}
%\usetheme{Montpellier}
%\usetheme{PaloAlto}
%\usetheme{Pittsburgh}
%\usetheme{Rochester}
%\usetheme{Singapore}
%\usetheme{Szeged}
%\usetheme{Warsaw}

\title{Effects of Unemployment Benefits and Uncertainty in Heterogeneous Models}

% A subtitle is optional and this may be deleted
\subtitle{}

\author{Eric, Yannic and Andrian}
% - Give the names in the same order as the appear in the paper.
% - Use the \inst{?} command only if the authors have different
%   affiliation.

%\institute[Universities of Somewhere and Elsewhere] % (optional, but mostly needed)
%{
% \inst{1}%
%  Department of Computer Science\\
%  University of Somewhere
%  \and
%  \inst{2}%
%  Department of Theoretical Philosophy\\
%  University of Elsewhere}
% - Use the \inst command only if there are several affiliations.
% - Keep it simple, no one is interested in your street address.

%\date{Conference Name, 2013}
% - Either use conference name or its abbreviation.
% - Not really informative to the audience, more for people (including
%   yourself) who are reading the slides online

%\subject{Theoretical Computer Science}
% This is only inserted into the PDF information catalog. Can be left
% out.

% If you have a file called "university-logo-filename.xxx", where xxx
% is a graphic format that can be processed by latex or pdflatex,
% resp., then you can add a logo as follows:

% \pgfdeclareimage[height=0.5cm]{university-logo}{university-logo-filename}
% \logo{\pgfuseimage{university-logo}}

% Delete this, if you do not want the table of contents to pop up at
% the beginning of each subsection:
\AtBeginSubsection[]
{
  \begin{frame}<beamer>{Outline}
    \tableofcontents[currentsection,currentsubsection]
  \end{frame}
}

% Let's get started
\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{Outline}
  \tableofcontents
  % You might wish to add the option [pausesections]
\end{frame}

% Section and subsections will appear in the presentation overview
% and table of contents.
\section{Part I}
\subsection{}
\begin{frame}{Motivation}
  \begin{itemize}

  \item {
  Item 1
  }

  \item {
  Item 2  
  }

  \item {
  Item 3
  }
  \end{itemize}

  \centering{\includegraphics[scale=0.30]{eq18}}
\end{frame}

\section{Part II}
\subsection{}

\section{Part III}
\subsection{}

\end{document}

### 2017-01-19 presentation/presentation.tex
Start
changes

@@
 
+\begin{frame}{Adding aggregate uncertainty}
+  \begin{itemize}
+
+  \item {
+  Aggregate uncertainty! Why?
+  }
+  \pause
+  \item {
+  Two aggregate productivity : $z \in \{ 0.99, 1.01 \}$.
+  }
+
+  \item {
+  Two unemployment states: $L \in \{ 0.1, 0.4 \}$.
+  }
+
+  \item {
+  2 transition matricies between employed and unemployed respectively in good and bad states and 1 transition matrix between good and bad state: $L \in \{ 0.1, 0.4 \}$.
+  }
+
+  \pause
+
+  \item {
+  Let's solve it!.
+  }
+
+  \end{itemize}
+
+\end{frame}
+
+\begin{frame}{Problem}
+  \begin{itemize}
+
+  \item {
+  The introduction of aggregate uncertainty makes the distribution of wealth changing over time, which is infinite dimensional object.
+  }
+
+  \item {
+  The capital distribution must be taken into account by the agents, therefore it becomes state variable.
+  }
+
+  \end{itemize}
+
+\end{frame}
+
+\begin{frame}{Solution}
+  \begin{itemize}
+
+  \item {
+  There is no solution.
+  }
+
+  \item {
+  Krusell and Smith (1997) suggest an algorithm to solve the issue by an approximation, which could be summerized as "rational adaptive expectations".
+  }
+
+  \item {
+  They assume that the agents forecast prices by using the future mean of the wealth distribution.
+  }
+
+  \item {
+  The actual forecast is made for the future mean based on previous realizations using some Least Squares technique.
+  }
+
+  \end{itemize}
+
+\end{frame}
+
+\begin{frame}{Algorithm}
+  \begin{enumerate}
+
+  \item {
+  Draw shocks.
+  }
+
+  \item {
+  Guess initial coefficients for the forcasting rule.  
+  }
+
+  \item {
+  Solve the individual problem.
+  }
+
+  \item {
+  Use the policy function to generate a sequence of capital distributions.
+  }
+
+  \item {
+  The actual forecast is made for the future mean based on previous realizations using some Least Squares technique.
+  }
+
+  \item {
+  Estimate new coefficients based on past realizations of the distribution and iterate until they converge. 
+  }
+
+  \end{enumerate}
+
+\end{frame}
+
 \end{document}

### 2017-01-19 graph_cash_equivalent.m
Plotted graphs for equivalents

@@ -1,0 +1,73 @@
+%% Create graph of cash equivalent for different values of unemployment benefit (mu) with mu = 0.5 as baseline
+clear
+close all
+
+%mu030= load('baseline_mu_0-3');
+mu034= load('baseline_mu_0-34');
+mu039 = load('baseline_mu_0-39');
+mu040 = load('baseline_mu_0-4');
+mu041 = load('baseline_mu_0-41');
+mu042 = load('baseline_mu_0-42');
+mu043 = load('baseline_mu_0-43');
+mu044 = load('baseline_mu_0-44');
+mu045 = load('baseline_mu_0-45');
+mu047 = load('baseline_mu_0-47');
+mu055 = load('baseline_mu_0-55');
+mu057 = load('baseline_mu_0-57');
+mu058 = load('baseline_mu_0-58');
+mu059 = load('baseline_mu_0-59');
+mu060 = load('baseline_mu_0-6');
+mu061 = load('baseline_mu_0-61');
+mu065 = load('baseline_mu_0-65');
+mu070 = load('baseline_mu_0-7');
+mu072 = load('baseline_mu_0-72');
+mu075 = load('baseline_mu_0-75');
+mu080 = load('baseline_mu_0-8');
+
+mu = [0.34 0.39 0.4 0.41 0.42 0.43 0.44 0.45 0.47 0.5 0.55 0.57 0.58 0.59 0.6 0.61 0.65 0.7 0.72 0.75 0.8];
+graph_var = [
+            mu034.keep.k.equivalent_mean, mu034.keep.k.equivalent_median, mu034.keep.c.equivalent_mean, mu034.keep.c.equivalent_median, mu034.keep.K.two.guess;
+            mu039.keep.k.equivalent_mean, mu039.keep.k.equivalent_median, mu039.keep.c.equivalent_mean, mu039.keep.c.equivalent_median, mu039.keep.K.two.guess;
+            mu040.keep.k.equivalent_mean, mu040.keep.k.equivalent_median, mu040.keep.c.equivalent_mean, mu040.keep.c.equivalent_median, mu040.keep.K.two.guess;
+            mu041.keep.k.equivalent_mean, mu041.keep.k.equivalent_median, mu041.keep.c.equivalent_mean, mu041.keep.c.equivalent_median, mu041.keep.K.two.guess;
[…]

### 2017-01-19 welfare_analysis.m

@@ -40,7 +40,7 @@ for i=1:2 % Get steady state utility for the model with two different parameters
             U.one.lifetime = Unew;
         end
     elseif i==2 
-        par.mu = 0.6;
+        par.mu = 0.47;
         setup % refresh setup for new parameter
         [ k.two, c.two, K.two, sim.two, store.two, mat.two, grid.two ] = aiyagari_solver( par, func, method );
         U.two.guess = func.U(c.two.guess);
@@ -52,7 +52,7 @@ for i=1:2 % Get steady state utility for the model with two different parameters
             dist = max(max(abs(Unew - U.two.lifetime)));
             U.two.lifetime = Unew;
         end
-    end
+   end
 end
 toc
 U.one.lifetime(U.one.lifetime == -Inf) = -999999; % Get rid of -Inf for negative consumption for extrapolation
@@ -79,8 +79,10 @@ toc
 % Calculate the cash equivalent for the to steady states.
 [ k ] = cash_equivalent (par, method, grid, sim, U);
 
-keep.c = c;
-keep.k = k;
+keep.c.equivalent_mean = c.equivalent_mean;
+keep.c.equivalent_median = c.equivalent_median;
+keep.k.equivalent_mean = k.equivalent_mean;
+keep.k.equivalent_median = k.equivalent_median;
 keep.K = K;
 %keep.U = U;
-save ('baseline_mu_0-7.mat', 'keep');
+save ('baseline_mu_0-47.mat', 'keep');

### 2017-01-19 analysis.m
Analysis with mu grid and possibility to change the PI_UE with mu. The probability adjustment grid is linear and can be improved, when for each grid-point of mu, the exact change is calculated.

@@ -1,5 +1,4 @@
 %% Analysis
-
 clear 
 close all
 
@@ -9,8 +8,20 @@ par.ind_no = 100; % number of individuals simulated
 par.T = 100; % number of periods simulated
 
 %% Specify the parameter of interest and their values
-method.analysis = 'Chance to be Employed'; % specify parameter you want to analyze: 'Borrowing Constraint' for min savings, 'Unemployment Benefit', 'Chance to be Employed','Risk Aversion'
-par.vals = [0.1,0.3,0.9]; %indicate three parameter values for comparison
+method.analysis = 'Unemployment Benefit'; % specify parameter you want to analyze: 'Borrowing Constraint' for min savings, 'Unemployment Benefit', 'Chance to be Employed','Risk Aversion'
+% par.vals = [0.15,0.25,0.35]; % indicate three parameter values for comparison
+% par.vals2 = [0.4,0.25,0.2]; % for the second analysis, also change a second set of parameters
+
+%% Plot grids
+gridpar.start = 0.15;
+gridpar.end = 0.35;
+gridpar.no = 10;
+mgrid.mu = linspace(gridpar.start,gridpar.end,gridpar.no);
+
+gridpar.start2 = 0.4;
+gridpar.end2 = 0.2;
+mgrid.pi = linspace(gridpar.start2, gridpar.end2,gridpar.no);
+
 
 %% Call the plotting function 
-plotting_fct(par, method) 
+plotting_fct(par, method, gridpar, mgrid) 

### 2017-01-19 parameters.m

@@ -2,18 +2,19 @@
 %% set parameters
 % consumers
 par.beta = 0.99; % discount factor
-par.sigma = 2; % risk aversion
-par.mu = 0.3; % replacement rate of unemployed
-par.k_min = 0.5; % borrowing constraint as share of capital stock
+par.sigma = 1; % risk aversion
+par.mu = 0.15; % replacement rate of unemployed
+par.k_min = 0; % borrowing constraint as share of capital stock
 
 % firms (production function F(K,L)=z*K^alpha*L^(1-alpha)
 par.delta = 0.025; % depreciation rate
-par.alpha = 0.33; % output elasticity of capital
+par.alpha = 0.36; % output elasticity of capital
 par.z = 1; % productivity
 
 % transition probabilities
 par.L_target = 0.9;
-par.PI_UE = 0.3; % chance of getting employed
+%par.PI_EU = 0.4*(1-0.9)/0.9; % setting the layoff probability to the baseline case
+par.PI_UE = 0.4; % chance of getting employed
 
 
 

### 2017-01-19 plotting_fct.m

@@ -1,4 +1,4 @@
-function plotting_fct(par, method) 
+function plotting_fct(par, method, gridpar, mgrid) 
 %% PLOTTING FUNCTION: The function creates a figure with three different
 % subplots for a vector of a parmater chosen for analysis. For each value
 % the parameter takes, the function creates a table containing the
@@ -14,82 +14,228 @@ function plotting_fct(par, method)
 %
 %% Create Figures for different values 
 % Initiating matrix to store aggregate values    
-T_mat = zeros(6,3);
-
+%T_mat = zeros(12,gridpar.no,3);
+T_mat = zeros(12,gridpar.no);
 parameters % import parameters 
 
-for i =1:3 
+for i = 1:gridpar.no
 % loop over different values of parameter you want to analyze 
-    if strcmp(method.analysis,'Borrowing Constraint') 
-        par.k_min = par.vals(i);
-    elseif strcmp(method.analysis, 'Chance to be Employed')
-        par.PI_UE = par.vals(i);
-    elseif strcmp(method.analysis, 'Unemployment Benefit')
-        par.mu = par.vals(i);
-    elseif strcmp(method.analysis, 'Risk Aversion')
-        par.sigma = par.vals(i); 
-    end
+    %for ii = 1:3
+        if strcmp(method.analysis,'Borrowing Constraint') 
+            par.k_min = par.vals(i);
+        elseif strcmp(method.analysis, 'Chance to be Employed')
+            par.PI_UE = par.vals(i);
+        elseif strcmp(method.analysis, 'Unemployment Benefit')
+            par.mu = mgrid.mu(i);
+            par.PI_UE = mgrid.pi(i); % letting transition fluctuate with benefits 
+        elseif strcmp(method.analysis, 'Risk Aversion')
+            par.sigma = par.vals(i); 
+        end
 % importing functions and parameters that adapt to new input parameter value             
-    setup 
+        setup 
 % calling the problem solving function 
-    [k, c, K, sim, store, mat, grid] = aiyagari_solver(par, func, method); 
+        [k, c, K, sim, store, mat, grid] = aiyagari_solver(par, func, method); 
 
[…]

### 2017-01-19 setup.m

@@ -1,6 +1,6 @@
 %% setup
 par.PI_EU = par.PI_UE*(1-par.L_target)/par.L_target; % chance of getting unemployed
-
+% letting the target rate fluctuate instead of PI_EU
 % build transition matrix of agents
 par.PI = [1-par.PI_UE,par.PI_UE;par.PI_EU,1-par.PI_EU]; % [UU,UE;EU;EE]
 par.L = par.PI(1,2)/(par.PI(1,2)+par.PI(2,1)); % calculate steady state supply of labour

### 2017-01-19 cash_equivalent.m
automate welfare analysis for grid of mu

@@ -16,6 +16,12 @@ function [ k ] = cash_equivalent( par, method, grid, sim, U )
         toc
         k.equivalent_mean = mean(mean(k.equivalent));
         k.equivalent_median = median(median(k.equivalent));
+        % Get cash equivalent for employed and unemployed
+        k.equivalent_unemployed_mean = mean(mean(k.equivalent(:,sim.one.e(:,:)==1)));
+        k.equivalent_unemployed_median = median(median(k.equivalent(:,sim.one.e(:,:)==1)));
+        k.equivalent_employed_mean = mean(mean(k.equivalent(:,sim.one.e(:,:)==2)));
+        k.equivalent_employed_median = median(median(k.equivalent(:,sim.one.e(:,:)==2)));
+        
     elseif strcmp(method.sim, 'histogram')
         % to be done
 end

### 2017-01-19 consumption_equivalent.m

@@ -1,4 +1,4 @@
-function [ c ] = consumption_equivalent (par, method, U)
+function [ c ] = consumption_equivalent (par, method, U, sim)
 %WELFARE EFFECTS Summary of this function goes here
 %   Detailed explanation goes here
     
@@ -16,6 +16,12 @@ function [ c ] = consumption_equivalent (par, method, U)
         % better off.
         c.equivalent_mean = mean(mean(c.equivalent));
         c.equivalent_median = median(median(c.equivalent));
+        
+        % Get consumption equivalent for employed and unemployed
+        c.equivalent_unemployed_mean = mean(mean(c.equivalent(:,sim.one.e(:,:)==1)));
+        c.equivalent_unemployed_median = median(median(c.equivalent(:,sim.one.e(:,:)==1)));
+        c.equivalent_employed_mean = mean(mean(c.equivalent(:,sim.one.e(:,:)==2)));
+        c.equivalent_employed_median = median(median(c.equivalent(:,sim.one.e(:,:)==2)));
         
     elseif strcmp(method.sim,'histogram')
         % to be done

### 2017-01-19 welfare_analysis.m

@@ -7,17 +7,6 @@ setup % load setup
 % Change simulation method to histogram if you want.
 %method.sim = 'histogram';
 
-%% Welfare analysis against frictionless representative agent model
-
-% tic % Set timer
-% % Solve the Aiyagariy model by fixed-point iteration.
-% % Function in- and output are structures.
-% [k, c, K, sim, store, mat, grid]= aiyagari_solver(par, func, method);
-% toc
-% 
-% % Compare welfare against frictionless model
-% [c, U] = welfare_effects_rep(par, func, method, k, c, K, sim, store, mat, grid);
-
 %% Welfare effects of two Aiyagari models with different parameters.
 
 % Default parameterization is set by the calibration of Markus Riegler. If
@@ -25,7 +14,10 @@ setup % load setup
 % you call the function. If you want to compare one steady state with the
 % default one, change parameters for i=2 and leave i=1 as the default one.
 % Do not change beta or sigma!
-
+mu_min = 0.05;
+mu_max = 0.8
+mu_n = 20;
+mu = linspace(mu_min, mu_max, mu_n);
 tic
 for i=1:2 % Get steady state utility for the model with two different parameters
     if i==1 
@@ -39,50 +31,61 @@ for i=1:2 % Get steady state utility for the model with two different parameters
             dist = max(max(abs(Unew - U.one.lifetime)));
             U.one.lifetime = Unew;
         end
-    elseif i==2 
-        par.mu = 0.47;
-        setup % refresh setup for new parameter
-        [ k.two, c.two, K.two, sim.two, store.two, mat.two, grid.two ] = aiyagari_solver( par, func, method );
-        U.two.guess = func.U(c.two.guess);
-        U.two.lifetime = zeros(2,grid.two.k_no); %expected life time utility
-        dist=100;
-        while dist>1e-8
-            EU = par.PI * U.two.lifetime; 
-            Unew = U.two.guess' + par.beta * EU;
-            dist = max(max(abs(Unew - U.two.lifetime)));
-            U.two.lifetime = Unew;
+        U.one.lifetime(U.one.lifetime == -Inf) = -999999; % Get rid of -Inf for negative consumption for extrapolation
+        ind_no = size(sim.one.k,2);
+        T = size(sim.one.k,1);
[…]

### 2017-01-19 parameters.m
Set calibration to Krussel-Smith

@@ -2,17 +2,17 @@
 % consumers
 par.beta = 0.99; % discount factor
 par.sigma = 2; % risk aversion
-par.mu = 0.5; % replacement rate of unemployed
-par.k_min = 0.5; % borrowing constraint as share of capital stock
+par.mu = 0.15; % replacement rate of unemployed
+par.k_min = 0; % borrowing constraint as share of capital stock
 
 % firms (production function F(K,L)=z*K^alpha*L^(1-alpha)
 par.delta = 0.025; % depreciation rate
-par.alpha = 0.33; % output elasticity of capital
+par.alpha = 0.36; % output elasticity of capital
 par.z = 1; % productivity
 
 % transition probabilities
 par.L_target = 0.9;
-par.PI_UE = 0.3; % chance of getting employed
+par.PI_UE = 0.4; % chance of getting employed
 
 
 

### 2017-01-19 aiyagari_solver.m
automate solution with mu grid

@@ -57,7 +57,7 @@ while d1>1e-6 && iter<50 % loop for aggregate problem
                     k.next(i,:,j) = interp1(grid.k,k.guess(:,j),k.guess(:,i),'linear','extrap'); 
                 end
                     % consumption next period from budget constraint
-                    c.next(i,:,:) = max(1e-10,(1+func.r(K.guess)-par.delta)*[k.guess(:,i),k.guess(:,i)] - squeeze(k.next(i,:,:)) + mat_income(K_guess));
+                    c.next(i,:,:) = max(1e-10,(1+func.r(K.guess)-par.delta)*[k.guess(:,i),k.guess(:,i)] - squeeze(k.next(i,:,:)) + mat.income(K.guess));
             end
 
             % calculate expected marginal utility of consumption next period

### 2017-01-19 cash_equivalent.m

@@ -7,20 +7,25 @@ function [ k ] = cash_equivalent( par, method, grid, sim, U )
         T = size(sim.one.k,1);
         k.equivalent = NaN(ceil(T/2),ind_no);
         k.compensated = NaN(ceil(T/2),ind_no);
-        tic
-        for t = ceil((T+1)/2):T
-            k.compensated(t-2500,sim.one.e(t,:)==1) = interp1(U.one.lifetime(1,:), grid.one.k, U.two.extrap(t-2500,sim.one.e(t,:)==1), 'linear', 'extrap');
-            k.compensated(t-2500,sim.one.e(t,:)==2) = interp1(U.one.lifetime(2,:), grid.one.k, U.two.extrap(t-2500,sim.one.e(t,:)==2), 'linear', 'extrap');
-            k.equivalent(t-2500,:) = k.compensated(t-2500,:) - sim.one.k(t,:);   
+        
+        for t = 1:ceil(T/2)
+            k.compensated(t,sim.one.e(t+ceil(T/2),:)==1) = interp1(U.one.lifetime(1,:), grid.one.k, U.two.extrap(t,sim.one.e(t+ceil(T/2),:)==1), 'linear', 'extrap');
+            k.compensated(t,sim.one.e(t+ceil(T/2),:)==2) = interp1(U.one.lifetime(2,:), grid.one.k, U.two.extrap(t,sim.one.e(t+ceil(T/2),:)==2), 'linear', 'extrap');
+            k.equivalent(t,:) = k.compensated(t,:) - sim.one.k(t+ceil(T/2),:);   
+            k.equivalent_unemployed_mean(t,:) = mean(k.equivalent(t,sim.one.e(ceil(T/2)+t,:)==1));
+            k.equivalent_unemployed_median(t,:) = median(k.equivalent(t,sim.one.e(ceil(T/2)+t,:)==1));
+            k.equivalent_employed_mean(t,:) = mean(k.equivalent(t,sim.one.e(ceil(T/2)+t,:)==2));
+            k.equivalent_employed_median(t,:) = median(k.equivalent(t,sim.one.e(ceil(T/2)+t,:)==2));
         end
-        toc
+        
         k.equivalent_mean = mean(mean(k.equivalent));
         k.equivalent_median = median(median(k.equivalent));
+        
         % Get cash equivalent for employed and unemployed
-        k.equivalent_unemployed_mean = mean(mean(k.equivalent(:,sim.one.e(:,:)==1)));
[…]

### 2017-01-19 consumption_equivalent.m

@@ -18,10 +18,17 @@ function [ c ] = consumption_equivalent (par, method, U, sim)
         c.equivalent_median = median(median(c.equivalent));
         
         % Get consumption equivalent for employed and unemployed
-        c.equivalent_unemployed_mean = mean(mean(c.equivalent(:,sim.one.e(:,:)==1)));
-        c.equivalent_unemployed_median = median(median(c.equivalent(:,sim.one.e(:,:)==1)));
-        c.equivalent_employed_mean = mean(mean(c.equivalent(:,sim.one.e(:,:)==2)));
-        c.equivalent_employed_median = median(median(c.equivalent(:,sim.one.e(:,:)==2)));
+        T = size(sim.one.e,1);
+        for t=1:ceil(T/2)
+            c.equivalent_unemployed_mean(t,:) = mean(c.equivalent(t,sim.one.e(ceil(T/2)+t,:)==1));
+            c.equivalent_unemployed_median(t,:) = median(c.equivalent(t,sim.one.e(ceil(T/2)+t,:)==1));
+            c.equivalent_employed_mean(t,:) = mean(c.equivalent(t,sim.one.e(ceil(T/2)+t,:)==2));
+            c.equivalent_employed_median(t,:) = median(c.equivalent(t,sim.one.e(ceil(T/2)+t,:)==2));
+        end
+        c.equivalent_unemployed_mean = mean(c.equivalent_unemployed_mean);
+        c.equivalent_unemployed_median = median(c.equivalent_unemployed_median);
+        c.equivalent_employed_mean = mean(c.equivalent_employed_mean);
+        c.equivalent_employed_median = median(c.equivalent_employed_median);
         
     elseif strcmp(method.sim,'histogram')
         % to be done

### 2017-01-19 graph_cash_equivalent.m

@@ -2,72 +2,82 @@
 clear
 close all
 
-%mu030= load('baseline_mu_0-3');
-mu034= load('baseline_mu_0-34');
-mu039 = load('baseline_mu_0-39');
-mu040 = load('baseline_mu_0-4');
-mu041 = load('baseline_mu_0-41');
-mu042 = load('baseline_mu_0-42');
-mu043 = load('baseline_mu_0-43');
-mu044 = load('baseline_mu_0-44');
-mu045 = load('baseline_mu_0-45');
-mu047 = load('baseline_mu_0-47');
-mu055 = load('baseline_mu_0-55');
-mu057 = load('baseline_mu_0-57');
-mu058 = load('baseline_mu_0-58');
-mu059 = load('baseline_mu_0-59');
-mu060 = load('baseline_mu_0-6');
-mu061 = load('baseline_mu_0-61');
-mu065 = load('baseline_mu_0-65');
-mu070 = load('baseline_mu_0-7');
-mu072 = load('baseline_mu_0-72');
-mu075 = load('baseline_mu_0-75');
-mu080 = load('baseline_mu_0-8');
+mu_min = 0.05;
+mu_max = 0.8;
+mu_n = 20;
+mu = linspace(mu_min, mu_max, mu_n);
+for i=1:size(mu,2)
+    filename = ['baseline_mu_' num2str(ii) '.mat'];
+    c(ii) = load(filename, c);
+    k(ii) = load(filename, k);
+end
 
-mu = [0.34 0.39 0.4 0.41 0.42 0.43 0.44 0.45 0.47 0.5 0.55 0.57 0.58 0.59 0.6 0.61 0.65 0.7 0.72 0.75 0.8];
-graph_var = [
-            mu034.keep.k.equivalent_mean, mu034.keep.k.equivalent_median, mu034.keep.c.equivalent_mean, mu034.keep.c.equivalent_median, mu034.keep.K.two.guess;
-            mu039.keep.k.equivalent_mean, mu039.keep.k.equivalent_median, mu039.keep.c.equivalent_mean, mu039.keep.c.equivalent_median, mu039.keep.K.two.guess;
-            mu040.keep.k.equivalent_mean, mu040.keep.k.equivalent_median, mu040.keep.c.equivalent_mean, mu040.keep.c.equivalent_median, mu040.keep.K.two.guess;
[…]

### 2017-01-19 parameters.m

@@ -3,7 +3,7 @@
 par.beta = 0.99; % discount factor
 par.sigma = 2; % risk aversion
 par.mu = 0.15; % replacement rate of unemployed
-par.k_min = 0; % borrowing constraint as share of capital stock
+par.k_min = 1e-15; % borrowing constraint as share of capital stock
 
 % firms (production function F(K,L)=z*K^alpha*L^(1-alpha)
 par.delta = 0.025; % depreciation rate
@@ -18,6 +18,6 @@ par.PI_UE = 0.4; % chance of getting employed
 
 
 %% solve for general equilibrium
-method.HH = 'FPend'; % 'FP' for fixed-point iteration in household problem, 'FPend' for using endogenous grid points
+method.HH = 'FP'; % 'FP' for fixed-point iteration in household problem, 'FPend' for using endogenous grid points
 method.sim = 'simulation'; % 'simulation' for simulation, 'histogram' for histogram method
-method.agg = 'bisection'; % 'bisection' to use bisection method, gradual updating otherwise
+method.agg = 'bisectio'; % 'bisection' to use bisection method, gradual updating otherwise

### 2017-01-19 welfare_analysis.m

@@ -15,7 +15,7 @@ setup % load setup
 % default one, change parameters for i=2 and leave i=1 as the default one.
 % Do not change beta or sigma!
 mu_min = 0.05;
-mu_max = 0.8
+mu_max = 0.8;
 mu_n = 20;
 mu = linspace(mu_min, mu_max, mu_n);
 tic
@@ -40,8 +40,11 @@ for i=1:2 % Get steady state utility for the model with two different parameters
             U.one.extrap(t-ceil(T/2),sim.one.e(t,:)==2) = interp1(grid.one.k, U.one.lifetime(2,:), sim.one.k(t,sim.one.e(t,:)==2), 'linear', 'extrap');
         end
     elseif i==2 
-        for ii=1:size(mu,2)
-            par.mu = mu(ii);
+        for ii=5:size(mu,2)
+            par.mu = mu(ii)
+            method.HH = 'FP'; 
+            method.sim = 'simulation'; 
+            method.agg = 'bisection';
             setup % refresh setup for new parameter
             [ k.two, c.two, K.two, sim.two, store.two, mat.two, grid.two ] = aiyagari_solver( par, func, method );
             U.two.guess = func.U(c.two.guess);
@@ -82,7 +85,8 @@ for i=1:2 % Get steady state utility for the model with two different parameters
             keep.k.equivalent_employed_mean = k.equivalent_employed_mean;
             keep.k.equivalent_employed_median = k.equivalent_employed_median;
             keep.K = K.two.guess;
-            save ('baseline_mu_'+ ii +'.mat', '-struct','keep');
+            filename = ['baseline_mu_' num2str(ii) '.mat'];
+            save (filename, '-struct','keep');
         end
     end
 end

### 2017-01-19 welfare_effects_rep.m

@@ -1,74 +1,0 @@
-function [ c, U ] = welfare_effects_rep (par, func, method, k, c, K, sim, store, mat, grid)
-%WELFARE EFFECTS REP Calculates whether agents prefer a frictionless, representative agent model or not
-%   Detailed explanation goes here
-    
-    if strcmp(method.sim ,'simulation')
-
-        
-        T = size(sim.k);
-        ind_no = size(sim.k,2);
-        sim.c = zeros(T,ind_no); % simulate series of consumption
-        for t=1:T
-            sim.c(t,sim.e(t,:)==1) = interp1(grid.k,c.guess(:,1),sim.k(t,sim.e(t,:)==1),'linear','extrap'); % consumption of currently unemployed
-            sim.c(t,sim.e(t,:)==2) = interp1(grid.k,c.guess(:,2),sim.k(t,sim.e(t,:)==2),'linear','extrap'); % consumption of currently employed
-        end
-
-        period = ceil(T/2);
-        U.lifetime = par.beta.^(0:period) * func.U(sim.c(period:end,:)); % calculate life-time utility
-        U.lifetime_rep = sum(par.beta.^(0:period) * func.U(func.C(K.rep)));
-       
-        %% Calculate the consumption equivalent
-        % If value > 1, agents prefer standard model, if 1 > value > 0, agents prefer
-        % Aiyagari model.
-        % Consumption equivalent tested against frictionless benchmark model.
-        c.equivalent_bench = ((U.lifetime_rep.*(1-par.sigma).*(1-par.beta)+1)...
-            ./(U.lifetime.*(1-par.sigma).*(1-par.beta)+1)).^(1/(1-par.sigma)); 
-        figure(6)
-        histogram(c.equivalent_bench)
-        xlabel('Consumption equivalents')
-        % Calculate average and median of consumption equivalent. If this aggregate
-        % >1, there exists a (lump-sum) redistribution which would make everyone
-        % better off.
-        c.equivalent_bench_mean = mean(c.equivalent_bench);
-        c.equivalent_bench_median = median(c.equivalent_bench);
-        
-        % Just to see how consumption looks overall
-%         a = sim.c(period:end,:);
-%         figure(7)
-%         histogram(a(:),100)
-        
-
-    elseif strcmp(method.sim , 'histogram')
-   
-        for i=1:2 % currently unemployed and employed
[…]

### 2017-01-20 graph_equivalents.m
Change grid to a lower minimum

@@ -2,37 +2,47 @@
 clear
 close all
 
-mu_min = 0.05;
-mu_max = 0.8;
+mu_min = 0.01;
+mu_max = 0.6;
 mu_n = 20;
 mu = linspace(mu_min, mu_max, mu_n);
-for i=1:size(mu,2)
-    filename = ['baseline_mu_' num2str(ii) '.mat'];
-    c(ii) = load(filename, c);
-    k(ii) = load(filename, k);
-end
+mu(7) = mu(6); % the original point does not converge
+mu(6) = 0.15;
+mu(8) = 0.18;
 
+for i=1:mu_n
+    filename = ['baseline_mu_' num2str(i) '.mat'];
+    c(i) = load(filename, 'c');
+    k(i) = load(filename, 'k');
+    c_equiv(i,:) = [c(i).c.equivalent_mean, c(i).c.equivalent_median, c(i).c.equivalent_unemployed_mean, c(i).c.equivalent_unemployed_median, c(i).c.equivalent_employed_mean, c(i).c.equivalent_employed_median];
+    k_equiv(i,:) = [k(i).k.equivalent_mean, k(i).k.equivalent_median, k(i).k.equivalent_unemployed_mean, k(i).k.equivalent_unemployed_median, k(i).k.equivalent_employed_mean, k(i).k.equivalent_employed_median];
+end
+output_baseline = 3.3539;
       
 figure (1)
-plot(mu', graph_var(:,1)./ output_baseline,'r', mu, graph_var(:,2)./ output_baseline,'g')
-legend('mean','median')
+plot(mu', k_equiv(:,1)./ output_baseline,'r', mu', k_equiv(:,2)./ output_baseline,'--r' ...
+    ,mu', k_equiv(:,3)./ output_baseline,'m', mu', k_equiv(:,5)./ output_baseline,'g' ...
+    ,mu', k_equiv(:,4)./ output_baseline,'--m', mu', k_equiv(:,6)./ output_baseline,'--g')
+legend('mean','median','unemployed','employed')
 xlabel('unemployment benefit')
 ylabel('cash equivalent / output')
 refline (0,0)
  
 figure (2)
-plot(mu', graph_var(:,3),'r', mu, graph_var(:,4),'g')
-legend('mean','median')
+plot(mu', c_equiv(:,1),'r', mu', c_equiv(:,2),'--r' ...
+    ,mu', c_equiv(:,3),'m', mu', c_equiv(:,5),'g' ...
[…]

### 2017-01-20 welfare_analysis.m

@@ -14,10 +14,13 @@ setup % load setup
 % you call the function. If you want to compare one steady state with the
 % default one, change parameters for i=2 and leave i=1 as the default one.
 % Do not change beta or sigma!
-mu_min = 0.05;
-mu_max = 0.8;
+mu_min = 0.01;
+mu_max = 0.6;
 mu_n = 20;
 mu = linspace(mu_min, mu_max, mu_n);
+mu(7) = mu(6); % the original point does not converge
+mu(6) = 0.15;
+mu(8) = 0.18;
 tic
 for i=1:2 % Get steady state utility for the model with two different parameters
     if i==1 
@@ -40,11 +43,11 @@ for i=1:2 % Get steady state utility for the model with two different parameters
             U.one.extrap(t-ceil(T/2),sim.one.e(t,:)==2) = interp1(grid.one.k, U.one.lifetime(2,:), sim.one.k(t,sim.one.e(t,:)==2), 'linear', 'extrap');
         end
     elseif i==2 
-        for ii=5:size(mu,2)
+        for ii=1:size(mu,2)
             par.mu = mu(ii)
             method.HH = 'FP'; 
             method.sim = 'simulation'; 
-            method.agg = 'bisection';
+            method.agg = 'bisectio';
             setup % refresh setup for new parameter
             [ k.two, c.two, K.two, sim.two, store.two, mat.two, grid.two ] = aiyagari_solver( par, func, method );
             U.two.guess = func.U(c.two.guess);
@@ -91,5 +94,3 @@ for i=1:2 % Get steady state utility for the model with two different parameters
     end
 end
 toc
-
-

### 2017-01-20 presentation/presentation.tex
Added first slide.
Added slides for the introduction.

--- 2017-01-19 presentation/presentation.tex
@@
 % and table of contents.
-\section{Part I}
+\section{Introduction}
 \subsection{}
-\begin{frame}{Motivation}
+\begin{frame}{The complete market framework}
   \begin{itemize}
@@
   \item {
-  Item 1
+  Results
+  }
+	\begin{enumerate}
+		\item{
+		Outcomes are efficient - there is no alternative in which all households can be made better off.
+		}
+		\item{
+		These models do not produce any inequality in well-being for identical households starting from identical positions. 
+		}
+	\end{enumerate}
+
+  \item {
+  Limitations  
+  }
+	\begin{enumerate}
+		\item{
+Unrealistic assumption of full insurance.
+		}
+		\item{
+Limitation in questions we can ask. Impossible to ask questions, where differences across people might affect macroeconomic outcomes.
+		}
+	\end{enumerate}
+
+  \end{itemize}
+
+\end{frame}
+
+\begin{frame}{Heterogeneity in models}
+  \begin{itemize}
+
+  \item {
+  Uninsured risk
+  }
+	\begin{enumerate}
+		\item{
+Introduction of idiosyncratic or uncorrelated risk among individuals.
+		}
+		\item{
+Accompanied by incomplete markets.
+		}
+		\item{
+In such an environment aggregate risk may create further differences across groups of people.
+		}
+	\end{enumerate}
+
+\item{
+Differences among decisionmakers.
 }
 
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Why these models?}
+	\begin{itemize}
+
 	\item {
-  Item 2  
+	Why the Aiyagari Model? 
+	}
+	\begin{enumerate}
+	\item {
+Allows for the study of agents' savings behavior while facing idiosyncratic risk in an incomplete market framework, where only part of the risk is covered by, for instance, public institutions. 
+	}
+	\item {
+How does the bahvior of selfinsured agents change when public insurance systems, such as UI, change? 
+	}
+	\item {
+	How do these changes in behavior in turn affect the other economic variables?
+	}
+	\item {	
+	When would agents prefer a change and when not? Do these changes affect different groups differently? 
+	}	
+	\end{enumerate}
+
+	\end{itemize}
+
+\end{frame}
+
+\begin{frame}{Why these models?}
+	\begin{itemize}
+
+	\item {
+	Why the Krussell Smith model? 
 	}
 
+	\begin{enumerate}
+
 	\item {
-  Item 3
+Aggregate shocks might affect different groups in a contrasting manner.  
+	}
+	\item {
+Helps to improve redistributional policy measures in business cycles.
+	}
+
+	\end{enumerate}
+
+	\end{itemize}
+
+\end{frame}
+
+\section{The Aiyagari Model}
+\subsection{Model Setup}
+
+\begin{frame}{Why these models?}
+	\begin{itemize}
+
+	\item {
+	Consumers 
+	}
+
+	\end{itemize}
+
+\end{frame}
+
+\subsection{Mechanics governing the model}
+
+\section{Aggregate Uncertainty}
+\subsection{}
+
+\begin{frame}{Idiosyncratic Uncertainty}
+	\begin{itemize}
+
+	\item {
+	Why the Aiyagari Model? - Explaining the 				differences from the Representative Agent Model.
+	}
+	\item {
+	Model Mechanics - How does a change in 					idiosyncratic uncertainty affect the agents' behavior?
+	}
+	\item {
+	What conclusions can we draw from such an analysis?
+	}
+	\item {
+	Where are the model's limitations?
 	}		
 	\end{itemize}
+	  \centering{\includegraphics[scale=0.30]{eq18}}
 
-  \centering{\includegraphics[scale=0.30]{eq18}}
 \end{frame}
 
-\section{Part II}
-\subsection{}
-
-\section{Part III}
-\subsection{}
-
 \end{document}

### 2017-01-21 presentation/presentation.tex
Added slides with equations from the Aiyagari Model.
First draft of the presentation, plots are still missing.

@@
 	\item {
-	Why the Krussell Smith model? 
+	Why the Krussell Smith Model? 
 	}
@@
 
-\begin{frame}{Why these models?}
+\begin{frame}{Model Equations}
 	\begin{itemize}
@@
 	\item {
-	Consumers 
+	Agents maximize utility:
 	}
+
+\[ 
+max_{\{{ c_{i,t}, k_{i,t+1} }\}_{t = 0}^{\infty}} {\mathbb{E}} \sum_{i=0}^{\infty} \beta^{t}  u(c_{i,t}) 
+\]
+ \[ 
+ c_{i,t} + k_{i,t+1} = (1 + r_{t} - \delta) k_{i,t} + w_{t} (1 - \tau_{t})  e_{i,t} + \mu w_{t} (1 - e_{i,t})
+ \]
+  \[
+  k_{i,t + 1} \geq \bar{k}
+	\]
 
@@
 
-\subsection{Mechanics governing the model}
-
-\section{Aggregate Uncertainty}
-\subsection{}
-
-\begin{frame}{Idiosyncratic Uncertainty}
+\begin{frame}{Model Equations}
 	\begin{itemize}
@@
 	\item {
-	Why the Aiyagari Model? - Explaining the 				differences from the Representative Agent Model.
+	Representative Firm maximizes profit:
+	}
+\[ 
+\underset{K_{t},L_{t}}{max} F_{t}(K_{t},L_{t}) -r_{t}K_{t} - w_{t}L_{t}
+\]
+
+	\item {
+	Government redistributes taxes from employed to unemployed in terms of benefits:
+	}
+
+\[ 
+\tau_{t}L_{t} = \mu(1-L_{t})
+\]
+
+	\end{itemize}
+
+\end{frame}
+
+\begin{frame}{System of Equations}
+
+Euler equation:
+\[ 
+c_{i,t}^{- \sigma} \geq \beta (1+r -\delta){\mathbb{E}[c_{i,t+1}^{- \sigma}}]
+\]
+Budget constraint:
+ \[ 
+ c_{i,t} + k_{i,t+1} = (1 + r_{t} - \delta) k_{i,t} + w (1 - \tau)  e_{i,t} + \mu w (1 - e_{i,t})
+ \]
+Borrowing constraint:
+  \[
+  k_{i,t + 1} \geq k_{min}
+	\]
+Factor prices:
+\[
+r = \alpha z (\tfrac{L}{K})^{1-\alpha} \ \ \ w = (1-\alpha)z (\tfrac{K}{L})^{\alpha}
+\]
+Employment and Tax rate: 
+\[
+L = \tfrac{\pi_{UE}}{\pi_{UE}+\pi_{EU}} \ \ \ \ \  \tau = \mu \tfrac{1-L}{L}
+\]
+
+\end{frame}
+
+\subsection{Mechanics governing the model}
+
+\begin{frame}{Changes in idiosyncratic risk}
+	\begin{itemize}
+
+	\item {
+	We are interested in studying the mechanics behind changes in precautionary savings. 
 	}
 	\item {
-	Model Mechanics - How does a change in 					idiosyncratic uncertainty affect the agents' behavior?
+	We thus look at different steady states corresponding to different values of $\mu$ and study the changes of the model variables.
 	}
+
+	\end{itemize}
+\end{frame}
+
+\begin{frame}{Changes in idiosyncratic risk}
+	\begin{itemize}
+
 	\item {
-	What conclusions can we draw from such an analysis?
+	First, we look at the changes in aggregates and compare them to the representative agent case.
 	}
-	\item {
-	Where are the model's limitations?
-	}		
+
 	\end{itemize}
+\end{frame}
+
+\begin{frame}{Changes in idiosyncratic risk}
+
+graph with log-deviations and aggregates 
   \centering{\includegraphics[scale=0.30]{eq18}}
@@
 
+\begin{frame}{Changes in idiosyncratic risk}
+	\begin{itemize}
+
+	\item {
+	As the unemployment insurance increases and idiosyncratic risk decreases, the aggregates decrease and approach the values of the representative agent model. 
+	}
+
+	\item {
+Hence, with an increasing $\mu$ savings tend to decrease on average.
+	}
+
+	\item {
+Looking at the distribution of capital holdings gives us an even better picture.
+	}
+
+	\end{itemize} 
+\end{frame}
+
+\begin{frame}{Changes in idiosyncratic risk}
+
+distributional plot 
+  \centering{\includegraphics[scale=0.30]{eq18}}
+
+\end{frame}
+
+\begin{frame}{Changes in idiosyncratic risk}
+
+\begin{itemize} 
+	\item {
+We saw that the policy change has a different effect on the unemployed and the employed. 
+}
+	\item {
+Hence, we will now look at the different variables, to get an even better image.
+}
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}{Changes in idiosyncratic risk}
+
+big subplot with all the variables
+  \centering{\includegraphics[scale=0.30]{eq18}}
+
+\end{frame}
+
+\begin{frame}{Changes in idiosyncratic risk}
+
+We can distinguish between different effects:
+
+	\begin{itemize}
+	\item {
+The Income-effect: On aggregate consumers will have more income as unemployed receive additional benefits
+
+	}	
+	\item {
+Tax-effect: The working are taxed to finance the unemployment benefits and to keep the government buget in balance, reducing their net-income.
+
+	}	
+	\item {
+Price effect: A reduction of individual risk by a more generous UI benefit decreases precautionary savings, and therefore reduces the aggregate capital stock.
+This will increase the interest rate and reduce the wage rate.
+	}
+
+	\end{itemize} 
+\end{frame}
+
+\begin{frame}{Changes in idiosyncratic risk}
+
+What conclusions can we draw from this?
+
+	\begin{itemize}
+	\item {
+There are diverse effects, affecting the agents' welfare in contradictory ways. Hence, we do need a different metric, in order to make qualified statements about the policy change. 
+	}	
+	\item {
+The model neglegcts certain aspects: There is no voluntary unemployment. A change in the UI does not affect the overall unemployment rate, which contradicts empirical evidence. 
+	}	
+	\item {
+Finally, it is important to note, that we only compare steady states. However, every policy change includes a transition phase, which might aversely affect the agents' welfare. 
+	}
+
+	\end{itemize} 
+\end{frame}
+
+\section{Welfare effects}
+\subsection{}
+
+\section{Aggregate risk}
+\subsection{}
+
+\section{Conclusions}
+\subsection{}
+
 \end{document}

### 2017-01-21 graph_equivalents.m
Create graphs

@@ -18,31 +18,50 @@ for i=1:mu_n
     k_equiv(i,:) = [k(i).k.equivalent_mean, k(i).k.equivalent_median, k(i).k.equivalent_unemployed_mean, k(i).k.equivalent_unemployed_median, k(i).k.equivalent_employed_mean, k(i).k.equivalent_employed_median];
 end
 output_baseline = 3.3539;
+
       
 figure (1)
-plot(mu', k_equiv(:,1)./ output_baseline,'r', mu', k_equiv(:,2)./ output_baseline,'--r' ...
-    ,mu', k_equiv(:,3)./ output_baseline,'m', mu', k_equiv(:,5)./ output_baseline,'g' ...
-    ,mu', k_equiv(:,4)./ output_baseline,'--m', mu', k_equiv(:,6)./ output_baseline,'--g')
-legend('mean','median','unemployed','employed')
+plot(mu(1:17)', k_equiv(1:17,3)./ output_baseline,'m', mu(1:17)', k_equiv(1:17,5)./ output_baseline,'g' ...
+    ,mu(1:17)', k_equiv(1:17,4)./ output_baseline,'--m', mu(1:17)', k_equiv(1:17,6)./ output_baseline,'--g')
+legend('unemployed','employed')
 xlabel('unemployment benefit')
 ylabel('cash equivalent / output')
 refline (0,0)
- 
+axis tight
+
 figure (2)
-plot(mu', c_equiv(:,1),'r', mu', c_equiv(:,2),'--r' ...
-    ,mu', c_equiv(:,3),'m', mu', c_equiv(:,5),'g' ...
+plot(mu(1:13)', k_equiv(1:13,1)./ output_baseline,'r', mu(1:13)', k_equiv(1:13,2)./ output_baseline,'--r')
+legend('mean','median')
+xlabel('unemployment benefit')
+ylabel('cash equivalent / output')
+refline (0,0)
+
+
+figure (3)
+plot(mu', c_equiv(:,3),'m', mu', c_equiv(:,5),'g' ...
     ,mu', c_equiv(:,4),'--m', mu', c_equiv(:,6),'--g')
-legend('mean','median','unemployed','employed')
+legend('unemployed','employed')
 xlabel('unemployment benefit')
 ylabel('consumption equivalent')
 refline (0,1)
- 
-% figure (3)
[…]

### 2017-01-21 welfare_analysis.m

@@ -21,6 +21,7 @@ mu = linspace(mu_min, mu_max, mu_n);
 mu(7) = mu(6); % the original point does not converge
 mu(6) = 0.15;
 mu(8) = 0.18;
+% mu(21) = 0.1425;
 tic
 for i=1:2 % Get steady state utility for the model with two different parameters
     if i==1 
@@ -43,7 +44,7 @@ for i=1:2 % Get steady state utility for the model with two different parameters
             U.one.extrap(t-ceil(T/2),sim.one.e(t,:)==2) = interp1(grid.one.k, U.one.lifetime(2,:), sim.one.k(t,sim.one.e(t,:)==2), 'linear', 'extrap');
         end
     elseif i==2 
-        for ii=1:size(mu,2)
+        for ii=9:size(mu,2)
             par.mu = mu(ii)
             method.HH = 'FP'; 
             method.sim = 'simulation'; 

### 2017-01-21 presentation/presentation.tex
Copied graphs into image folder, started ẃorking on presentation

--- 2017-01-19 presentation/presentation.tex
@@
 \subsection{}
-\begin{frame}{Motivation}
+\begin{frame}{Introduction}
+  \begin{itemize}
+
+  \item {1.}
+  \end{itemize}
+\end{frame}
+\section{Part II}
+\subsection{}
+\begin{frame}{Welfare Measurement}
+  \begin{itemize}
+  \item {
+  Which variable should we look at if we want to say consumers are better off? Output? Consumption?
+  }
+  \item {
+  We want to measure somehow whether consumer welfare increased or not.
+  }
+  \item {
+  But how to measure welfare? Can we compare the utility levels of consumers? And whose utility should we compare in a heterogeneous agent framework?
+  }
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Life-time Utility}
+  \begin{itemize}
+  \item {
+  We calculate the life-time utility of each agent when the economy is in steady state. One time before the policy change and once after the policy change.
+  }
+  \item {
+  Cannot compare two steady states directly. We need to take the transition into account.
+  }
+  \item {
+  Calculating the exact transition path is troublesome. We follow the approximation by Krussel, Mukoyama, and Sahin (2010) which takes care of the idiosyncratic transition.
+  }
+  \item {
+  Just place the agents in the first economy with their current assets into the second economy.
+  }
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Welfare Analysis}
+  \begin{itemize}
+  \item {
+  Now we can compare the utility level of the same agent before and after the policy change.
+  }
+  \item {
+  Need to come up with a way to quantify the utility differences sensibly.
+  }
+  \item {
+  We calculate a consumption and a cash equivalent of the policy change.
+  }
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Consumption Equivalent}
   \begin{itemize}
@@
   \item {
-  Item 1
-  }
-
-  \item {
-  Item 2  
-  }
-
-  \item {
-  Item 3
+  Permanent change of consumption by factor $\Delta$ that increases life-time
+  utility by same amount as policy change:
   }
   \end{itemize}
-
-  \centering{\includegraphics[scale=0.30]{eq18}}
+  \begin{equation}
+  U^{2}(e,k) = \mathbb{E}\sum_{t=0}^{\infty}\beta^{t}\frac{(c^{1}_{i,t}\Delta)^{1-\sigma}-1}{1-\sigma}\nonumber
+  \end{equation}
+  \begin{itemize}
+  \item {
+  If $ \Delta>1 $ agents prefer policy change $ (U^{2}) $, otherwise they do not want it.
+  }
+  \end{itemize}
 \end{frame}
 
-\section{Part II}
-\subsection{}
+\begin{frame}{Consumption Equivalent}
+  \centering \includegraphics[scale=5]{/cons_equiv.pdf}
+\end{frame}
 
@@
 
-\begin{frame}{Adding aggregate uncertainty}
-  \begin{itemize}
-
-  \item {
-  Aggregate uncertainty! Why?
-  }
-  \pause
-  \item {
-  Two aggregate productivity : $z \in \{ 0.99, 1.01 \}$.
-  }
-
-  \item {
-  Two unemployment states: $L \in \{ 0.1, 0.4 \}$.
-  }
-
-  \item {
-  2 transition matricies between employed and unemployed respectively in good and bad states and 1 transition matrix between good and bad state: $L \in \{ 0.1, 0.4 \}$.
-  }
-
-  \pause
-
-  \item {
-  Let's solve it!.
-  }
-
-  \end{itemize}
-
-\end{frame}
-
-\begin{frame}{Problem}
-  \begin{itemize}
-
-  \item {
-  The introduction of aggregate uncertainty makes the distribution of wealth changing over time, which is infinite dimensional object.
-  }
-
-  \item {
-  The capital distribution must be taken into account by the agents, therefore it becomes state variable.
-  }
-
-  \end{itemize}
-
-\end{frame}
-
-\begin{frame}{Solution}
-  \begin{itemize}
-
-  \item {
-  There is no solution.
-  }
-
-  \item {
-  Krusell and Smith (1997) suggest an algorithm to solve the issue by an approximation, which could be summerized as "rational adaptive expectations".
-  }
-
-  \item {
-  They assume that the agents forecast prices by using the future mean of the wealth distribution.
-  }
-
-  \item {
-  The actual forecast is made for the future mean based on previous realizations using some Least Squares technique.
-  }
-
-  \end{itemize}
-
-\end{frame}
-
-\begin{frame}{Algorithm}
-  \begin{enumerate}
-
-  \item {
-  Draw shocks.
-  }
-
-  \item {
-  Guess initial coefficients for the forcasting rule.  
-  }
-
-  \item {
-  Solve the individual problem.
-  }
-
-  \item {
-  Use the policy function to generate a sequence of capital distributions.
-  }
-
-  \item {
-  The actual forecast is made for the future mean based on previous realizations using some Least Squares technique.
-  }
-
-  \item {
-  Estimate new coefficients based on past realizations of the distribution and iterate until they converge. 
-  }
-
-  \end{enumerate}
-
-\end{frame}
-
 \end{document}

### 2017-01-22 presentation/presentation.tex
Change graph extension to eps
Tried to add plots to the presentation, did not manage.
Continue presentation
some minor changes to the content.

--- 2017-01-21 presentation/presentation.tex
@@
 \begin{frame}{Changes in idiosyncratic risk}
-
-graph with log-deviations and aggregates 
-  \centering{\includegraphics[scale=0.30]{eq18}}
+  \centering{\includegraphics[scale=0.5]{log-deviation}}
 
@@
 	\item {
-Looking at the distribution of capital holdings gives us an even better picture.
+Yet it is not clear, if unemployed and employed are affected differently. 
 	}
@@
 \begin{frame}{Changes in idiosyncratic risk}
+  \centering{\includegraphics[scale=0.5]{distribution}}
 
-distributional plot 
-  \centering{\includegraphics[scale=0.30]{eq18}}
+\end{frame}
+
+\begin{frame}{Changes in idiosyncratic risk}
+
+  \centering{\includegraphics[scale=0.5]{meanandmedian}}
 
@@
 \begin{itemize}
+
 	\item {
-We saw that the policy change has a different effect on the unemployed and the employed. 
+Generally speaking, the unemployed and employed decrease capital holdings. 
 }
 	\item {
-Hence, we will now look at the different variables, to get an even better image.
+ When UI increase, differences between unemployed and employed are reduced, however, within-group inequality increases.
 }
+	\item {
+Somewhat puzzling, at some point the $mean_{ue}$ starts to increase again.
+}
+	\item {
+There seem to be different forces operating. 
+}
+
 \end{itemize}
@@
 
-big subplot with all the variables
-  \centering{\includegraphics[scale=0.30]{eq18}}
+  \centering{\includegraphics[scale=0.30]{parameters}}
+
+\end{frame}
+
+\begin{frame}{Changes in idiosyncratic risk}
+
+  \centering{\includegraphics[scale=0.30]{parameters_sigma}}
 

### 2017-01-22 graph_equivalents.m
Include relative cash equivalent

@@ -18,7 +18,7 @@ for i=1:mu_n
     k_equiv(i,:) = [k(i).k.equivalent_mean, k(i).k.equivalent_median, k(i).k.equivalent_unemployed_mean, k(i).k.equivalent_unemployed_median, k(i).k.equivalent_employed_mean, k(i).k.equivalent_employed_median];
 end
 output_baseline = 3.3539;
-
+rel_k_equiv = k_equiv./output_baseline;
       
 figure (1)
 plot(mu(1:17)', k_equiv(1:17,3)./ output_baseline,'m', mu(1:17)', k_equiv(1:17,5)./ output_baseline,'g' ...

### 2017-01-22 presentation/presentation.tex
Added graphs to the presentation.
Need to do the summaries
Corrected size of graph in latex
First version of summaries

--- 2017-01-21 presentation/presentation.tex
@@
 \subsection{}
-\begin{frame}{Welfare Measurement}
+\begin{frame}{Welfare Analysis}
   \begin{itemize}
@@
   }
+  	\begin{itemize}
   	\item {
@@
   	}
+  	\end{itemize}
   \end{itemize}
@@
 \begin{frame}{Consumption Equivalent}
-  \centering \includegraphics[scale=5]{/cons_equiv.pdf}
+  \centering{\includegraphics[scale=0.6]{cons_equiv}}
+\end{frame}
+
+\begin{frame}{Consumption Equivalent}
+  \centering{\includegraphics[scale=0.6]{cons_equiv_unemp_emp}}
+\end{frame}
+
+\begin{frame}{Consumption Equivalent}
+  \begin{itemize}
+  \item {
+  There exists a welfare increase in the mean and in the median.
+  }
+  \item {
+  However, there is disagreement on whether to increase or decrease the unemployment benefits.
+  }
+  \item {
+  Careful: the consumption equivalent is biased towards poorer agents as relative increases for them are higher than for already high-consumption agents.
+  }
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Cash Equivalent}
+  \begin{itemize}
+  \item {
+  Transfer of $\Delta$ units of wealth in the first period
+  }
+  \end{itemize}
+
+  \begin{equation}
+  U^{2}(e,k) = U^{1}(e,k+\Delta) \nonumber
+  \end{equation}
+
+  \begin{itemize}
+  \item {
+  If $ \Delta>0 $ agents prefer the policy change $ (U^{2}) $, otherwise not.
+  }
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Cash Equivalent}
+  \centering{\includegraphics[scale=0.6]{cash_equiv}}
+\end{frame}
+
+\begin{frame}{Cash Equivalent}
+  \centering{\includegraphics[scale=0.6]{cash_equiv_unemp_emp}}
+\end{frame}
+
+\begin{frame}{Cash Equivalent}
+  \begin{itemize}
+  \item {
+  There does not exist a higher welfare state in the mean, only in the median.
+  }
+  \item {
+  If a higher welfare state existed for the mean we could redistribute wealth such that everyone would be better off. \\
+  $\rightarrow$ Pareto improvement.
+  }
+  \item {
+  One can clearly see the friction between unemployed and employed.
+  }
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Cash vs. Consumption Equivalent}
+\centering{\includegraphics[scale=0.6]{cash_cons_equiv}}
+\end{frame}
+
+\begin{frame}{Cash vs. Consumption Equivalent}
+  \begin{itemize}
+  \item {
+  Agents do not want full unemployment insurance although there is no moral hazard.
+  }
+  \item {
+  Different groups in society want different policies. We did not find a policy reform that could make everyone better off.
+  }
+  \item {
+  3
+  }
+  \end{itemize}
 \end{frame}

### 2017-01-22 presentation/presentation.tex
minor changes to presentation.

--- 2017-01-22 presentation/presentation.tex
@@
 \usepackage{breqn}
-\graphicspath{ {images/} }
+\graphicspath{ {images/Eric/} }
 \usepackage{amsmath}
@@
 
+\begin{frame}{Model overview}
+	\begin{itemize}
+
+	\item {
+	Ex ante identical individuals are subject to uninsurable idiosyncratic shocks. 
+	}
+	\item {
+Agents can interact on the asset market
+	}
+	\item {
+The model generates an endogenous distribution of wealth across consumers. 
+	}	
+	\item {
+Unlike in the stochastic representative agent model seen in the macro class, individual uncertainty does not coincide with aggregate uncertainty. 
+	}
+	\item {
+Aggregates and prices are jointly determined by the saving behavior of the collection of all hh. 
+}
+
+	\end{itemize}
+
+\end{frame}
+
 \begin{frame}{Model Equations}
@@
 \begin{frame}{Changes in idiosyncratic risk}
-  \centering{\includegraphics[scale=0.5]{log-deviation}}
+  \centering{\includegraphics[scale=0.45]{log-deviation}}
+
+\end{frame}
+
+\begin{frame}{Changes in idiosyncratic risk}
+  \centering{\includegraphics[scale=0.45]{deviations_sigma}}
 
@@
 \begin{frame}{Changes in idiosyncratic risk}
-  \centering{\includegraphics[scale=0.5]{distribution}}
+  \centering{\includegraphics[scale=0.45]{distribution}}
 
@@
 
-  \centering{\includegraphics[scale=0.5]{meanandmedian}}
+  \centering{\includegraphics[scale=0.425]{meanandmedian}}
 
@@
 
-  \centering{\includegraphics[scale=0.30]{parameters}}
+  \centering{\includegraphics[scale=0.45]{parameters}}
 
@@
 
-  \centering{\includegraphics[scale=0.30]{parameters_sigma}}
+  \centering{\includegraphics[scale=0.45]{parameters_sigma}}
 

### 2017-01-23 presentation/presentation.tex
Version2 of slides.

--- 2017-01-22 presentation/presentation.tex
@@
 % and table of contents.
-\section{Part I}
-\subsection{}
-\begin{frame}{Introduction}
+\section{Changes in idiosyncratic risk}
+
+\begin{frame}{Questions}
 	\begin{itemize}
 
-  \item {1.}
-  \end{itemize}
-\end{frame}
-\section{Part II}
-\subsection{}
-\begin{frame}{Welfare Analysis}
-  \begin{itemize}
 	\item {
-  Which variable should we look at if we want to say consumers are better off? Output? Consumption?
+	Does idiosyncratic risk matter? How do changes in such risk affect other economic variables? Are there distributional consequences?
 	}
-  \item {
-  We want to measure somehow whether consumer welfare increased or not.
-  }
-  \item {
-  But how to measure welfare? Can we compare the utility levels of consumers? And whose utility should we compare in a heterogeneous agent framework?
-  }
+
 	\end{itemize}
@@
 
-\begin{frame}{Life-time Utility}
+\begin{frame}{How do we examine these questions?}
 	\begin{itemize}
+
 	\item {
-  We calculate the life-time utility of each agent when the economy is in steady state. One time before the policy change and once after the policy change.
+	We will look at changes in the unemployment benefit. 
 	}
-  \item {
-  Cannot compare two steady states directly. We need to take the transition into account.
-  }
-  \item {
-  Calculating the exact transition path is troublesome. We follow the approximation by Krussel, Mukoyama, and Sahin (2010) which takes care of the idiosyncratic transition.
-  }
-  	\begin{itemize}
-  	\item {
-  	Just place the agents in the first economy with their current assets into the second economy.
-  	}
-  	\end{itemize}
+
 	\end{itemize}
@@
 
-\begin{frame}{Welfare Analysis}
+\subsection{The model}
+\begin{frame}{Model Summary}
 	\begin{itemize}
+
 	\item {
-  Now we can compare the utility level of the same agent before and after the policy change.
+	Ex ante identical individuals are subject to uninsurable idiosyncratic shocks. 
 	}
 	\item {
-  Need to come up with a way to quantify the utility differences sensibly.
+Agents can interact on the asset market.
 	}
 	\item {
-  We calculate a consumption and a cash equivalent of the policy change.
+The model generates an endogenous distribution of wealth across consumers. 
 	}	
+	\item {
+Aggregates and prices are jointly determined by the saving behavior of the collection of all households. 
+}
+
+	\end{itemize}
+
+\end{frame}
+
+\subsection{Changes in the unemployment insurance}
+
+\begin{frame}{Different parameters of the model}
+
+  \centering{\includegraphics[scale=0.45]{parameters}}
+
+\end{frame}
+
+\begin{frame}{Different levels of risk aversion}
+
+  \centering{\includegraphics[scale=0.45]{parameters_sigma}}
+
+\end{frame}
+
+\begin{frame}{First Observations}
+	\begin{itemize}
+
+	\item {
+	Changes in precautionary savings as a reaction to changes in idiosyncratic risk do affect aggregate variables.
+	}
+
+	\item {
+	These magnitude of these changes varies for different levels of risk aversion.
+	}
+
+		\item {
+	How do these aggregates compare to a situation with perfect insurance? 
+	}
+
+	\end{itemize}
+
+\end{frame}
+
+\begin{frame}{Comparing to complete markets}
+  \centering{\includegraphics[scale=0.45]{log-deviation}}
+
+\end{frame}
+
+\begin{frame}{Comparing to complete markets}
+	\begin{itemize}
+
+	\item {
+	As the insurance increases, the aggregates converge to the levels of the complete market economy. 
+	}
+
 	\end{itemize} 
@@
 
-\begin{frame}{Consumption Equivalent}
+\begin{frame}{Distribution of capital}
 	\begin{itemize}
@@
 	\item {
-  Permanent change of consumption by factor $\Delta$ that increases life-time
-  utility by same amount as policy change:
+These processes are driven by changes in precautionary savings reacting to changes in different levels of idiosyncratic risk. 
 	}
-  \end{itemize}
-  \begin{equation}
-  U^{2}(e,k) = \mathbb{E}\sum_{t=0}^{\infty}\beta^{t}\frac{(c^{1}_{i,t}\Delta)^{1-\sigma}-1}{1-\sigma}\nonumber
-  \end{equation}
-  \begin{itemize}
 	\item {
-  If $ \Delta>1 $ agents prefer policy change $ (U^{2}) $, otherwise they do not want it.
+Let us look at the different distributions of capital. 
 	}
+
 	\end{itemize} 
@@
 
-\begin{frame}{Consumption Equivalent}
-  \centering{\includegraphics[scale=0.6]{cons_equiv}}
+\begin{frame}{Distribution of capital}
+  \centering{\includegraphics[scale=0.45]{distribution}}
+
 \end{frame}
 
-\begin{frame}{Consumption Equivalent}
-  \centering{\includegraphics[scale=0.6]{cons_equiv_unemp_emp}}
+\begin{frame}{Concluding on the distribution}
+
+\begin{itemize}
+
+	\item {
+As precautionary savings decrease, aggregate capital decreases, thus increasing the interest rate and reducing the wage. 
+}
+	\item {
+The increase in unemployment benefits further reduces the net wage of the employed. The government has to increase income taxes to finance the higher unemployment benefits.
+}
+	\item {
+Therefore, with higher unemployment benefits the agent's income depends more on his accumulated capital than his labor or benefits income. 
+}
+	\item {
+The dispersion of the distribution therefore increases as benefits increase.
+}
+
+\end{itemize}
+
 \end{frame}
 
-\begin{frame}{Consumption Equivalent}
+\begin{frame}{Concluding the first part}
+
 	\begin{itemize}
+
 	\item {
-  There exists a welfare increase in the mean and in the median.
+Idiosyncratic risk matters: 
+Precautionary savings increase with higher uncertainty, thus increasing aggregate capital. 
 	}	
 	\item {
-  However, there is disagreement on whether to increase or decrease the unemployment benefits.
+Increasing unemployment benefits has distributional consequences. 
 	}
-  \item {
-  Careful: the consumption equivalent is biased towards poorer agents as relative increases for them are higher than for already high-consumption agents.
-  }
+
 	\end{itemize} 
@@
 
-\begin{frame}{Cash Equivalent}
-  \begin{itemize}
-  \item {
-  Transfer of $\Delta$ units of wealth in the first period
-  }
-  \end{itemize}
-
-  \begin{equation}
-  U^{2}(e,k) = U^{1}(e,k+\Delta) \nonumber
-  \end{equation}
+\begin{frame}{The limitations}
 
 	\begin{itemize}
+
 	\item {
-  If $ \Delta>0 $ agents prefer the policy change $ (U^{2}) $, otherwise not.
+Idiosyncratic risk matters: 
+Precautionary savings increase with higher uncertainty, thus increasing aggregate capital. 
 	}	
+	\item {
+Increasing unemployment benefits has distributional consequences. 
+	}
+
 	\end{itemize} 
@@
 
-\begin{frame}{Cash Equivalent}
-  \centering{\includegraphics[scale=0.6]{cash_equiv}}
-\end{frame}
+\section{Welfare effects}
+\subsection{}
 
-\begin{frame}{Cash Equivalent}
-  \centering{\includegraphics[scale=0.6]{cash_equiv_unemp_emp}}
-\end{frame}
+\section{Aggregate risk}
+\subsection{}
 
-\begin{frame}{Cash Equivalent}
-  \begin{itemize}
-  \item {
-  There does not exist a higher welfare state in the mean, only in the median.
-  }
-  \item {
-  If a higher welfare state existed for the mean we could redistribute wealth such that everyone would be better off. \\
-  $\rightarrow$ Pareto improvement.
-  }
-  \item {
-  One can clearly see the friction between unemployed and employed.
-  }
-  \end{itemize}
-\end{frame}
-
-\begin{frame}{Cash vs. Consumption Equivalent}
-\centering{\includegraphics[scale=0.6]{cash_cons_equiv}}
-\end{frame}
-
-\begin{frame}{Cash vs. Consumption Equivalent}
-  \begin{itemize}
-  \item {
-  Agents do not want full unemployment insurance although there is no moral hazard.
-  }
-  \item {
-  Different groups in society want different policies. We did not find a policy reform that could make everyone better off.
-  }
-  \item {
-  3
-  }
-  \end{itemize}
-\end{frame}
-
-\section{Part III}
+\section{Conclusions}
 \subsection{}

### 2017-01-23 consumption_equivalent.m
Add graph cons_equiv vs wealth

@@ -30,6 +30,18 @@ function [ c ] = consumption_equivalent (par, method, U, sim)
         c.equivalent_employed_mean = mean(c.equivalent_employed_mean);
         c.equivalent_employed_median = median(c.equivalent_employed_median);
         
+        
+%         [c.equivalent_unemp_sorted, sort_index_unemp] = sort(c.equivalent(end,sim.one.e(T,:)==1),'descend');
+%         [c.equivalent_emp_sorted, sort_index_emp] = sort(c.equivalent(end,sim.one.e(T,:)==2),'descend');
+%         k_unemp = sim.one.k(T,sim.one.e(T,:)==1);
+%         k_emp = sim.one.k(T,sim.one.e(T,:)==2);
+%         figure (1)
+%         plot(k_unemp(sort_index_unemp),c.equivalent_unemp_sorted,'g',k_emp(sort_index_emp),c.equivalent_emp_sorted,'r')
+%         legend('unemployed','employed')
+%         xlabel('wealth')
+%         ylabel('consumption equivalent')
+%         refline (0,1)
+        
     elseif strcmp(method.sim,'histogram')
         % to be done
         

### 2017-01-23 presentation/presentation.tex
Change
Version3
Final version without references, include moments or not?
Added wealth consumption equiv graph

--- 2017-01-22 presentation/presentation.tex
@@
   }
-  	\begin{itemize}
+  	\begin{enumerate}
   	\item {
@@
   	}
-  	\end{itemize}
+  	\end{enumerate}
   \end{itemize}
@@
 
+\begin{frame}{Consumption Equivalent vs Wealth}
+  \centering{\includegraphics[scale=0.6]{cons_equiv_wealth}}
+\end{frame}
+
 \begin{frame}{Consumption Equivalent}
+\framesubtitle{Summary}
   \begin{itemize}
@@
 \begin{frame}{Cash Equivalent}
+\framesubtitle{Summary}
   \begin{itemize}
@@
 
-\begin{frame}{Cash vs. Consumption Equivalent}
+\begin{frame}{Summary}
   \begin{itemize}
@@
   \item {
-  Different groups in society want different policies. We did not find a policy reform that could make everyone better off.
+  Different groups in society want different policies. We did not find a policy reform that could make everyone better off with certainty.
   }
   \item {
-  3
+  Of course, the model is not complete. A next step would be to endogenize the unemployment rate such that it reacts to changes in unemployment benefits.
   }

### 2017-01-23 presentation/presentation.tex
Fixed typo.

--- 2017-01-23 presentation/presentation.tex
@@
 	\item {
-	Changes in precautionary savings as a reaction to changes in idiosyncratic risk do affect aggregate variables.
+	Changes in idiosyncratic risk do affect aggregate variables.
 	}
@@
 \begin{frame}{Distribution of capital}
-  \centering{\includegraphics[scale=0.45]{distribution}}
+
+\begin{figure}[!tbp]
+  \centering
+  \begin{minipage}[b]{0.32\textwidth}
+    \includegraphics[width=\textwidth]{distribution1}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[b]{0.32\textwidth}
+    \includegraphics[width=\textwidth]{distribution2}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[b]{0.32\textwidth}
+    \includegraphics[width=\textwidth]{distribution3}
+  \end{minipage}
+\end{figure}
+\ \ \ \ \ \ \  rw = 0.01 \ \ \ \ \ \ \ \ \ \ \ \ rw = 0.42579 \ \ \ \ \ \ \ \ \ \ \ \ \ rw = 0.8
+\end{frame}
+
+\begin{frame}{Moments Employed}
+
+\centering
+\begin{tabular}{l*{6}{c}r}
+UI             & Mean & Median & Std & Skewness\\
+\hline
+Low 			& 22.24 & 22.56 & 14.97 & 1.31\\
+Medium         & 17.94 & 17.60 & 17.68 & 1.41\\
+High          & 17.41 & 15.73 & 18.07 & 1.41 \\
+\end{tabular}
+
+\end{frame}
+
+\begin{frame}{Moments Unemployed}
+
+\centering	
+\begin{tabular}{l*{6}{c}r}
+UI             & Mean & Median & Std & Skewness\\
+\hline
+Low 			& 20.35 & 20.60 & 16.08 & 1.39\\
+Medium         & 16.88 & 16.56 & 18.45 & 1.41\\
+High          & 17.17 & 15.51 & 18.23 & 1.41 \\
+\end{tabular}
 
@@
 
-	\item {
-Idiosyncratic risk matters: 
-Precautionary savings increase with higher uncertainty, thus increasing aggregate capital. 
+	\item {The model's labor supply is exogenous. Thus, changing the unemployment benefits has no impact on labor supply or the transition probabilities.
 }	
-	\item {
-Increasing unemployment benefits has distributional consequences. 
+	\item {This contradicts empirical evidence: Decker(1997).
+	}
+	\item{Endogenous labor matters: Mukoyama(2012).
 	}

### 2017-01-23 presentation/presentation.tex
Final version.

@@
 	\item {
-	These magnitude of these changes varies for different levels of risk aversion.
+	The magnitude of impact varies for different levels of risk aversion.
 	}
@@
 		\item {
-	How do these aggregates compare to a situation with perfect insurance? 
+	How do the different levels of the aggregates compare to a situation with perfect insurance? 
 	}
@@
 \begin{frame}{Distribution of capital}
-	\begin{itemize}
-
-	\item {
-These processes are driven by changes in precautionary savings reacting to changes in different levels of idiosyncratic risk. 
-	}
-	\item {
-Let us look at the different distributions of capital. 
-	}
-
-	\end{itemize} 
-\end{frame}
-
-\begin{frame}{Distribution of capital}
 
@@
   \centering
-  \begin{minipage}[b]{0.32\textwidth}
+  \begin{minipage}[b]{0.325\textwidth}
     \includegraphics[width=\textwidth]{distribution1}
@@
   \hfill
-  \begin{minipage}[b]{0.32\textwidth}
+  \begin{minipage}[b]{0.325\textwidth}
     \includegraphics[width=\textwidth]{distribution2}
@@
   \hfill
-  \begin{minipage}[b]{0.32\textwidth}
+  \begin{minipage}[b]{0.325\textwidth}
     \includegraphics[width=\textwidth]{distribution3}
@@
 \ \ \ \ \ \ \  rw = 0.01 \ \ \ \ \ \ \ \ \ \ \ \ rw = 0.42579 \ \ \ \ \ \ \ \ \ \ \ \ \ rw = 0.8
-\end{frame}
-
-\begin{frame}{Moments Employed}
-
-\centering
-\begin{tabular}{l*{6}{c}r}
-UI             & Mean & Median & Std & Skewness\\
-\hline
-Low 			& 22.24 & 22.56 & 14.97 & 1.31\\
-Medium         & 17.94 & 17.60 & 17.68 & 1.41\\
-High          & 17.41 & 15.73 & 18.07 & 1.41 \\
-\end{tabular}
-
-\end{frame}
-
-\begin{frame}{Moments Unemployed}
-
-\centering	
-\begin{tabular}{l*{6}{c}r}
-UI             & Mean & Median & Std & Skewness\\
-\hline
-Low 			& 20.35 & 20.60 & 16.08 & 1.39\\
-Medium         & 16.88 & 16.56 & 18.45 & 1.41\\
-High          & 17.17 & 15.51 & 18.23 & 1.41 \\
-\end{tabular}
-
 \end{frame}

### 2017-01-24 presentation/presentation.tex
Final Version 2

@@
 	\item {
-	Does idiosyncratic risk matter? How do changes in such risk affect other economic variables? Are there distributional consequences?
+How do changes in idisynratic risk affect other economic variables in the long run? How do these results compare to an economy with perfect markets? Are there distributional consequences?
 	}
@@
 \end{figure}
-\ \ \ \ \ \ \  rw = 0.01 \ \ \ \ \ \ \ \ \ \ \ \ rw = 0.42579 \ \ \ \ \ \ \ \ \ \ \ \ \ rw = 0.8
+\ \ \ \ \ \ \  UI = 0.01 \ \ \ \ \ \ \ \ \ \ \ \ UI = 0.42579 \ \ \ \ \ \ \ \ \ \ \ \ \ UI = 0.8
 \end{frame}
@@
 	\item {
-Idiosyncratic risk matters: 
-Precautionary savings increase with higher uncertainty, thus increasing aggregate capital. 
+The presence of idiosyncratic risk leads to higher aggregate capital. 
+	}
+		\item {
+A model with idiosyncratic risk allows for the study of distributional questions.
 	}	

### 2017-01-24 presentation/presentation.tex
Include reference

--- 2017-01-23 presentation/presentation.tex
@@
 \usepackage{breqn}
-\graphicspath{ {images/Eric/} }
+\graphicspath{ {images/} }
 \usepackage{amsmath}
@@
 % and table of contents.
-\section{Changes in idiosyncratic risk}
+\section{Part I}
+\subsection{}
+\begin{frame}{Introduction}
+  \begin{itemize}
 
-\begin{frame}{Questions}
+  \item {1.}
+  \end{itemize}
+\end{frame}
+\section{Part II}
+\subsection{}
+\begin{frame}{Welfare Analysis}
+  \begin{itemize}
+  \item {
+  Which variable should we look at if we want to say consumers are better off? Output? Consumption?
+  }
+  \item {
+  We want to measure somehow whether consumer welfare increased or not.
+  }
+  \item {
+  But how to measure welfare? Can we compare the utility levels of consumers? And whose utility should we compare in a heterogeneous agent framework?
+  }
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Life-time Utility}
+  \begin{itemize}
+  \item {
+  We calculate the life-time utility of each agent when the economy is in steady state. One time before the policy change and once after the policy change.
+  }
+  \item {
+  Cannot compare two steady states directly. We need to take the transition into account.
+  }
+  \item {
+  Calculating the exact transition path is troublesome. We follow the approximation by \cite{KMS2010} which takes care of the idiosyncratic transition.
+  }
+  	\begin{enumerate}
+  	\item {
+  	Just place the agents in the first economy with their current assets into the second economy.
+  	}
+  	\end{enumerate}
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Welfare Analysis}
+  \begin{itemize}
+  \item {
+  Now we can compare the utility level of the same agent before and after the policy change.
+  }
+  \item {
+  Need to come up with a way to quantify the utility differences sensibly.
+  }
+  \item {
+  We calculate a consumption and a cash equivalent of the policy change.
+  }
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Consumption Equivalent}
   \begin{itemize}
@@
   \item {
-	Does idiosyncratic risk matter? How do changes in such risk affect other economic variables? Are there distributional consequences?
+  Permanent change of consumption by factor $\Delta$ that increases life-time
+  utility by same amount as policy change:
   }
-
+  \end{itemize}
+  \begin{equation}
+  U^{2}(e,k) = \mathbb{E}\sum_{t=0}^{\infty}\beta^{t}\frac{(c^{1}_{i,t}\Delta)^{1-\sigma}-1}{1-\sigma}\nonumber
+  \end{equation}
+  \begin{itemize}
+  \item {
+  If $ \Delta>1 $ agents prefer policy change $ (U^{2}) $, otherwise they do not want it.
+  }
   \end{itemize}
@@
 
-\begin{frame}{How do we examine these questions?}
+\begin{frame}{Consumption Equivalent}
+  \centering{\includegraphics[scale=0.6]{cons_equiv}}
+\end{frame}
+
+\begin{frame}{Consumption Equivalent}
+  \centering{\includegraphics[scale=0.6]{cons_equiv_unemp_emp}}
+\end{frame}
+
+\begin{frame}{Consumption Equivalent vs Wealth}
+  \centering{\includegraphics[scale=0.6]{cons_equiv_wealth}}
+\end{frame}
+
+\begin{frame}{Consumption Equivalent}
+\framesubtitle{Summary}
   \begin{itemize}
-
   \item {
-	We will look at changes in the unemployment benefit. 
+  There exists a welfare increase in the mean and in the median.
   }
-
+  \item {
+  However, there is disagreement on whether to increase or decrease the unemployment benefits.
+  }
+  \item {
+  Careful: the consumption equivalent is biased towards poorer agents as relative increases for them are higher than for already high-consumption agents.
+  }
   \end{itemize}
@@
 
-\subsection{The model}
-\begin{frame}{Model Summary}
+\begin{frame}{Cash Equivalent}
   \begin{itemize}
-
   \item {
-	Ex ante identical individuals are subject to uninsurable idiosyncratic shocks. 
+  Transfer of $\Delta$ units of wealth in the first period
   }
-	\item {
-Agents can interact on the asset market.
-	}
-	\item {
-The model generates an endogenous distribution of wealth across consumers. 
-	}	
-	\item {
-Aggregates and prices are jointly determined by the saving behavior of the collection of all households. 
-}
-
   \end{itemize}
 
-\end{frame}
+  \begin{equation}
+  U^{2}(e,k) = U^{1}(e,k+\Delta) \nonumber
+  \end{equation}
 
-\subsection{Changes in the unemployment insurance}
-
-\begin{frame}{Different parameters of the model}
-
-  \centering{\includegraphics[scale=0.45]{parameters}}
-
-\end{frame}
-
-\begin{frame}{Different levels of risk aversion}
-
-  \centering{\includegraphics[scale=0.45]{parameters_sigma}}
-
-\end{frame}
-
-\begin{frame}{First Observations}
   \begin{itemize}
-
   \item {
-	Changes in idiosyncratic risk do affect aggregate variables.
+  If $ \Delta>0 $ agents prefer the policy change $ (U^{2}) $, otherwise not.
   }
-
-	\item {
-	The magnitude of impact varies for different levels of risk aversion.
-	}
-
-		\item {
-	How do the different levels of the aggregates compare to a situation with perfect insurance? 
-	}
-
-	\end{itemize}
-
-\end{frame}
-
-\begin{frame}{Comparing to complete markets}
-  \centering{\includegraphics[scale=0.45]{log-deviation}}
-
-\end{frame}
-
-\begin{frame}{Comparing to complete markets}
-	\begin{itemize}
-
-	\item {
-	As the insurance increases, the aggregates converge to the levels of the complete market economy. 
-	}
-
   \end{itemize}
@@
 
-\begin{frame}{Distribution of capital}
-
-\begin{figure}[!tbp]
-  \centering
-  \begin{minipage}[b]{0.325\textwidth}
-    \includegraphics[width=\textwidth]{distribution1}
-  \end{minipage}
-  \hfill
-  \begin{minipage}[b]{0.325\textwidth}
-    \includegraphics[width=\textwidth]{distribution2}
-  \end{minipage}
-  \hfill
-  \begin{minipage}[b]{0.325\textwidth}
-    \includegraphics[width=\textwidth]{distribution3}
-  \end{minipage}
-\end{figure}
-\ \ \ \ \ \ \  rw = 0.01 \ \ \ \ \ \ \ \ \ \ \ \ rw = 0.42579 \ \ \ \ \ \ \ \ \ \ \ \ \ rw = 0.8
+\begin{frame}{Cash Equivalent}
+  \centering{\includegraphics[scale=0.6]{cash_equiv}}
 \end{frame}
 
-\begin{frame}{Concluding on the distribution}
+\begin{frame}{Cash Equivalent}
+  \centering{\includegraphics[scale=0.6]{cash_equiv_unemp_emp}}
+\end{frame}
 
+\begin{frame}{Cash Equivalent}
+\framesubtitle{Summary}
   \begin{itemize}
-
   \item {
-As precautionary savings decrease, aggregate capital decreases, thus increasing the interest rate and reducing the wage. 
+  There does not exist a higher welfare state in the mean, only in the median.
   }
   \item {
-The increase in unemployment benefits further reduces the net wage of the employed. The government has to increase income taxes to finance the higher unemployment benefits.
+  If a higher welfare state existed for the mean we could redistribute wealth such that everyone would be better off. \\
+  $\rightarrow$ Pareto improvement.
   }
   \item {
-Therefore, with higher unemployment benefits the agent's income depends more on his accumulated capital than his labor or benefits income. 
+  One can clearly see the friction between unemployed and employed.
   }
-	\item {
-The dispersion of the distribution therefore increases as benefits increase.
-}
-
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}{Concluding the first part}
-
-	\begin{itemize}
-
-	\item {
-Idiosyncratic risk matters: 
-Precautionary savings increase with higher uncertainty, thus increasing aggregate capital. 
-	}	
-	\item {
-Increasing unemployment benefits has distributional consequences. 
-	}
-
   \end{itemize}
@@
 
-\begin{frame}{The limitations}
+\begin{frame}{Cash vs. Consumption Equivalent}
+\centering{\includegraphics[scale=0.6]{cash_cons_equiv}}
+\end{frame}
 
+\begin{frame}{Summary}
   \begin{itemize}
-
-	\item {The model's labor supply is exogenous. Thus, changing the unemployment benefits has no impact on labor supply or the transition probabilities.
+  \item {
+  Agents do not want full unemployment insurance although there is no moral hazard.
   }
-	\item {This contradicts empirical evidence: Decker(1997).
+  \item {
+  Different groups in society want different policies. We did not find a policy reform that could make everyone better off with certainty.
   }
-	\item{Endogenous labor matters: Mukoyama(2012).
+  \item {
+  Of course, the model is not complete. A next step would be to endogenize the unemployment rate such that it reacts to changes in unemployment benefits.
   }
-
   \end{itemize}
@@
 
-\section{Welfare effects}
-\subsection{}
-
-\section{Aggregate risk}
-\subsection{}
-
-\section{Conclusions}
+\section{Part III}
 \subsection{}

### 2017-01-24 presentation/presentation.tex
Combined presentation

@@
 \usepackage{breqn}
-\graphicspath{ {images/} }
+\graphicspath{ {./images/} }
 \usepackage{amsmath}
 \usepackage{dsfont}
+\usepackage{ wasysym }
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
+\usepackage[backend=biber]{biblatex}
+\bibliography{pres.bib}
+
 % There are many different themes available for Beamer. A comprehensive
@@
 % and table of contents.
-\section{Part I}
+\section{Idiosyncratic risk}
 \subsection{}
-\begin{frame}{Introduction}
+\begin{frame}{Questions}
   \begin{itemize}
 
-  \item {1.}
+  \item {
+How do changes in idiosynratic risk affect other economic variables in the long run? How do these results compare to an economy with complete markets? Are there distributional consequences?
+  }
+
+  \pause
+
+  \item {
+  We will look at changes in the unemployment benefit. 
+  }
+
   \end{itemize}
 \end{frame}
-\section{Part II}
+
+\begin{frame}{Model Summary}
+  \begin{itemize}
+
+  \item {
+  Ex ante identical individuals are subject to uninsurable idiosyncratic shocks. 
+  }
+  \item {
+Agents can interact on the asset market.
+  }
+  \item {
+The model generates an endogenous distribution of wealth across consumers. 
+  } 
+  \item {
+Aggregates and prices are jointly determined by the saving behavior of the collection of all households. 
+}
+
+  \end{itemize}
+
+\end{frame}
+
+\begin{frame}{Different parameters of the model}
+
+  \centering{\includegraphics[scale=0.45]{parameters}}
+
+\end{frame}
+
+\begin{frame}{Different levels of risk aversion}
+
+  \centering{\includegraphics[scale=0.45]{parameters_sigma}}
+
+\end{frame}
+
+\begin{frame}{First Observations}
+  \begin{itemize}
+
+  \item {
+  Changes in idiosyncratic risk do affect aggregate variables.
+  }
+
+  \item {
+  The magnitude of impact varies for different levels of risk aversion.
+  }
+
+    \item {
+  How do the different levels of the aggregates compare to a situation with perfect insurance? 
+  }
+
+  \end{itemize}
+
+\end{frame}
+
+\begin{frame}{Comparing to complete markets}
+  \centering{\includegraphics[scale=0.45]{log-deviation}}
+
+\end{frame}
+
+\begin{frame}{Comparing to complete markets}
+  \begin{itemize}
+
+  \item {
+  As the insurance increases, the aggregates converge to the levels of the complete market economy. 
+  }
+
+  \end{itemize} 
+\end{frame}
+
+\begin{frame}{Distribution of capital}
+
+\begin{figure}[!tbp]
+  \centering
+  \begin{minipage}[b]{0.325\textwidth}
+    \includegraphics[width=\textwidth]{distribution1}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[b]{0.325\textwidth}
+    \includegraphics[width=\textwidth]{distribution2}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[b]{0.325\textwidth}
+    \includegraphics[width=\textwidth]{distribution3}
+  \end{minipage}
+\end{figure}
+\ \ \ \ \ \ \  UI = 0.01 \ \ \ \ \ \ \ \ \ \ \ \ UI = 0.42579 \ \ \ \ \ \ \ \ \ \ \ \ \ UI = 0.8
+\end{frame}
+
+\begin{frame}{Concluding on the distribution}
+
+\begin{itemize}
+
+  \item {
+As precautionary savings decrease, aggregate capital decreases, thus increasing the interest rate and reducing the wage. 
+}
+  \item {
+The increase in unemployment benefits further reduces the net wage of the employed. The government has to increase income taxes to finance the higher unemployment benefits.
+}
+  \item {
+Therefore, with higher unemployment benefits the agent's income depends more on his accumulated capital than his labor or benefits income. 
+}
+  \item {
+The dispersion of the distribution therefore increases as benefits increase.
+}
+
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}{Concluding the first part}
+
+  \begin{itemize}
+
+  \item {
+The presence of idiosyncratic risk leads to higher aggregate capital. 
+  }
+    \item {
+A model with idiosyncratic risk allows for the study of distributional questions.
+  } 
+  \item {
+Increasing unemployment benefits has distributional consequences. 
+  }
+
+  \end{itemize} 
+\end{frame}
+
+\begin{frame}{The limitations}
+
+  \begin{itemize}
+
+  \item {The model's labor supply is exogenous. Thus, changing the unemployment benefits has no impact on labor supply or the transition probabilities.
+} 
+  \item {This contradicts empirical evidence: \citeauthor{decker} \cite{decker}.
+  }
+  \item{Endogenous labor matters: \citeauthor{mukoyama} \cite{mukoyama}.
+  }
+
+  \end{itemize} 
+\end{frame}
+
+\section{Welfare analysis of unemployment benefits}
 \subsection{}
@@
   \item {
-  Calculating the exact transition path is troublesome. We follow the approximation by \cite{KMS2010} which takes care of the idiosyncratic transition.
+  Calculating the exact transition path is troublesome. We follow the approximation by \citeauthor{sahin} \cite{sahin} which takes care of the idiosyncratic transition.
   }
@@
 
-\section{Part III}
-\subsection{}
+\section{Aggregate uncertainty}
+\subsection{The cost of the business cycle}
+
+\begin{frame}{Adding Aggregate uncertainty}
+  \begin{itemize}
+
+  \item {
+  Aggregate uncertainty! Why?
+  }
+
+  \pause
+
+  \item {
+   Two productivity states: $z_t \in \{ 0.99, 1.01\}$.
+  }
+
+  \item {
+  Two unemployment states. $U \in \{0.1, 0.04\}$.
+  }
+
+  \item {
+  3 transition matricies.
+  }
+
+ \end{itemize}
+
+\end{frame}
+
+\begin{frame}{Problem}
+  \begin{itemize}
+
+  \item {
+  The introduction of aggregate uncertainty makes the distribution of wealth changing over time, which is infinite dimensional object.
+  }
+
+  \item {
+  The capital distribution must be taken into account by the agents, therefore it becomes state variable.  
+  }
+
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Solution}
+  \begin{itemize}
+
+  \item {
+  There is no exact solution.
+  }
+
+  \item {
+  \citeauthor{krussel_smith97} \cite{krussel_smith97} suggest an algorithm to solve the issue by an approximation, which could be summerized as ”rational adaptive expectations”.  
+  }
+
+  \item {
+  They assume that the agents forecast prices by using the future mean of the wealth distribution.  
+  }
+
+  \item {
+  The actual forecast is made for the future mean based on previous realizations using some Least Squares technique.  
+  }
+
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Algorithm}
+  \begin{enumerate}
+    \item {
+    Draw shocks.  
+    }
+
+    \item {
+    Guess initial coefficients for the forecasting rule.  
+    }
+
+    \item {
+    Solve the individual problem.  
+    }
+
+    \item {
+    Simulate the economy and take the sequence of the distributions.  
+    }
+
+    \item {
+    Estimate new coefficients based on past realizations of the distribution and iterate until they converge. 
+    }
+
+  \end{enumerate}
+   \pause
+    Solution based on \citeauthor{soft} \cite{soft}.
+
+\end{frame}
+
+\begin{frame}{Results}
+  \begin{itemize}
+    \item {
+    When it is solved you obtain the final sequence of capital distributions implied by the individual policy function.
+    }
+
+    \item {
+    Use the coefficients of the regression to see if the forecasts coincide.
+    }
+
+  \end{itemize}
+
+ \textrm{Good state forecast:}  \\
+  \[ \ln{K_t} = 0.09 + 0.97\ln{K_{t-1}}; R^2 = 0.99 \]\\
+\textrm{Bad state forecast:} \\
+  \[ \ln{K_t} = 0.10 + 0.97\ln{K_{t-1}}; R^2 = 0.99 \]
+
+\end{frame}
+
+\begin{frame}{Aggregate uncertainty}
+\centering{\includegraphics[width=12cm,height=7cm, keepaspectratio]{fig1}}
+\end{frame}
+
+\begin{frame}{Welfare loss of the business cycle}
+  \begin{itemize}
+
+  \item {
+  Surpress Krussel - Smith algorithm such that the economy is initialy at the middle between good and bad state.
+i.
+e.
+$z = 1, U = 0.07$ and the probability of being employed next period is equal to the half in the 2 aggregate states.
+  }
+
+  \item {
+  Check if it converges to the steady state starting from a random and much higher aggregate demand level.  
+  }
+
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Welfare loss of the business cycle}{Convergence to steady state}
+\centering{\includegraphics[width=12cm,height=6cm,keepaspectratio]{fig2}}
+\end{frame}
+
+\begin{frame}{Wellfare loss of the business cycle}{Calculate lifetime utilities}
+  \begin{itemize}
+
+  \item {
+  Solve the individual problem and the life-time utility for steady state. Calculate its value for all the consumers.
+  }
+
+  \item {
+  Take the ergodic distribution and put it in aggregate economy framework. Solve the individual problem and caluclate the \textbf{EXPECTED} lifetime utility. 
+  }
+
+  \[\textrm{Compare: }U^1(k_i, e_i) \textrm{ and } \mathbb{E}U^2(e_i, k_i, K^{ss}, z)\]
+
+  \item {
+  Calculate the consumption equivalent.  
+  }
+
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Results}
+  \begin{itemize}
+
+  \item {
+  The median consumption equvalent is: 0.1603\%.
+  }
+
+  \item {
+  The median personal disposable income for 2015 is \$30,240 (U.S. Bureau of the Census).
+  }
+
+  \item {
+  The consumers would give up to \$48.47 per year or 13 $\cent$ per day to eliminate the business cycle.
+  }
+
+  \item {
+  Similar results to \citeauthor{ks_99} \cite{ks_99}. 
+  }
+
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Winners and losers from the business cycle}
+\centering{\includegraphics[width=40cm,height=6.5cm,keepaspectratio]{cons_equiv_agg}}
+\end{frame}
+
+\subsection{Numerical problems}
+
+\begin{frame}{Another application}{Transition between two steady states for 10k individuals}
+\centering{\includegraphics[width=12cm,height=6cm,keepaspectratio]{fig3}}
+\end{frame}
+
+\begin{frame}{Another application}{Transition between two steady states for 100k individuals}
+\centering{\includegraphics[width=12cm,height=6cm,keepaspectratio]{fig4}}
+\end{frame}
+
+\begin{frame}{Another application}{Transition between two steady states for histogram method}
+\centering{\includegraphics[width=12cm,height=6cm,keepaspectratio]{fig5}}
+\end{frame}
+
+\begin{frame}{Numerical problems and solutions}
+  \begin{itemize}
+
+  \item {
+  How to calibrate?
+  }
+
+  \item {
+  How to choose state space?
+
+  \begin{itemize}
+    \item Boundaries
+    \item {
+    Precision  
+    }
+    \item {
+    Position  
+    }
+  \end{itemize}
+
+  }
+
+  \item {
+  How to solve the individual problem? Trade off between accuracy and speed.  
+  }
+
+  \item {
+  How to find the root?  
+  }
+
+  \item {
+  How to find the ergodic distribution?  
+  }
+
+  \end{itemize}
+\end{frame}
+
+\section{Conclusion}
+\begin{frame}{Conclusion}
+  \begin{enumerate}
+
+  \item {
+  Government policies could influece the society significantly!
+  }
+
+  \item {
+  There is no pareto improvement!
+  }
+
+  \item {
+  Aggregate uncertainty doesn't matter much!
+  }
+
+  \end{enumerate}
+\end{frame}
+
+\appendix
+
+\begin{frame}[allowframebreaks]{References}
+
+\printbibliography
+\end{frame}
 

### 2017-01-24 presentation/presentation.tex
Final at the Cafe

@@
 
-\title{Effects of Unemployment Benefits and Uncertainty in Heterogeneous Models}
+\title{Effects of Uncertainty in Heterogeneous Models}
 
@@
 
-%\date{Conference Name, 2013}
+\date{Project Module, 25.01.2017}
 % - Either use conference name or its abbreviation.
@@
 
-\begin{frame}{First Observations}
+\begin{frame}{Comparing to complete markets}
   \begin{itemize}
-
-  \item {
-  Changes in idiosyncratic risk do affect aggregate variables.
-  }
-
-  \item {
-  The magnitude of impact varies for different levels of risk aversion.
-  }
 
@@
 \end{figure}
-\ \ \ \ \ \ \  UI = 0.01 \ \ \ \ \ \ \ \ \ \ \ \ UI = 0.42579 \ \ \ \ \ \ \ \ \ \ \ \ \ UI = 0.8
-\end{frame}
-
-\begin{frame}{Concluding on the distribution}
-
-\begin{itemize}
-
-  \item {
-As precautionary savings decrease, aggregate capital decreases, thus increasing the interest rate and reducing the wage. 
-}
-  \item {
-The increase in unemployment benefits further reduces the net wage of the employed. The government has to increase income taxes to finance the higher unemployment benefits.
-}
-  \item {
-Therefore, with higher unemployment benefits the agent's income depends more on his accumulated capital than his labor or benefits income. 
-}
-  \item {
-The dispersion of the distribution therefore increases as benefits increase.
-}
-
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}{Concluding the first part}
-
-  \begin{itemize}
-
-  \item {
-The presence of idiosyncratic risk leads to higher aggregate capital. 
-  }
-    \item {
-A model with idiosyncratic risk allows for the study of distributional questions.
-  } 
-  \item {
-Increasing unemployment benefits has distributional consequences. 
-  }
-
-  \end{itemize} 
+\ \ \ \ \ \ \  UI = 0.01 \ \ \ \ \ \ \ \ \ \ \ \ UI = 0.40 \ \ \ \ \ \ \ \ \ \ \ \ \ UI = 0.8
 \end{frame}
@@
   \item{Endogenous labor matters: \citeauthor{mukoyama} \cite{mukoyama}.
+  }
+
+  \end{itemize} 
+\end{frame}
+
+\begin{frame}{Summary}
+
+  \begin{itemize}
+
+  \item {
+Idiosyncratic risk affects aggregate variables.
+  }
+
+    \item {
+Increasing unemployment benefits has distributional consequences. 
+  }
+
+\item {
+Welfare implications are unclear.
 }
@@
   }
-    \begin{enumerate}
+    \begin{itemize}
     \item {
@@
     }
-    \end{enumerate}
+    \end{itemize}
   \end{itemize}
@@
 
-\begin{frame}{Consumption Equivalent}
-  \centering{\includegraphics[scale=0.6]{cons_equiv_unemp_emp}}
-\end{frame}
-
 \begin{frame}{Consumption Equivalent vs Wealth}
@@
 \begin{frame}{Consumption Equivalent}
-\framesubtitle{Summary}
   \begin{itemize}
+
   \item {
-  There exists a welfare increase in the mean and in the median.
-  }
-  \item {
-  However, there is disagreement on whether to increase or decrease the unemployment benefits.
-  }
-  \item {
-  Careful: the consumption equivalent is biased towards poorer agents as relative increases for them are higher than for already high-consumption agents.
+  The consumption equivalent is biased towards poorer agents as relative increases for them are higher than for already-high consumption agents. Therefore, we need another measure.
   }
@@
   \centering{\includegraphics[scale=0.6]{cash_equiv_unemp_emp}}
-\end{frame}
-
-\begin{frame}{Cash Equivalent}
-\framesubtitle{Summary}
-  \begin{itemize}
-  \item {
-  There does not exist a higher welfare state in the mean, only in the median.
-  }
-  \item {
-  If a higher welfare state existed for the mean we could redistribute wealth such that everyone would be better off. \\
-  $\rightarrow$ Pareto improvement.
-  }
-  \item {
-  One can clearly see the friction between unemployed and employed.
-  }
-  \end{itemize}
-\end{frame}
-
-\begin{frame}{Cash vs. Consumption Equivalent}
-\centering{\includegraphics[scale=0.6]{cash_cons_equiv}}
 \end{frame}
@@
 
-  \item {
-  3 transition matricies.
-  }
-
  \end{itemize}
@@
   \item {
-  The introduction of aggregate uncertainty makes the distribution of wealth changing over time, which is infinite dimensional object.
+  The introduction of aggregate uncertainty makes the distribution of wealth changing over time, which is an infinite dimensional object.
   }
@@
   \item {
-  The capital distribution must be taken into account by the agents, therefore it becomes state variable.  
+  The capital distribution must be taken into account by the agents, therefore it becomes a state variable.  
   }
@@
   \item {
-  \citeauthor{krussel_smith97} \cite{krussel_smith97} suggest an algorithm to solve the issue by an approximation, which could be summerized as ”rational adaptive expectations”.  
+  \citeauthor{krussel_smith97} \cite{krussel_smith97} suggested an algorithm to solve the issue by an approximation.  
   }
@@
   Surpress Krussel - Smith algorithm such that the economy is initialy at the middle between good and bad state.
-i.
-e.
-$z = 1, U = 0.07$ and the probability of being employed next period is equal to the half in the 2 aggregate states.
   }
@@
 
-\begin{frame}{Wellfare loss of the business cycle}{Calculate lifetime utilities}
+\begin{frame}{Welfare loss of the business cycle}{Calculate lifetime utilities}
   \begin{itemize}
@@
   \item {
-  Take the ergodic distribution and put it in aggregate economy framework. Solve the individual problem and caluclate the \textbf{EXPECTED} lifetime utility. 
+  Take the ergodic distribution and put it in aggregate economy framework. Solve the individual problem and calculate the \textbf{EXPECTED} lifetime utility. 
   }
 
-  \[\textrm{Compare: }U^1(k_i, e_i) \textrm{ and } \mathbb{E}U^2(e_i, k_i, K^{ss}, z)\]
+  \[\textrm{Compare: }U^1(k_i, e_i) \textrm{ and } \mathbb{E}U^2(k_i, e_i, K^{ss}, z)\]
 
@@
   \item {
-  The median consumption equvalent is: 0.1603\%.
+  The median consumption equivalent is: 0.1603\%.
   }
@@
   \item {
-  How to solve the individual problem? Trade off between accuracy and speed.  
-  }
-
-  \item {
-  How to find the root?  
+  How to solve the individual problem?  
   }
@@
   \item {
-  Government policies could influece the society significantly!
+  Government policies could influece the economy significantly!
   }
@@
   \item {
-  There is no pareto improvement!
+  There is no Pareto improvement!
   }

### 2017-01-24 presentation/presentation.tex
Changing the problem slide

@@
   \item {
-  The introduction of aggregate uncertainty makes the distribution of wealth changing over time, which is an infinite dimensional object.
+  The introduction of aggregate uncertainty makes the distribution of wealth changing over time.
   }
@@
   \item {
-  The capital distribution must be taken into account by the agents, therefore it becomes a state variable.  
+  The capital distribution must be taken into account by the agents.  
   }

### 2017-01-24 presentation/presentation.tex
4th section
Change titles
Change policy change
Changing Yannics title
remove the
of KS added

@@
 
-\section{Welfare analysis of unemployment benefits}
+\section{Optimal unemployment benefit}
 \subsection{}
@@
 
-\section{Aggregate uncertainty}
-\subsection{The cost of the business cycle}
+\section{Business cycle costs}
+\subsection{}
 
@@
 
-\subsection{Numerical problems}
-
-\begin{frame}{Another application}{Transition between two steady states for 10k individuals}
+\section{Numerical problems}
+\subsection{}
+\begin{frame}{Another application of Krussel - Smith}{Transition between two steady states for 10k individuals}
 \centering{\includegraphics[width=12cm,height=6cm,keepaspectratio]{fig3}}
@@
 
-\begin{frame}{Another application}{Transition between two steady states for 100k individuals}
+\begin{frame}{Another application of Krussel - Smith}{Transition between two steady states for 100k individuals}
 \centering{\includegraphics[width=12cm,height=6cm,keepaspectratio]{fig4}}
@@
 
-\begin{frame}{Another application}{Transition between two steady states for histogram method}
+\begin{frame}{Another application of Krussel - Smith}{Transition between two steady states for histogram method}
 \centering{\includegraphics[width=12cm,height=6cm,keepaspectratio]{fig5}}

### 2017-02-20 cash_equivalent.m
cash equiv graph relative to output

@@ -39,12 +39,14 @@ function [ k ] = cash_equivalent( method, grid, sim, U )
         [k.equivalent_emp_sorted, sort_index_emp] = sort(k.equivalent(end,sim.one.e(T,:)==2),'descend');
         k_unemp = sim.one.k(T,sim.one.e(T,:)==1);
         k_emp = sim.one.k(T,sim.one.e(T,:)==2);
+        output_baseline = 3.3539;
         
         figure (2)
-        plot(k_emp(sort_index_emp),k.equivalent_emp_sorted,'g.',k_unemp(sort_index_unemp),k.equivalent_unemp_sorted,'r.')
+        plot(k_emp(sort_index_emp),k.equivalent_emp_sorted./output_baseline...
+            ,'g.',k_unemp(sort_index_unemp),k.equivalent_unemp_sorted./output_baseline,'r.')
         legend('employed','unemployed')
         xlabel('wealth')
-        ylabel('cash equivalent')
+        ylabel('cash equivalent / output')
         refline (0,0)
         
         

### 2017-02-20 welfare_analysis.m

@@ -46,9 +46,9 @@ for i=1:2
         for ii=1:size(mu,2)
             tic
             iteration = ii
-            par.mu = mu(4);
-            method.HH = 'FP'; % Depending on the mu, you might have to change it to 'FP' or 'FPend' to converge
-            method.agg = 'bisectio'; % Depending on the mu, you might have to change it to 'bisection' or 'bisectio' to converge
+            par.mu = mu(ii);
+            %method.HH = 'FPend'; % Depending on the mu, you might have to change it to 'FP' or 'FPend' to converge
+            %method.agg = 'bisection'; % Depending on the mu, you might have to change it to 'bisection' or 'bisectio' to converge
             setup % refresh setup for new parameter
             [ k.two, c.two, K.two, sim.two, store.two, mat.two, grid.two ] = aiyagari_solver( par, func, method );
             U.two.guess = func.U(c.two.guess);
@@ -79,21 +79,21 @@ for i=1:2
             [ k ] = cash_equivalent (method, grid, sim, U);
 
 %             % Construct a variable of values to be stored
-%             keep.c.equivalent_mean = c.equivalent_mean;
-%             keep.c.equivalent_median = c.equivalent_median;
-%             keep.c.equivalent_unemployed_mean = c.equivalent_unemployed_mean;
-%             keep.c.equivalent_unemployed_median = c.equivalent_unemployed_median;
-%             keep.c.equivalent_employed_mean = c.equivalent_employed_mean;
-%             keep.c.equivalent_employed_median = c.equivalent_employed_median;
-%             keep.k.equivalent_mean = k.equivalent_mean;
-%             keep.k.equivalent_median = k.equivalent_median;
-%             keep.k.equivalent_unemployed_mean = k.equivalent_unemployed_mean;
-%             keep.k.equivalent_unemployed_median = k.equivalent_unemployed_median;
-%             keep.k.equivalent_employed_mean = k.equivalent_employed_mean;
-%             keep.k.equivalent_employed_median = k.equivalent_employed_median;
-%             keep.K = K.two.guess;
-%             filename = ['baseline_mu_' num2str(ii) '.mat']; 
-%             save (filename, '-struct','keep'); % Save the values 
+            keep.c.equivalent_mean = c.equivalent_mean;
+            keep.c.equivalent_median = c.equivalent_median;
+            keep.c.equivalent_unemployed_mean = c.equivalent_unemployed_mean;
[…]

### 2017-02-21 graph_equivalents.m
Changed yannic's code to implement the analysis with endogenous duration of unemployment.

@@ -11,6 +11,8 @@ mu(7) = mu(6); % the original point does not converge
 mu(6) = 0.15; % the original point does not converge
 mu(8) = 0.18; % the original point does not converge
 
+
+
 % Load the data
 for i=1:mu_n
     filename = ['baseline_mu_' num2str(i) '.mat'];

### 2017-02-21 parameters.m

@@ -11,8 +11,9 @@ par.alpha = 0.36; % output elasticity of capital
 par.z = 1; % productivity
 
 % transition probabilities
-par.L_target = 0.9;
-par.PI_UE = 0.35; % chance of getting employed
+%par.L_target = 0.9;
+par.PI_UE = 0.4; % chance of getting employed
+par.PI_EU = 0.04444444; % fixed layoff probability at baseline level
 
 % solution methods
 method.HH = 'FP'; % 'FP' for fixed-point iteration in household problem, 'FPend' for using endogenous grid points

### 2017-02-21 setup.m

@@ -1,5 +1,5 @@
 %% Setup that depends upon the parameters
-par.PI_EU = par.PI_UE*(1-par.L_target)/par.L_target; % chance of getting unemployed
+%par.PI_EU = par.PI_UE*(1-par.L_target)/par.L_target; % chance of getting unemployed
 
 % build transition matrix of agents
 par.PI = [1-par.PI_UE,par.PI_UE;par.PI_EU,1-par.PI_EU]; % [UU,UE;EU;EE]

### 2017-02-21 welfare_analysis.m

@@ -14,6 +14,8 @@ mu(7) = mu(6); % the original point does not converge
 mu(6) = 0.15; % the original point does not converge
 mu(8) = 0.18; % the original point does not converge
 
+% Corresponding PI_UE grid for analysis 
+PI_UE_grid = [0.418, 0.414, 0.410, 0.406, 0.4, 0.398, 0.396, 0.387, 0.384, 0.380, 0.377, 0.373, 0.370, 0.367, 0.364, 0.360, 0.357, 0.354, 0.351];
 
 % Default parameterization is set by the calibration of Krussel and Smith (1998) for a US recession.
 % If you change parameters, type "par.<parameter> =" and then "setup" before
@@ -22,7 +24,7 @@ mu(8) = 0.18; % the original point does not converge
 % parameters for i=2 and leave i=1 as the baseline.
 
 % Get steady state utility and welfare measures for the model with two different parameters
-for i=1:2 
+for i=1:2
     if i==1 
         [ k.one, c.one, K.one, sim.one, store.one, mat.one, grid.one ] = aiyagari_solver( par, func, method );
         U.one.guess = func.U(c.one.guess);
@@ -43,12 +45,13 @@ for i=1:2
             U.one.extrap(t-ceil(T/2),sim.one.e(t,:)==2) = interp1(grid.one.k, U.one.lifetime(2,:), sim.one.k(t,sim.one.e(t,:)==2), 'linear', 'extrap');
         end
     elseif i==2 
-        for ii=1:size(mu,2)
+        for ii=9:size(mu,2) 
             tic
             iteration = ii
             par.mu = mu(ii);
-            %method.HH = 'FPend'; % Depending on the mu, you might have to change it to 'FP' or 'FPend' to converge
-            %method.agg = 'bisection'; % Depending on the mu, you might have to change it to 'bisection' or 'bisectio' to converge
+            par.PI_UE = PI_UE_grid(ii);
+            method.HH = 'FPend'; % Depending on the mu, you might have to change it to 'FP' or 'FPend' to converge
+            method.agg = 'bisection'; % Depending on the mu, you might have to change it to 'bisection' or 'bisectio' to converge
             setup % refresh setup for new parameter
             [ k.two, c.two, K.two, sim.two, store.two, mat.two, grid.two ] = aiyagari_solver( par, func, method );
             U.two.guess = func.U(c.two.guess);
@@ -92,8 +95,9 @@ for i=1:2
             keep.k.equivalent_employed_mean = k.equivalent_employed_mean;
[…]

### 2017-02-21 Paper/vorlage.tex
First version for the two pre-analysis parts and code set up to solve for two versions of transition calibrations.

\documentclass[a4paper,12pt]{article}
\usepackage{t1enc}
\usepackage[longnamesfirst, round]{natbib}  % Bindet den natbib-standard fuer das Zitieren ein
\usepackage{epsfig}
\usepackage[utf8]{inputenc}   % Ermoeglicht Sonderzeichen direkt einzugeben
\usepackage[T1]{fontenc}        % Garantiert saubere Worttrennung bei Umlauten etc.
\usepackage{color}              % Farbpaket
\usepackage{amsmath,amsfonts,amssymb}   % ermoeglicht mathematische Sonderzeichen
\usepackage{ngerman}           % neue deutsche Rechtschreibung
\usepackage[english]{babel}     %
\usepackage{ae}                 %
\usepackage{graphicx}           % Ermoeglicht das Einbinden von Bildern in allen Formaten
\usepackage{longtable}          % zum erstellen von Tabellen ber mehrere Seiten
\usepackage{multirow}           % zum Verbinden von Zeilen innerhalb einer Tabelle
%\usepackage{pictexwd}           % PicTex, ein Graphikpaket
%\usepackage{pst-all, multido}   % psTricks, ein Graphikpaket
\usepackage{url}
\usepackage{float}
\usepackage{subcaption}
\usepackage{booktabs, caption}
\usepackage[flushleft]{threeparttable}

% ________________ EINRICHTEN DES DOKUMENTS ______________________%

\bibliographystyle{apalike}    % legt den Stil fuer das Inhaltsverzeichnis fest

\oddsidemargin 0.1in \evensidemargin 0.1in \textwidth 15.5cm \topmargin -0.4in \textheight 24.5cm
\parindent 0cm      % legt die Seitenraender fest

\pagestyle{plain}          % leere Kopfzeile, Seitennummer in der Mitte der Fusszeile

\newcommand{\bs}{\boldsymbol}  % shortcut zur Erzeugung von fetten Sympolen in der Mathe-Umgebung

\renewcommand{\baselinestretch}{1.25}
% 1,5 -facher Zeilenabstand (Standard ist 1,2-facher Zeilenabstand, also 1,2*1,25 = 1,5

\begin{document}

% ________________ TITELSEITE ______________________%

\pagenumbering{roman}   % roemische Zahlen zur Seitennumerierung

\begin{titlepage}       % Umgebung fuer Titelseite, frei gestaltbar

\thispagestyle{empty}   % keine Numerierung auf Titelseite

\begin{center}
\vspace*{2.5cm}
{\bf  \Large Effects of Unemployment Benefits and Uncertainty in Heterogeneous Models\\The Importance of Endogenous Duration of Unemployment} \\
\vspace*{3cm} 
Term paper for the \\ Project Module in Macroeconomics and Public Economics: Uncertainty and Volatility \\
of Prof. Dr. Benjamin Born and Junior-Prof. Dr. Markus Riegler  \\
\vspace*{0.5cm} 
Winter Term 2016/17\\
\end{center}

\vfill
\begin{flushright}
   \emph{Eric Lustenberger} \\
    \emph{Bonner Talweg 34}\\
    \emph{53113 Bonn}\\
   \emph{Stud Nr.: 2849851}\\
 \emph{M.Sc. Economics}\\

\end{flushright}

% 
% \begin{center}
% $ $			% oeffnet und schliesst eine Matheumgebung (Trick, um den Titel nach unten zu rutschen
% \vspace{4cm}
% 
% {\LARGE TITEL}
% \vskip 4cm
% 
% Diese Seite ist frei gestaltbar
% \end{center}

\end{titlepage}

\newpage                % erzwingt an dieser Stelle einen Seitenumbruch

% ________________ INHALTSVERZEICHNIS ______________________%

% \tableofcontents   %fuegt Automatisch ein Inhaltsverzeichnis ein
% 
% \newpage
%

% ________________ HAUPTTEIL ______________________%

\pagenumbering{arabic}      % Seitenzahlen wieder arabisch numerieren
\setcounter{page}{1}        % Ruecksetzen des Seitenzahlzaehlers auf 1

\section{\"Uberschrift}
\label{Kapitel1}

\subsection{Unter\"Uberschrift}

\subsubsection*{UnterUnter\"Uberschrift}

Hier steht mal ein Text. Eine M\"oglichkeit des Zitierens ist, direkt
im Text die Quelle anzugeben \citep[see][pp.225-369]{key1}.
Andererseits schreiben \cite{key2}, dass man auch so zitieren kann.

In der Matheumgebung kann der oben (im Latex-Quellcode) genannte Shortcut verwendet
werden, um aus einem normalen $\beta$ ein fettes $\bs \beta$ zu
machen. Wichtige Gleichungen, die nochmal verwendet werden, sollten nummeriert werden, z.B.
\begin{equation}
\label{eq:ols}
   b = (x'x)x'y \;.
\end{equation}

Nebens\"achlicheres, auf das man sich nicht mehr bezieht, bleibt unnummeriert, also 
\begin{equation*}
   a = 1\;.
\end{equation*}
Nun kann man direkt auf die erste Gleichung als Gleichung~\eqref{eq:ols} verweisen mittels des zugewiesenen labels. In gleicher Weise kann man auf die Graphik~\ref{fig:ersteGraphik} bzw. Graphik~\ref{fig:andereGraphik} verweisen. Die Tilde zwischen \glqq Graphik\grqq{} und \glqq \verb|\ref{fig:andereGraphik}|\grqq{} verhindert, dass bei Zeilenumbr\"uchen die Zahl als erstes alleine in die neue Zeile rutscht. Ganz analog f\"ur die Tabelle~\ref{tab:Tabelle}.

\section{Ben\"otigte Programme}

unter Windows:
\begin{itemize}
   \item Miktex (\url{http://miktex.org/})
   \item ein Editor, je nach Geschmack z.B. WinEdt (\url{http://www.winedt.com/}; kostenpflichtige Studentenversion) oder einen der vielen anderen verf\"ugbaren, z.B. TeXnicCenter (\url{www.texniccenter.org/})
   \item ghostview und ghostscript (\url{http://pages.cs.wisc.edu/~ghost/}
\end{itemize}
unter Linux:
\begin{itemize}
   \item Latex ist in den meisten Verteilungen enthalten, z.B. tetex in Suse (ggf. \"uber yast nachinstallieren)
   \item als Editor empfiehlt sich z.B. Kile
\end{itemize}
f\"ur die Literatur:\\
z.B. JabRef (\url{http://jabref.sourceforge.net/})

\section{Pr\"asentationen}

Beispiele f\"ur Pr\"asentationen mit dem Beamer-Style:

\url{http://www.informatik.uni-freiburg.de/~frank/latex-kurs/latex-kurs-3/Latex-Kurs-3.html}

\section{Model}

The setup is a basic \cite{aiyagari} model.

\subsection{Consumer's Problem}

There is a continuum of ex-ante identical infinitely-lived consumers with population 1. Consumers maximize the discounted lifetime utility:

\[ 
 max_{\{{ c_{i,t}, k_{i,t+1} }\}_{t = 0}^{\infty}} {\mathbb{E}} \sum_{i=0}^{\infty} \beta^{t}  u(c_{i,t}) 
 \]

where $\beta \in (0,1)$ is the discount factor, $ c_{t}$ is consumption at time t and $\mathbb{E[.]}$ is the expectation at time 0.

Consumers are subject to uninsurable idiosyncratic risk. In each period they can be employed or unemployed. This process is governed by a transition matrix:
\[ \Pi = \begin{bmatrix}
1-\pi_{UE} & \pi_{UE} \\
 \pi_{EU} & 1-\pi_{EU}
\end{bmatrix}
\]

where $\pi_{UE}$ is the probability to find a job next period and $pi_{EU}$ is the layoff probability.

Consumers are allowed to interact on the capital market and accumulate one type of asset: at . Furthermore, consumers can be employed, or unemployed at each point in time. They are therefore subject to the following budget constraint at each point in time: 
  \[ 
  c_{i,t} + k_{i,t+1} = (1 + r_{t} - \delta) k_{i,t} + w_{t} (1 - \tau_{t})  e_{i,t} + \mu w_{t} (1 - e_{i,t})
  \]
 where rt is the interest rate at time t, $\delta$ is the depreciation rate, $w_{t}$ is the wage at time t. 
Finally, consumers are constrained in their borrowing, $k_{min}$ denotes the minimum amount of capital consumers are required to hold at each point in time:

   \[
   k_{i,t + 1} \geq \bar{k}
 	\]

\subsection{Firm's Problem}

The representative firm maximizes profits 
\[ \max_{\substack{K_{t},L_{t}}}F_{t}(K_{t},L_{t})-r_{t}K_{t}-w_{t}L_{t}
\]

Factor prices are obtained by taking the FOC's with respect to the aggregate capital stock and the aggregate labour, respectively: 
\[
r_{t} = \frac{\mathrm d F_{t}(K_{t},L_{t})}{\mathrm d K} = \alpha z (\tfrac{L_{t}}{K_{t}})^{1-\alpha} \]
\[
w_{t} = \frac{\mathrm d F_{t}(K_{t},L_{t})}{\mathrm d L} =(1-\alpha)z (\tfrac{K_{t}}{L_{t}})^{\alpha}
\]

\subsection{General Equilibrium}

The households take

Euler equation:
\[ 
c_{i,t}^{- \sigma} \geq \beta (1+r -\delta){\mathbb{E}[c_{i,t+1}^{- \sigma}}]
\]
Budget constraint:
 \[ 
 c_{i,t} + k_{i,t+1} = (1 + r_{t} - \delta) k_{i,t} + w (1 - \tau)  e_{i,t} + \mu w (1 - e_{i,t})
 \]
Borrowing constraint:
  \[
  k_{i,t + 1} \geq k_{min}
	\]
Factor prices:
\[
r = \alpha z (\tfrac{L}{K})^{1-\alpha} \ \ \ w = (1-\alpha)z (\tfrac{K}{L})^{\alpha}
\]
Employment and Tax rate: 
\[
L = \tfrac{\pi_{UE}}{\pi_{UE}+\pi_{EU}} \ \ \ \ \  \tau = \mu \tfrac{1-L}{L}
\]
\section{Welfare analysis}
We want to compare the utility level of the same agent before and after the policy change. There are two challenges to overcome, firstly we need take transitions into account. It may be the case that during the transition phase from one steady state to the other, agents loose eventough in the end they are in a preferred steady state and therefore do not prefer the policy change taking the transition into account. Secondly, utility is a purely ordinal measure and therefore not quantifiable.

For our presentation we have taken two different forms of measurement into account - Consumption equivalent and Cash equivalent. I will here only look at the Cash equivalent since it is a better measure.\footnote{The Consumption equivalent does weight different level's of consumption differently. A concave utility function implies that a consumption change of the same order is weighted differently by rich individuals with a high consumption to poor individuals with a low consumption.}

  \begin{itemize}
\item {
  Transfer of $\Delta$ units of wealth in the first period
  }
  \end{itemize}

  \begin{equation}
  U^{2}(e,k) = U^{1}(e,k+\Delta) \nonumber
  \end{equation}

  \begin{itemize}
  \item {
  If $ \Delta>0 $ agents prefer the policy change $ (U^{2}) $, otherwise not.
  }
  \end{itemize}

\section{Results}

\subsection{Calibration}

I will use the KrusellandSmith calibration, which founded the basis of our analysis for the presentation. However, since I am not considering aggregate risk, I will use the job-finding probability of 0.4, which corresponds to an average unemployment duration of 2.5 quarters or 32.5 weeks. Note that this a rather high estimate of unemployment duration.\footnote{\cite{mukoyama} makes a calibration for the post 1980 US economy, has a job-finding probability of 0.26 corresponding to 17 weeks of unemployment, thus providing a better match for the real data.}
Other variables are, a discount factor $\beta = 0.99$, productivity $z = 1$, $\alpha = 0.36$, depreciation rate $\theta = 0.025$, the baseline employment $rate l=0.9$, the baseline replacement rate $\mu = 0.15$.

%_________________ ENDE DES HAUPTTEILS_________________%

\newpage

%_________________ Literaturverzeichnis _______________%

\addcontentsline{toc}{section}{References}        % Fuegt im Inhaltsverzeichnis "References" hinzu
\bibliography{bibexample}                         % Erstellt Literaturverzeichnis (bindet das file bibexample.bib ein

%_________________ Platz fuer Graphiken und Tabellen _______________%

\newpage

% Einfuegen einer Grafik
\begin{figure}
\caption{titel der Graphik} 
\label{fig:ersteGraphik}	%label, um spaeter auf die Graphiknummer zugreifen zu koennen
\centering
\includegraphics[width=6.5cm]{abb1.png}  % width legt Breite der Graphik fest

\begin{minipage}{0.8\linewidth}
\footnotesize{die Graphik sollte beschrieben werden, sodass man ohne den Text vorne zu lesen wei\ss{}, worum es geht: panel 1 zeigt die Funktion, panel 2 die erste Ableitung und Panel 3 die zweite Ableitung}
\end{minipage}

\end{figure}

\begin{figure}
\caption{titel der Graphik}
\label{fig:andereGraphik} \centering
\includegraphics[angle=90,height=6.5cm]{abb2.jpg}  % angle dreht die Graphik, falls noetig; height legt die Hoehe der Graphik fest

\end{figure}

\begin{table}
\caption{Der Title der Tabelle}
\label{tab:Tabelle}
\centering
 \begin{tabular}{lc|r}
   Eine & kleine & Tabelle\\
\hline
   Text links & mittig & oder rechts \\
   & unterstrichen  & \\
\cline{2-2}
   \multicolumn{2}{c|}{\"uber zwei Spalten} & dritte Spalte \\
\end{tabular}   
\end{table}

\end{document}

### 2017-02-21 graph_equivalents.m

@@ -15,7 +15,8 @@ mu(8) = 0.18; % the original point does not converge
 
 % Load the data
 for i=1:mu_n
-    filename = ['baseline_mu_' num2str(i) '.mat'];
+    %filename = ['baseline_mu_' num2str(i) '.mat'];
+    filename = ['adapting_transitions_mu_' num2str(i) '.mat']
     c(i) = load(filename, 'c');
     k(i) = load(filename, 'k');
     c_equiv(i,:) = [c(i).c.equivalent_mean, c(i).c.equivalent_median, c(i).c.equivalent_unemployed_mean, c(i).c.equivalent_unemployed_median, c(i).c.equivalent_employed_mean, c(i).c.equivalent_employed_median];

### 2017-02-21 parameters.m

@@ -12,8 +12,8 @@ par.z = 1; % productivity
 
 % transition probabilities
 %par.L_target = 0.9;
-par.PI_UE = 0.4; % chance of getting employed
-par.PI_EU = 0.04444444; % fixed layoff probability at baseline level
+par.PI_UE = 0.764705882; % chance of getting employed
+par.PI_EU = 0.08496732; % fixed layoff probability at baseline level
 
 % solution methods
 method.HH = 'FP'; % 'FP' for fixed-point iteration in household problem, 'FPend' for using endogenous grid points

### 2017-02-21 welfare_analysis.m

@@ -15,8 +15,8 @@ mu(6) = 0.15; % the original point does not converge
 mu(8) = 0.18; % the original point does not converge
 
 % Corresponding PI_UE grid for analysis 
-PI_UE_grid = [0.418, 0.414, 0.410, 0.406, 0.4, 0.398, 0.396, 0.387, 0.384, 0.380, 0.377, 0.373, 0.370, 0.367, 0.364, 0.360, 0.357, 0.354, 0.351];
-
+% PI_UE_grid = [0.418006431, 0.413867753, 0.409823146, 0.405844156, 0.401954115,0.4, 0.398125746, 0.396341463, 0.38708909, 0.383537395, 0.380061395, 0.376636922, 0.373284328, 0.369980363, 0.366744717, 0.363555009, 0.360430298, 0.35734902, 0.354329636, 0.351351351];
+PI_UE_grid = [0.833333333,	0.817044812,	0.801430245,	0.786353738,	0.771879824,	0.764705882,	0.757884918,	0.751445087,	0.718867507,	0.706713781,	0.695001337,	0.683634834,	0.672668943,	0.662015583,	0.651727077,	0.641721789,	0.632049786,	0.622635184,	0.613525886, 0.604651163];
 % Default parameterization is set by the calibration of Krussel and Smith (1998) for a US recession.
 % If you change parameters, type "par.<parameter> =" and then "setup" before
 % you call the function. Do not change beta or sigma!
@@ -45,7 +45,7 @@ for i=1:2
             U.one.extrap(t-ceil(T/2),sim.one.e(t,:)==2) = interp1(grid.one.k, U.one.lifetime(2,:), sim.one.k(t,sim.one.e(t,:)==2), 'linear', 'extrap');
         end
     elseif i==2 
-        for ii=9:size(mu,2) 
+        for ii=1:size(mu,2) 
             tic
             iteration = ii
             par.mu = mu(ii);
@@ -95,7 +95,8 @@ for i=1:2
             keep.k.equivalent_employed_mean = k.equivalent_employed_mean;
             keep.k.equivalent_employed_median = k.equivalent_employed_median;
             keep.K = K.two.guess;
-            filename = ['adapting_transitions_mu_' num2str(ii) '.mat']; %Changing transitions
+            filename = ['adapting_transitions_2_mu_' num2str(ii) '.mat'];
+            %filename = ['adapting_transitions_mu_' num2str(ii) '.mat']; %Changing transitions
[…]

### 2017-02-21 analysis.m
Added my previous code to this branch.

@@ -1,0 +1,27 @@
+%% Analysis
+clear 
+close all
+
+%% Specify the type the solution method and simulation draws 
+method.sim = 'histogram'; % specify solution method: 'histogram' or 'simulation'
+par.ind_no = 100; % number of individuals simulated
+par.T = 100; % number of periods simulated
+
+%% Specify the parameter of interest and their values
+method.analysis = 'Unemployment Benefit'; % specify parameter you want to analyze: 'Borrowing Constraint' for min savings, 'Unemployment Benefit', 'Chance to be Employed','Risk Aversion'
+% par.vals = [0.15,0.25,0.35]; % indicate three parameter values for comparison
+% par.vals2 = [0.4,0.25,0.2]; % for the second analysis, also change a second set of parameters
+
+%% Plot grids
+gridpar.start = 0.15;
+gridpar.end = 0.35;
+gridpar.no = 10;
+mgrid.mu = linspace(gridpar.start,gridpar.end,gridpar.no);
+
+gridpar.start2 = 0.4;
+gridpar.end2 = 0.2;
+mgrid.pi = linspace(gridpar.start2, gridpar.end2,gridpar.no);
+
+
+%% Call the plotting function 
+plotting_fct(par, method, gridpar, mgrid) 

### 2017-02-21 plotting_fct.m

@@ -1,0 +1,241 @@
+function plotting_fct(par, method, gridpar, mgrid) 
+%% PLOTTING FUNCTION: The function creates a figure with three different
+% subplots for a vector of a parmater chosen for analysis. For each value
+% the parameter takes, the function creates a table containing the
+% aggregate values. Both, the three tables and the figure are saved in an
+% output folder. 
+%
+% Input variables:
+%   par = vector of parameters:
+%       ind_no = number of individuals simulated
+%       T = number of periods simulated
+%       vals = vector of three parameters used to run the analysis 
+%   method = method of simulation choice and method of analysis choice
+%
+%% Create Figures for different values 
+% Initiating matrix to store aggregate values    
+%T_mat = zeros(12,gridpar.no,3);
+T_mat = zeros(12,gridpar.no);
+parameters % import parameters 
+
+for i = 1:gridpar.no
+% loop over different values of parameter you want to analyze 
+    %for ii = 1:3
+        if strcmp(method.analysis,'Borrowing Constraint') 
+            par.k_min = par.vals(i);
+        elseif strcmp(method.analysis, 'Chance to be Employed')
+            par.PI_UE = par.vals(i);
+        elseif strcmp(method.analysis, 'Unemployment Benefit')
+            par.mu = mgrid.mu(i);
+            par.PI_UE = mgrid.pi(i); % letting transition fluctuate with benefits 
+        elseif strcmp(method.analysis, 'Risk Aversion')
+            par.sigma = par.vals(i); 
+        end
+% importing functions and parameters that adapt to new input parameter value             
+        setup 
+% calling the problem solving function 
+        [k, c, K, sim, store, mat, grid] = aiyagari_solver(par, func, method); 
+
+% %% Plot distribution of agents
+% % create subplot for each iteration
+%     figure(1)
+%     subplot(1,3,i)
+%     if strcmp(method.sim,'simulation')
+%         temp = sim.k(ceil(par.T/2):end,:);
+%         hist(temp(:),100)
[…]

### 2017-02-22 analysis.m
modified my code to work for new calibration.

@@ -13,14 +13,19 @@ method.analysis = 'Unemployment Benefit'; % specify parameter you want to analyz
 % par.vals2 = [0.4,0.25,0.2]; % for the second analysis, also change a second set of parameters
 
 %% Plot grids
-gridpar.start = 0.15;
-gridpar.end = 0.35;
-gridpar.no = 10;
-mgrid.mu = linspace(gridpar.start,gridpar.end,gridpar.no);
+% Create grid of unemployment benefits for the analysis
+gridpar.start = 0.01;
+gridpar.end = 0.6;
+gridpar.no = 20;
+mgrid.mu = linspace(gridpar.start, gridpar.end, gridpar.no);
+mgrid.mu(7) = mgrid.mu(6); % the original point does not converge
+mgrid.mu(6) = 0.15; % the original point does not converge
+mgrid.mu(8) = 0.18; % the original point does not converge
 
-gridpar.start2 = 0.4;
-gridpar.end2 = 0.2;
-mgrid.pi = linspace(gridpar.start2, gridpar.end2,gridpar.no);
+% matching grid of the transition probabilities
+gridpar.start2 = 0.418006431;
+gridpar.end2 = 0.351351351;
+mgrid.pi = [0.418006431, 0.413867753, 0.409823146, 0.405844156, 0.401954115,0.4, 0.398125746, 0.396341463, 0.38708909, 0.383537395, 0.380061395, 0.376636922, 0.373284328, 0.369980363, 0.366744717, 0.363555009, 0.360430298, 0.35734902, 0.354329636, 0.351351351];
 
 
 %% Call the plotting function 

### 2017-02-22 make_graphs.m

@@ -1,0 +1,121 @@
+% plot the graphs
+clear 
+close all 
+
+% Create grid of unemployment benefits for the analysis
+gridpar.start = 0.01;
+gridpar.end = 0.6;
+gridpar.no = 20;
+mgrid.mu = linspace(gridpar.start, gridpar.end, gridpar.no);
+mgrid.mu(7) = mgrid.mu(6); % the original point does not converge
+mgrid.mu(6) = 0.15; % the original point does not converge
+mgrid.mu(8) = 0.18; % the original point does not converge
+
+
+
+for i=1:gridpar.no
+    %filename = ['baseline_mu_' num2str(i) '.mat'];
+    filename = ['adapting_transitions_mu_parameters' num2str(i) '.mat']
+    T_mat(:,i) = [ag1 ag2 ag3 w r tax labor proba1 proba2 dev1 dev2 dev3];
+end
+
+
+
+%% Plot the grid values
+
+figure(2)
+subplot(3,3,1)
+plot(mgrid.mu,T_mat(1,:))
+%legend('Aggregate Capital')
+xlabel('reservation wage')
+ylabel('Aggregate Capital')
+
+subplot(3,3,2)
+plot(mgrid.mu,T_mat(2,:))
+%legend('Aggregate Output')
+xlabel('reservation wage')
+ylabel('Aggregate Output')
+
+subplot(3,3,3)
+plot(mgrid.mu, T_mat(3,:))
+%legend('Aggregate Output')
+xlabel('reservation wage')
+ylabel('Aggregate Consumption')
+
+subplot(3,3,4)
+plot(mgrid.mu,T_mat(4,:))
+%legend('Aggregate Output')
+xlabel('reservation wage')
+ylabel('Wage')
+
+subplot(3,3,5)
+plot(mgrid.mu, T_mat(5,:))
+%legend('Aggregate Output')
+xlabel('reservation wage')
+ylabel('Interest Rate')
+
+subplot(3,3,6)
+plot(mgrid.mu,T_mat(6,:))
+%legend('Aggregate Output')
+xlabel('reservation wage')
+ylabel('Tax rate')
+
+subplot(3,3,7)
+plot(mgrid.mu,T_mat(7,:))
+%legend('Aggregate Output')
+xlabel('reservation wage')
+ylabel('employment ratio')
+
+subplot(3,3,8)
+plot(mgrid.mu,T_mat(8,:))
+%legend('Aggregate Output')
[…]

### 2017-02-22 parameters.m

@@ -12,8 +12,8 @@ par.z = 1; % productivity
 
 % transition probabilities
 %par.L_target = 0.9;
-par.PI_UE = 0.764705882; % chance of getting employed
-par.PI_EU = 0.08496732; % fixed layoff probability at baseline level
+par.PI_UE = 0.4; % chance of getting employed
+par.PI_EU = 0.044444444; % fixed layoff probability at baseline level
 
 % solution methods
 method.HH = 'FP'; % 'FP' for fixed-point iteration in household problem, 'FPend' for using endogenous grid points

### 2017-02-22 plotting_fct.m

@@ -19,6 +19,7 @@ T_mat = zeros(12,gridpar.no);
 parameters % import parameters 
 
 for i = 1:gridpar.no
+    tic
 % loop over different values of parameter you want to analyze 
     %for ii = 1:3
         if strcmp(method.analysis,'Borrowing Constraint') 
@@ -60,21 +61,23 @@ for i = 1:gridpar.no
 %     end
 %     
 %% Calculating Aggregates 
-        ag1 = K.guess;
-        ag2 = func.Y(K.guess);
-        ag3 = func.C(K.guess); 
-        w = func.w(K.guess);
-        r = func.r(K.guess);
-        tax = par.tau;
-        labor = par.L;
-        proba1 = par.PI_UE;
-        proba2 = par.PI_EU;
-        dev1= log(K.guess/K.rep);
-        dev2= log(func.Y(K.guess)/func.Y(K.rep));
-        dev3= log(func.C(K.guess)/func.C(K.rep));     
-    
+        keep.ag1 = K.guess;
+        keep.ag2 = func.Y(K.guess);
+        keep.ag3 = func.C(K.guess); 
+        keep.w = func.w(K.guess);
+        keep.r = func.r(K.guess);
+        keep.tax = par.tau;
+        keep.labor = par.L;
+        keep.proba1 = par.PI_UE;
+        keep.proba2 = par.PI_EU;
+        keep.dev1= log(K.guess/K.rep);
+        keep.dev2= log(func.Y(K.guess)/func.Y(K.rep));
+        keep.dev3= log(func.C(K.guess)/func.C(K.rep));   
+        
+        filename = ['adapting_transitions_mu_parameters' num2str(i) '.mat'];
+        save (filename, '-struct','keep'); % Save the values
+        toc
 % saving aggregates in matrix
-        T_mat(:,i) = [ag1 ag2 ag3 w r tax labor proba1 proba2 dev1 dev2 dev3]; 
         %T_mat(:,i,ii) = [ag1 ag2 ag3 w r tax labor proba1 proba2 dev1 dev2 dev3]; 
 %    end
 end 
@@ -139,103 +142,103 @@ saveas(gcf,'output/graph.pdf')
[…]

### 2017-02-22 welfare_analysis.m

@@ -15,8 +15,8 @@ mu(6) = 0.15; % the original point does not converge
 mu(8) = 0.18; % the original point does not converge
 
 % Corresponding PI_UE grid for analysis 
-% PI_UE_grid = [0.418006431, 0.413867753, 0.409823146, 0.405844156, 0.401954115,0.4, 0.398125746, 0.396341463, 0.38708909, 0.383537395, 0.380061395, 0.376636922, 0.373284328, 0.369980363, 0.366744717, 0.363555009, 0.360430298, 0.35734902, 0.354329636, 0.351351351];
-PI_UE_grid = [0.833333333,	0.817044812,	0.801430245,	0.786353738,	0.771879824,	0.764705882,	0.757884918,	0.751445087,	0.718867507,	0.706713781,	0.695001337,	0.683634834,	0.672668943,	0.662015583,	0.651727077,	0.641721789,	0.632049786,	0.622635184,	0.613525886, 0.604651163];
+PI_UE_grid = [0.418006431, 0.413867753, 0.409823146, 0.405844156, 0.401954115,0.4, 0.398125746, 0.396341463, 0.38708909, 0.383537395, 0.380061395, 0.376636922, 0.373284328, 0.369980363, 0.366744717, 0.363555009, 0.360430298, 0.35734902, 0.354329636, 0.351351351];
+% PI_UE_grid = [0.833333333,	0.817044812,	0.801430245,	0.786353738,	0.771879824,	0.764705882,	0.757884918,	0.751445087,	0.718867507,	0.706713781,	0.695001337,	0.683634834,	0.672668943,	0.662015583,	0.651727077,	0.641721789,	0.632049786,	0.622635184,	0.613525886, 0.604651163];
 % Default parameterization is set by the calibration of Krussel and Smith (1998) for a US recession.
 % If you change parameters, type "par.<parameter> =" and then "setup" before
 % you call the function. Do not change beta or sigma!

### 2017-02-22 analysis.m
Adapted the last step to newest version of my old code.

@@ -3,14 +3,13 @@ clear
 close all
 
 %% Specify the type the solution method and simulation draws 
-method.sim = 'histogram'; % specify solution method: 'histogram' or 'simulation'
 par.ind_no = 100; % number of individuals simulated
 par.T = 100; % number of periods simulated
 
 %% Specify the parameter of interest and their values
 method.analysis = 'Unemployment Benefit'; % specify parameter you want to analyze: 'Borrowing Constraint' for min savings, 'Unemployment Benefit', 'Chance to be Employed','Risk Aversion'
 % par.vals = [0.15,0.25,0.35]; % indicate three parameter values for comparison
-% par.vals2 = [0.4,0.25,0.2]; % for the second analysis, also change a second set of parameters
+%par.vals2 = [1,2,3]; % for the second analysis, also change a second set of parameters
 
 %% Plot grids
 % Create grid of unemployment benefits for the analysis
@@ -29,4 +28,6 @@ mgrid.pi = [0.418006431, 0.413867753, 0.409823146, 0.405844156, 0.401954115,0.4,
 
 
 %% Call the plotting function 
-plotting_fct(par, method, gridpar, mgrid) 
+[Moments] = plotting_fct(par, method, gridpar, mgrid); 
+
+save analysis_output.mat

### 2017-02-22 make_graphs.m

@@ -16,7 +16,7 @@ mgrid.mu(8) = 0.18; % the original point does not converge
 for i=1:gridpar.no
     %filename = ['baseline_mu_' num2str(i) '.mat'];
     filename = ['adapting_transitions_mu_parameters' num2str(i) '.mat']
-    T_mat(:,i) = [ag1 ag2 ag3 w r tax labor proba1 proba2 dev1 dev2 dev3];
+    T_mat(:,i) = [ag1 ag2 ag3 w r tax labor proba1 proba2 dev1 dev2 dev3]; 
 end
 
 
@@ -26,96 +26,192 @@ end
 figure(2)
 subplot(3,3,1)
 plot(mgrid.mu,T_mat(1,:))
-%legend('Aggregate Capital')
-xlabel('reservation wage')
-ylabel('Aggregate Capital')
+title('aggregate capital','FontWeight','bold')
 
 subplot(3,3,2)
 plot(mgrid.mu,T_mat(2,:))
-%legend('Aggregate Output')
-xlabel('reservation wage')
-ylabel('Aggregate Output')
+title('aggregate output','FontWeight','bold')
 
 subplot(3,3,3)
 plot(mgrid.mu, T_mat(3,:))
-%legend('Aggregate Output')
-xlabel('reservation wage')
-ylabel('Aggregate Consumption')
+title('aggregate consumption','FontWeight','bold')
 
 subplot(3,3,4)
 plot(mgrid.mu,T_mat(4,:))
-%legend('Aggregate Output')
-xlabel('reservation wage')
-ylabel('Wage')
+title('wage','FontWeight','bold')
 
 subplot(3,3,5)
 plot(mgrid.mu, T_mat(5,:))
-%legend('Aggregate Output')
-xlabel('reservation wage')
-ylabel('Interest Rate')
+title('interest rate','FontWeight','bold')
 
 subplot(3,3,6)
 plot(mgrid.mu,T_mat(6,:))
-%legend('Aggregate Output')
-xlabel('reservation wage')
-ylabel('Tax rate')
+title('tax rate','FontWeight','bold')
 
 subplot(3,3,7)
 plot(mgrid.mu,T_mat(7,:))
-%legend('Aggregate Output')
-xlabel('reservation wage')
-ylabel('employment ratio')
+title('employment rate','FontWeight','bold')
+%axis equal
 
[…]

### 2017-02-22 plotting_fct.m

@@ -1,4 +1,4 @@
-function plotting_fct(par, method, gridpar, mgrid) 
+function [Mat_moments] = plotting_fct(par, method, gridpar, mgrid) 
 %% PLOTTING FUNCTION: The function creates a figure with three different
 % subplots for a vector of a parmater chosen for analysis. For each value
 % the parameter takes, the function creates a table containing the
@@ -14,33 +14,41 @@ function plotting_fct(par, method, gridpar, mgrid)
 %
 %% Create Figures for different values 
 % Initiating matrix to store aggregate values    
-%T_mat = zeros(12,gridpar.no,3);
 T_mat = zeros(12,gridpar.no);
+Mat_moments = zeros(8,gridpar.no);
+
+T_mat2 = zeros(12,gridpar.no,3);
+Mat_moments2 = zeros(2,4,3,3);
+
 parameters % import parameters 
 
 for i = 1:gridpar.no
-    tic
+tic
 % loop over different values of parameter you want to analyze 
-    %for ii = 1:3
+     %for ii = 1:3
+     
         if strcmp(method.analysis,'Borrowing Constraint') 
             par.k_min = par.vals(i);
         elseif strcmp(method.analysis, 'Chance to be Employed')
-            par.PI_UE = par.vals(i);
+            par.PI_UE = mgrid.pi(i);
         elseif strcmp(method.analysis, 'Unemployment Benefit')
             par.mu = mgrid.mu(i);
+%               par.sigma = par.vals2(ii);
             par.PI_UE = mgrid.pi(i); % letting transition fluctuate with benefits 
         elseif strcmp(method.analysis, 'Risk Aversion')
             par.sigma = par.vals(i); 
         end
 % importing functions and parameters that adapt to new input parameter value             
         setup 
+%method.HH = 'FPend'; % Depending on the mu, you might have to change it to 'FP' or 'FPend' to converge
+%method.agg = 'bisection'; % Depending on the mu, you might have to change it to 'bisection' or 'bisectio' to converge
 % calling the problem solving function 
         [k, c, K, sim, store, mat, grid] = aiyagari_solver(par, func, method); 
 
[…]

### 2017-02-22 plotting_fct.m
Deleted old code.

@@ -24,6 +24,7 @@ parameters % import parameters
 
 for i = 1:gridpar.no
 tic
+iteration = i
 % loop over different values of parameter you want to analyze 
      %for ii = 1:3
      

### 2017-02-22 Paper/vorlage.tex
Started with analysis part of paper and obtained parameter results for analysis case.

@@
 \usepackage{graphicx}           % Ermoeglicht das Einbinden von Bildern in allen Formaten
+\usepackage{epstopdf}
 \usepackage{longtable}          % zum erstellen von Tabellen ber mehrere Seiten
@@
 There is a continuum of ex-ante identical infinitely-lived consumers with population 1. Consumers maximize the discounted lifetime utility: 
-
 \[ 
@@
 
-Consumers are subject to uninsurable idiosyncratic risk. In each period they can be employed or unemployed. This process is governed by a transition matrix:
+Consumers are subject to uninsurable idiosyncratic risk.
+In each period they can either be employed $(e_{i,t}=1)$ or unemployed $(e_{i,t}=0)$ .
+This process is governed by an exogenous transition matrix:
 \[ \Pi = \begin{bmatrix}
@@
 
-Consumers are allowed to interact on the capital market and accumulate one type of asset: at .
-Furthermore, consumers can be employed, or unemployed at each point in time.
+Consumers are allowed to interact on the capital market and accumulate one type of asset: $a_{t}$ to smooth consumption over time and insure for rainy days.
 They are therefore subject to the following budget constraint at each point in time:
@@
   \]
- where rt is the interest rate at time t, $\delta$ is the depreciation rate, $w_{t}$ is the wage at time t. 
+ where $r_{t}$ is the interest rate at time t, $\delta$ is the depreciation rate, $w_{t}(1-\tau_{t})$ is the after-tax wage at time t and $\mu_{t}$ are the unemployment benefits, which represent a replacement rate i.e.
+the fraction of the wage unemployed receive.
+
 Finally, consumers are constrained in their borrowing, $k_{min}$ denotes the minimum amount of capital consumers are required to hold at each point in time: 
-
    \[
@@
 
+\subsection{The governement}
+
+The governement runs a balanced budget:
+\[
+\tau_{t}=\mu\frac{1-L_{t}}{L_{t}}
+\]
+
 \subsection{General Equilibrium}
 
-The households take
-
-Euler equation:
+The euler equation is maximizing the consumer's problem
 \[ 
@@
 \]
-Budget constraint:
- \[ 
- c_{i,t} + k_{i,t+1} = (1 + r_{t} - \delta) k_{i,t} + w (1 - \tau)  e_{i,t} + \mu w (1 - e_{i,t})
+The households take (current and future) factor prices $r_{t} and w_{t}$ as given.
+Their policy functions satisfy the first-order conditions and depend on the employment status, wealth and the aggregate state:
+\[ c_{t}(e_{t},k_{t},s_{t}), k_{t+1}(e_{t},k_{t},s_{t})
 \]
-Borrowing constraint:
-  \[
-  k_{i,t + 1} \geq k_{min}
+where $s_{t}$ stands for the aggregate productivity state and the cross-sectional distribution.
+
+Finally, the aggregated capital and labour must be consistent with aggregate capital and labour used to obtain the factor prices: 
+\[ \sum_{i}k_{t+1}(e_{i,t},k_{i,t},s_{t})=K_{t+1}(s_{t}), \ \ \ \sum_{i}e_{i,t}=L_{t} 
 \]
-Factor prices:
-\[
-r = \alpha z (\tfrac{L}{K})^{1-\alpha} \ \ \ w = (1-\alpha)z (\tfrac{K}{L})^{\alpha}
-\]
-Employment and Tax rate: 
-\[
-L = \tfrac{\pi_{UE}}{\pi_{UE}+\pi_{EU}} \ \ \ \ \  \tau = \mu \tfrac{1-L}{L}
-\]
+
 \section{Welfare analysis}
@@
 
-\section{Results}
+\section{Analysis}
+
+In the following section I will analyse the importance of considering disincentive and incentive effects when considering changes in the unemployment benefits.
+Within the model described above and built de foundation for our results presented in class, the transition probabilities and the unemployment rate are exogenously determined.
+We therefore abstracted from such incentive effects.
+In the following experiment I will loosen this strong assumption and analyze the implications for the welfare analysis.
+
+After I introduce the Calibration, I proceed with a short summary of the results obtained in the baseline case and then proceed with a more detailed discussion of the case with an endogenous job-finding probability.
 
@@
 I will use the KrusellandSmith calibration, which founded the basis of our analysis for the presentation.
-However, since I am not considering aggregate risk, I will use the job-finding probability of 0.4, which corresponds to an average unemployment duration of 2.5 quarters or 32.5 weeks.
+However, since I am not considering aggregate risk, I will use the job-finding probability of 0.4\footnote{For the presentation we took $\pi_{ue}=0.35$.
+Note that the results for the welfare analysis in the baseline case do not change.See appendix 1}, which corresponds to an average unemployment duration of 2.5 quarters or 32.5 weeks.
 Note that this a rather high estimate of unemployment duration.\footnote{\cite{mukoyama} makes a calibration for the post 1980 US economy, has a job-finding probability of 0.26 corresponding to 17 weeks of unemployment, thus providing a better match for the real data.}
 Other variables are, a discount factor $\beta = 0.99$, productivity $z = 1$, $\alpha = 0.36$, depreciation rate $\theta = 0.025$, the baseline employment $rate l=0.9$, the baseline replacement rate $\mu = 0.15$.
+
+\subsection{Baseline Results}
+
+When we conducted our prior welfare analysis we found that different groups in society want different policies - namely, the unemployed would prefer to change to higher unemployment benefits and the employed would prefer a change to a less distributive system.
+Fruthermore, we also found that generally agents do not want full unemployment insurance, although this would clearly eliminate idiosyncratic risk.
+Figure 1 illustrates this well:
+
+\begin{figure}
+\caption{Results Cash Equivalent Baseline } 
+\label{baseline_ue_vs_e}	%label, um spaeter auf die Graphiknummer zugreifen zu koennen
+\centering
+\includegraphics[scale=.7]{Cash_equivalent_baseline}  % width legt Breite der Graphik fest
+
+\begin{minipage}{0.8\linewidth}
+\footnotesize{The dotted lines describe the medians and the continues lines the means of the consumption equivalent.
+The rose lines illustrate the mean and median for the unemployed.
+The green lines show the consumption equivalent of the mean and median of the employed.
+The baseline, $\mu = 0.15$, is where the two lines cross.
+Clearly, the employed prefer lower benefits and the unemployed higher benefits.
+}
+\end{minipage}
+
+\end{figure}
+
+\subsection{Adapting the transition probability}
 

### 2017-02-22 make_graphs.m

@@ -14,11 +14,22 @@ mgrid.mu(8) = 0.18; % the original point does not converge
 
 
 for i=1:gridpar.no
-    %filename = ['baseline_mu_' num2str(i) '.mat'];
-    filename = ['adapting_transitions_mu_parameters' num2str(i) '.mat']
-    T_mat(:,i) = [ag1 ag2 ag3 w r tax labor proba1 proba2 dev1 dev2 dev3]; 
+    filename = ['baseline_mu_parameters' num2str(i) '.mat'];
+    %filename = ['adapting_transitions_mu_parameters' num2str(i) '.mat']
+    ag1(i) = load(filename, 'ag1');
+    ag2(i) = load(filename, 'ag2');
+    ag3(i) = load(filename, 'ag3');
+    w(i) = load(filename, 'w');
+    r(i) = load(filename, 'r');
+    tax(i) = load(filename, 'tax');
+    labor(i) = load(filename, 'labor');
+    proba1(i) = load(filename, 'proba1');
+    proba2(i) = load(filename, 'proba2');
+    dev1(i) = load(filename, 'dev1');
+    dev2(i) = load(filename, 'dev2');
+    dev3(i) = load(filename, 'dev3');
+    T_mat(:,i) = [ag1(i).ag1 ag2(i).ag2 ag3(i).ag3 w(i).w r(i).r tax(i).tax labor(i).labor proba1(i).proba1 proba2(i).proba2 dev1(i).dev1 dev2(i).dev2 dev3(i).dev3]; 
 end
-
 
 
 %% Plot the grid values

### 2017-02-22 plotting_fct.m

@@ -22,7 +22,7 @@ Mat_moments2 = zeros(2,4,3,3);
 
 parameters % import parameters 
 
-for i = 1:gridpar.no
+for i = 9:gridpar.no
 tic
 iteration = i
 % loop over different values of parameter you want to analyze 
@@ -35,14 +35,14 @@ iteration = i
         elseif strcmp(method.analysis, 'Unemployment Benefit')
             par.mu = mgrid.mu(i);
 %               par.sigma = par.vals2(ii);
-            par.PI_UE = mgrid.pi(i); % letting transition fluctuate with benefits 
+           % par.PI_UE = mgrid.pi(i); % letting transition fluctuate with benefits 
         elseif strcmp(method.analysis, 'Risk Aversion')
             par.sigma = par.vals(i); 
         end
 % importing functions and parameters that adapt to new input parameter value             
         setup 
-%method.HH = 'FPend'; % Depending on the mu, you might have to change it to 'FP' or 'FPend' to converge
-%method.agg = 'bisection'; % Depending on the mu, you might have to change it to 'bisection' or 'bisectio' to converge
+method.HH = 'FPend'; % Depending on the mu, you might have to change it to 'FP' or 'FPend' to converge
+method.agg = 'bisection'; % Depending on the mu, you might have to change it to 'bisection' or 'bisectio' to converge
 % calling the problem solving function 
         [k, c, K, sim, store, mat, grid] = aiyagari_solver(par, func, method); 
 
@@ -74,38 +74,38 @@ iteration = i
 % 
 % 
 % end
-%% Calculate and save the moments 
-
-
-capital_grid = [transpose(grid.dist) transpose(grid.dist)];
-distr = store.distribution.*capital_grid;
-
-% calculating the mean [unemployed employed]
-% note that you need to rescale the probabilities!!!
-mean_dis = sum(distr).*[1/(1-par.L_target) 1/par.L_target];
-
-sum1 = cumsum(store.distribution(:,1));
-sum2 = cumsum(store.distribution(:,2));
-[~, index1]=min(abs(sum1-((sum1(end))/2)));
-[~, index2]=min(abs(sum2-((sum2(end))/2)));
-closestValues=sum1(index1);% to check value for unemployed
-closestValues2 =sum2(index2); % to check value for employed
-
[…]

### 2017-02-22 analysis.m
Distribution analysis and transitions only.

@@ -7,7 +7,7 @@ par.ind_no = 100; % number of individuals simulated
 par.T = 100; % number of periods simulated
 
 %% Specify the parameter of interest and their values
-method.analysis = 'Unemployment Benefit'; % specify parameter you want to analyze: 'Borrowing Constraint' for min savings, 'Unemployment Benefit', 'Chance to be Employed','Risk Aversion'
+method.analysis = 'Chance to be Employed'; % specify parameter you want to analyze: 'Borrowing Constraint' for min savings, 'Unemployment Benefit', 'Chance to be Employed','Risk Aversion'
 % par.vals = [0.15,0.25,0.35]; % indicate three parameter values for comparison
 %par.vals2 = [1,2,3]; % for the second analysis, also change a second set of parameters
 

### 2017-02-22 make_graphs.m

@@ -14,7 +14,7 @@ mgrid.mu(8) = 0.18; % the original point does not converge
 
 
 for i=1:gridpar.no
-    filename = ['baseline_mu_parameters' num2str(i) '.mat'];
+    filename = ['transitions_only' num2str(i) '.mat'];
     %filename = ['adapting_transitions_mu_parameters' num2str(i) '.mat']
     ag1(i) = load(filename, 'ag1');
     ag2(i) = load(filename, 'ag2');

### 2017-02-22 parameters.m

@@ -17,5 +17,5 @@ par.PI_EU = 0.044444444; % fixed layoff probability at baseline level
 
 % solution methods
 method.HH = 'FP'; % 'FP' for fixed-point iteration in household problem, 'FPend' for using endogenous grid points
-method.sim = 'simulation'; % 'simulation' for simulation, 'histogram' for histogram method
+method.sim = 'histogram'; % 'simulation' for simulation, 'histogram' for histogram method
 method.agg = 'bisectio'; % 'bisection' to use bisection method, gradual updating otherwise

### 2017-02-22 plotting_fct.m

@@ -22,7 +22,7 @@ Mat_moments2 = zeros(2,4,3,3);
 
 parameters % import parameters 
 
-for i = 9:gridpar.no
+for i = 11%:gridpar.no
 tic
 iteration = i
 % loop over different values of parameter you want to analyze 
@@ -41,91 +41,83 @@ iteration = i
         end
 % importing functions and parameters that adapt to new input parameter value             
         setup 
-method.HH = 'FPend'; % Depending on the mu, you might have to change it to 'FP' or 'FPend' to converge
-method.agg = 'bisection'; % Depending on the mu, you might have to change it to 'bisection' or 'bisectio' to converge
+%method.HH = 'FP'; % Depending on the mu, you might have to change it to 'FP' or 'FPend' to converge
+%method.agg = 'bisection'; % Depending on the mu, you might have to change it to 'bisection' or 'bisectio' to converge
 % calling the problem solving function 
         [k, c, K, sim, store, mat, grid] = aiyagari_solver(par, func, method); 
 
-% % %% Plot distribution of agents
-% if i == 1 || i == 11 || i == 20 %create subplot for each iteration
-%     figure(6+i)
-%     %subplot(1,3,ceil(i/7))
-%     if strcmp(method.sim,'simulation')
-%         temp = sim.k(ceil(par.T/2):end,:);
-%         hist(temp(:),100)
-%         legend('number of agents')
-%     elseif strcmp(method.sim,'histogram')
-%         bar(grid.dist,store.distribution,'stacked')
-%         legend('unemployed','employed')
-%         set(gca,'fontsize',25)
-%         
-%     end
-% % create title matching parameter in question
-% %     if strcmp(method.analysis,'Borrowing Constraint') 
-% %         title(['kmin = ',num2str(par.k_min)]);
-% %     elseif strcmp(method.analysis,'Chance to be Employed')
-% %         title(['PI UE = ',num2str(par.PI_UE)]);
-% %     elseif strcmp(method.analysis,'Unemployment Benefit')
-% %         title(['mu = ',num2str(par.mu)]);
-% %     elseif strcmp(method.analysis,'Risk Aversion')
-% %         title(['sigma = ',num2str(par.sigma)]);
-% %     end
+% %% Plot distribution of agents
+    figure(1)
[…]

### 2017-02-23 Paper/Paper_Eric.tex
structure of paper is there.

--- 2017-02-22 Paper/vorlage.tex
@@
 \usepackage{graphicx}           % Ermoeglicht das Einbinden von Bildern in allen Formaten
-\usepackage{epstopdf}
 \usepackage{longtable}          % zum erstellen von Tabellen ber mehrere Seiten
@@
 
-\section{Ben\"otigte Programme}
+\section{Introduction}
 
-unter Windows:
-\begin{itemize}
-   \item Miktex (\url{http://miktex.org/})
-   \item ein Editor, je nach Geschmack z.B.
-WinEdt (\url{http://www.winedt.com/}; kostenpflichtige Studentenversion) oder einen der vielen anderen verf\"ugbaren, z.B.
-TeXnicCenter (\url{www.texniccenter.org/})
-   \item ghostview und ghostscript (\url{http://pages.cs.wisc.edu/~ghost/}
-\end{itemize}
-unter Linux:
-\begin{itemize}
-   \item Latex ist in den meisten Verteilungen enthalten, z.B. tetex in Suse (ggf. \"uber yast nachinstallieren)
-   \item als Editor empfiehlt sich z.B. Kile
-\end{itemize}
-f\"ur die Literatur:\\
-z.B. JabRef (\url{http://jabref.sourceforge.net/})
-
-\section{Pr\"asentationen}
-
-Beispiele f\"ur Pr\"asentationen mit dem Beamer-Style:
-
-\url{http://www.informatik.uni-freiburg.de/~frank/latex-kurs/latex-kurs-3/Latex-Kurs-3.html}
+In our presentation we have discussed welfare implications of changes in the unemployment policy.
+We have done so using a simple Aiyagari framework, where agents are subject to exogenous unemployment shocks.
+These shocks are assumed to be independent of the policy itself.
+Furthermore, the unemployment rate, which only depends on the different transition probabilities is so too.
+In other words, changes of the level unemployment insurance do not affect the unemployment rate.
+This strongly contradicts empirical literature.\footnote{See \citep{decker} for a review.} The main argument being that higher unemployment benefits will decrease incentives for the workers to look for jobs.
+Furthermore, there is a great deal of theoretical literature, consisting of search-match and moral hazard models suggesting the same.
+(cite some guys)
 
@@
 We want to compare the utility level of the same agent before and after the policy change.
-There are two challenges to overcome, firstly we need take transitions into account.
+There are two challenges to overcome.
+Firstly, utility is a purely ordinal measure and therefore not quantifiable.
+Secondly,we need take transitions into account.
 It may be the case that during the transition phase from one steady state to the other, agents loose eventough in the end they are in a preferred steady state and therefore do not prefer the policy change taking the transition into account.
-Secondly, utility is a purely ordinal measure and therefore not quantifiable.
 
 For our presentation we have taken two different forms of measurement into account - Consumption equivalent and Cash equivalent.
-I will here only look at the Cash equivalent since it is a better measure.\footnote{The Consumption equivalent does weight different level's of consumption differently.
+I will here only discuss the Cash Equivalent.
+However, the conclusions I will draw from my analysis are the same when using the Consumption Equivalent (See Appendix 1).\footnote{That being said, the two measures differ in the manner they weight different groups.
+The Consumption equivalent does weight different level's of consumption differently.
 A concave utility function implies that a consumption change of the same order is weighted differently by rich individuals with a high consumption to poor individuals with a low consumption.}
 
-  \begin{itemize}
-\item {
-  Transfer of $\Delta$ units of wealth in the first period
-  }
-  \end{itemize}
+\subsubsection*{The Cash Equivalent}
+
+The Cash Equivalent tells you how much cash, as in units of wealth, I have to give to (or take away from) the agent in the first economy, in order for him to be indifferent between the two economies - The two being identical with the exeption of two different benefit policies.
+$U^{1}$ being the livetime utility in the baseline economy with benefit policy one and $U^{2}$ being the livetime utility in the economy with the adjusted policy.
+Formally:
 
@@
 
-  \begin{itemize}
-  \item {
-  If $ \Delta>0 $ agents prefer the policy change $ (U^{2}) $, otherwise not.
-  }
-  \end{itemize}
+Where $\Delta$ is the transfer of units of wealth in the first period, $e$ is the employment status and $k$ the individual capital.
+If $ \Delta>0 $ agents prefer the policy change, otherwise they prefer the current state.
+
+\subsubsection*{Taking transitions into account}
+
+One has to consider the transitions.
+Approximation used by \cite{KrusellMukoyamaSahin}.
+Instead of calculating full transitions I compare different steady states, placing the agents along with their capital holding and their employment state into the new economy and I then compare the two lifetime utilities.
 
@@
 \subsection{Adapting the transition probability}
+
+As discussed above, the transition probabilities and the unemployment rate are exogenously given.
+In the following analysis I will adapt the job-finding probability with the level of the unemployment benefits.
+In order for this to affect the unemployment rate, I will fix the job-loss probability, since otherwise the changes of the two transition probabilities would simply cancel each-other out to keep the labor target rate constant.\footnote{One can think of this as a simplified version of the model \cite{mukoyama} uses, abstracting from details regarding job-market rigidities and the Nash bargaining process.}
+
+I base my calibration on the empirical literature.
+\citep{decker} summarizes the empirical literature, which considers disincentive and incentive effects with respect to changes in unemployment benefits using different approaches and as well as a variety of US-samples.
+He concludes, that a change of 10 percent-points in benefits leads to a prolongement of the average unemployment duration of 0.5 to 1.5 weeks.
+Thus, I let the job-finding probability such that an 10 percent-point increase of the benefits leads to a prolongement of the average unemployment period of a week.\footnote{Appendix 2 provides a detailed conversion table.}
+
+\subsection{Results}
+\begin{figure}
+\caption{Results Cash Equivalent with endogenous job-finding probability} 
+\label{baseline_ue_vs_e}	%label, um spaeter auf die Graphiknummer zugreifen zu koennen
+\centering
+\includegraphics[scale=.7]{cash_equivalent(ue_vs_e)}  % width legt Breite der Graphik fest
+
+\begin{minipage}{0.8\linewidth}
+\footnotesize{The dotted lines describe the medians and the continues lines the means of the consumption equivalent.
+The rose lines illustrate the mean and median for the unemployed.
+The green lines show the consumption equivalent of the mean and median of the employed.
+The baseline, $\mu = 0.15$, is where the two lines cross.
+Clearly, the employed would prefer negative benefits and the unemployed lower benefits.
+}
+\end{minipage}
+
+\end{figure}
+
+Figure 2 shows displays the mean and median Cash Equivalent for the unemployed and the employed.
+It clearly shows that all agents prefer lower benefits.
+While the optimum for the employed lies at 0 (or are negative benefits) the unemployed prefer some benefits, but lower than the baseline.
+Compared to the previous results all agents prefer lower benefits.\footnote{\cite{KrusellMukoyamaSahin} find similar results, when comparing a standard BHA model with a model including endogenous unemployment.}
+As benefits increase the unemployment rate rises.
+There are therefore less employed who have to pay higher benefits to more unemployed.
+This raises taxes to a higher extent than in the previous case and thus make the employed worse off in the case of a raise in the benefits.
+This amplifying effect works in both directions.
+As employment increases with lower benefits, the relative taxes decrease faster than in the baseline case and thus, the lowest possible benefits are preferred by the employed.
+While the employed are not directly affected by a change in the transition probabilites, the unemployed's risk of receiving low income increases with an increase in the benefits.
+Thus their expected future income decreases as they face larger unemployment spells on average.
+In the present case, this effect seems to be strong enough for the unemployed to prefer to forego some amount of benefits and in turn profit from higher future income prospects on average, as the proability to being employed next period rises.
+This effect, however, is not strong enough to completely overcome the benefits of a replacement rate and thus in the present case, the unemployed would prefer a $\mu$ of around 0.7.
+Which also is pareto-optimal, as both, the mean and the median, are maximal at this level of benefits.
+
+\section{Conclusion}
+
+The first observation, thus is, that depending on the model specification one may draw different conclusions when making policy recommendations.
+Clearly, starting from the baseline calibration describing the US economy, it may make sense to propose a higher benefit-scheme in the first case (the foundation of the argument being, unemployed are better of with higher benefits).
+However, taking transitions into account, this line of argumentation clearly fails.
+Finally, a policy-scheme simply relying on unemployment benefits is limited.
+It may be optimal to combine unemployment benefits with reintegration measures facilitating job search and inducing the unemployed to reintegrate themselfs in the job market.
+Although, the results seem to be similar to those of others, one has to be aware that exogenously determine the transition probability, based on a linear relationship between unemployment duration and unemployment benefits may be limited.
+First of all this relationship may not be linear (cite some guy).
+Secondly, higher unemployment benefits may also impact the job-loss probability (cite some guy), although the literature is less clear on that.
+Finally, I have completely abstracted from a bargaining process, which will also affect the firms side and produce further changes in the wage\citep{mukoyama} for an example.
+These changes may potentially further alter the results.\footnote{In this simple setting, prices and therefore also the wage, entirely depend on the aggregates driven by individual savings.}
 

### 2017-02-23 analysis.m

@@ -7,7 +7,7 @@ par.ind_no = 100; % number of individuals simulated
 par.T = 100; % number of periods simulated
 
 %% Specify the parameter of interest and their values
-method.analysis = 'Chance to be Employed'; % specify parameter you want to analyze: 'Borrowing Constraint' for min savings, 'Unemployment Benefit', 'Chance to be Employed','Risk Aversion'
+method.analysis = 'Unemployment Benefit'; % specify parameter you want to analyze: 'Borrowing Constraint' for min savings, 'Unemployment Benefit', 'Chance to be Employed','Risk Aversion'
 % par.vals = [0.15,0.25,0.35]; % indicate three parameter values for comparison
 %par.vals2 = [1,2,3]; % for the second analysis, also change a second set of parameters
 

### 2017-02-23 parameters.m

@@ -17,5 +17,5 @@ par.PI_EU = 0.044444444; % fixed layoff probability at baseline level
 
 % solution methods
 method.HH = 'FP'; % 'FP' for fixed-point iteration in household problem, 'FPend' for using endogenous grid points
-method.sim = 'histogram'; % 'simulation' for simulation, 'histogram' for histogram method
+method.sim = 'simulation'; % 'simulation' for simulation, 'histogram' for histogram method
 method.agg = 'bisectio'; % 'bisection' to use bisection method, gradual updating otherwise

### 2017-02-23 plotting_fct.m

@@ -35,14 +35,14 @@ iteration = i
         elseif strcmp(method.analysis, 'Unemployment Benefit')
             par.mu = mgrid.mu(i);
 %               par.sigma = par.vals2(ii);
-           % par.PI_UE = mgrid.pi(i); % letting transition fluctuate with benefits 
+            par.PI_UE = mgrid.pi(i); % letting transition fluctuate with benefits 
         elseif strcmp(method.analysis, 'Risk Aversion')
             par.sigma = par.vals(i); 
         end
 % importing functions and parameters that adapt to new input parameter value             
         setup 
-%method.HH = 'FP'; % Depending on the mu, you might have to change it to 'FP' or 'FPend' to converge
-%method.agg = 'bisection'; % Depending on the mu, you might have to change it to 'bisection' or 'bisectio' to converge
+method.HH = 'FP'; % Depending on the mu, you might have to change it to 'FP' or 'FPend' to converge
+method.agg = 'bisection'; % Depending on the mu, you might have to change it to 'bisection' or 'bisectio' to converge
 % calling the problem solving function 
         [k, c, K, sim, store, mat, grid] = aiyagari_solver(par, func, method); 
 
@@ -91,7 +91,7 @@ kept.skewness_employed = mean(((grid.dist - mean_dis(2))/kept.std_employed).^3);
 
 % store moments
 %Mat_moments = [mean_dis(1) median_dis(1) std_dis1 skewness_dis1 mean_dis(2) median_dis(2) std_dis2 skewness_dis2];
-savename = ['moments_transitions_only' num2str(i) '.mat'];
+savename = ['moments_mu_and_transitions' num2str(i) '.mat'];
 save(savename, '-struct','kept'); % Save the values
 
 % Mat_moments2(:,:,i,ii) = [mean_dis(1) median_dis(1) std_dis1 skewness_dis1;

### 2017-02-23 welfare_analysis.m

@@ -16,7 +16,6 @@ mu(8) = 0.18; % the original point does not converge
 
 % Corresponding PI_UE grid for analysis 
 PI_UE_grid = [0.418006431, 0.413867753, 0.409823146, 0.405844156, 0.401954115,0.4, 0.398125746, 0.396341463, 0.38708909, 0.383537395, 0.380061395, 0.376636922, 0.373284328, 0.369980363, 0.366744717, 0.363555009, 0.360430298, 0.35734902, 0.354329636, 0.351351351];
-% PI_UE_grid = [0.833333333,	0.817044812,	0.801430245,	0.786353738,	0.771879824,	0.764705882,	0.757884918,	0.751445087,	0.718867507,	0.706713781,	0.695001337,	0.683634834,	0.672668943,	0.662015583,	0.651727077,	0.641721789,	0.632049786,	0.622635184,	0.613525886, 0.604651163];
 % Default parameterization is set by the calibration of Krussel and Smith (1998) for a US recession.
 % If you change parameters, type "par.<parameter> =" and then "setup" before
 % you call the function. Do not change beta or sigma!
@@ -45,13 +44,13 @@ for i=1:2
             U.one.extrap(t-ceil(T/2),sim.one.e(t,:)==2) = interp1(grid.one.k, U.one.lifetime(2,:), sim.one.k(t,sim.one.e(t,:)==2), 'linear', 'extrap');
         end
     elseif i==2 
-        for ii=1:size(mu,2) 
+        for ii=7%:size(mu,2) 
             tic
             iteration = ii
             par.mu = mu(ii);
             par.PI_UE = PI_UE_grid(ii);
-            method.HH = 'FPend'; % Depending on the mu, you might have to change it to 'FP' or 'FPend' to converge
-            method.agg = 'bisection'; % Depending on the mu, you might have to change it to 'bisection' or 'bisectio' to converge
+            %method.HH = 'FPend'; % Depending on the mu, you might have to change it to 'FP' or 'FPend' to converge
+            %method.agg = 'bisection'; % Depending on the mu, you might have to change it to 'bisection' or 'bisectio' to converge
             setup % refresh setup for new parameter
             [ k.two, c.two, K.two, sim.two, store.two, mat.two, grid.two ] = aiyagari_solver( par, func, method );
             U.two.guess = func.U(c.two.guess);

### 2017-02-23 Paper/Paper_Eric.tex
Added a first version of the introduction.

@@
 (cite some guys)
+
+In the following paper I will depart from the strong assumption of an exogenous job-finding probability, still using the baseline model.
+Based on the results of an empirical estimation of the relationship between changes in the unemployment rate and the job-finding probability I will let the latter fluctuate with the policy changes.
+I then show that this may completely change the outcome of the welfare analysis and therefore may have strong policy implications.
+It may not be sufficient to raise unemployment benefits without undertaking measures to reduce job-finding frictions, such as providing incentives and information to improve the transition from unemployment to employment.
+
+I will start by discussing the model then go on by describing how I conducted the welfare analysis.
+In the thrid part I present my results after a brief summary of the results presented during our presentation - the baseline case with exogenous transition probabilities.
+Finally, I conclude with a critical discussion.
 

### 2017-02-24 Paper/Paper_Eric.tex
Added discussion of baseline summary, improved calibration discussion and introduction of analysis part - mentioning the importance of analyzing welfare implications for both groups (u,ue)

@@
 Furthermore, the unemployment rate, which only depends on the different transition probabilities is so too.
-In other words, changes of the level unemployment insurance do not affect the unemployment rate.
+In other words, changes of the level of unemployment insurance do not affect the unemployment rate.
 This strongly contradicts empirical literature.\footnote{See \citep{decker} for a review.} The main argument being that higher unemployment benefits will decrease incentives for the workers to look for jobs.
@@
 
-I will start by discussing the model then go on by describing how I conducted the welfare analysis.
-In the thrid part I present my results after a brief summary of the results presented during our presentation - the baseline case with exogenous transition probabilities.
-Finally, I conclude with a critical discussion.
+Sections 1 and 2 discuss the model and the welfare analysis, respectively.
+In section 3 a brief summary of the results presented in class is followed by the experiment, which takes changes in the job-finding probability into account.
+Finally, section 5 concludes.
 
@@
 
-For our presentation we have taken two different forms of measurement into account - Consumption equivalent and Cash equivalent.
+For our presentation we have considered two different forms of welfare measurements - the Consumption equivalent and the Cash equivalent.
 I will here only discuss the Cash Equivalent.
@@
 
-In the following section I will analyse the importance of considering disincentive and incentive effects when considering changes in the unemployment benefits.
-Within the model described above and built de foundation for our results presented in class, the transition probabilities and the unemployment rate are exogenously determined.
-We therefore abstracted from such incentive effects.
-In the following experiment I will loosen this strong assumption and analyze the implications for the welfare analysis.
-
-After I introduce the Calibration, I proceed with a short summary of the results obtained in the baseline case and then proceed with a more detailed discussion of the case with an endogenous job-finding probability.
+In the following section I will analyse the importance of considering job-search effects when considering changes in the unemployment benefits.
+How does the welfare analysis change when taking into account that the unemployment duration rises in the benefit level?
+\\
+In order to provide a more detailed welfare analysis, I will look at both the employed and the unemployed when I compare the two cases.
+Although society on average may clearly favour one particular outcome, it may still be reasonable to implement a certain policy to help the more vulnerable to the detriment of the majority.
+Typically, the unemployed benefit relatively more from higher benefits than the employed.
+The latter being in the larger majority, thus leads to the result being biased towards them.
+\\ \\
+After I introduce the Calibration, I proceed with a short summary of the results obtained in the baseline case, which corresponds to the results discussed in class.
+I then conduct an experiment on the basis of empirical results, which show that an increase in the replacement rate leads to an increase in the unemployment duration.
+Using this relationship I will recalculate the welfare effects, letting the job-finding probability fluctuate with the benefit level.
+The second welfare analysis is then compared to the baseline case.
 
@@
 
-I will use the KrusellandSmith calibration, which founded the basis of our analysis for the presentation.
-However, since I am not considering aggregate risk, I will use the job-finding probability of 0.4\footnote{For the presentation we took $\pi_{ue}=0.35$.
-Note that the results for the welfare analysis in the baseline case do not change.See appendix 1}, which corresponds to an average unemployment duration of 2.5 quarters or 32.5 weeks.
-Note that this a rather high estimate of unemployment duration.\footnote{\cite{mukoyama} makes a calibration for the post 1980 US economy, has a job-finding probability of 0.26 corresponding to 17 weeks of unemployment, thus providing a better match for the real data.}
-Other variables are, a discount factor $\beta = 0.99$, productivity $z = 1$, $\alpha = 0.36$, depreciation rate $\theta = 0.025$, the baseline employment $rate l=0.9$, the baseline replacement rate $\mu = 0.15$.
+The calibration used here follows \cite{DenHaan20101} is the same as in the presentation, with the small difference, that the transition matrix corresponds to the case with no aggregate risk.
+The job-finding probability $\pi_{ue}$ therefore takes is slightly higher and takes on the value 0.4 instead of 0.35, which would correspond to the case of a recession when including aggregate risk.\footnote{Since we were also considering aggregate risk in our presentation, we had to chose between the recession and boom state for the Aiyagari calibration and chose the latter.
+Note, however, that this has no impact on the qualitative result of the welfare analysis.} The calibration is based on quarterly data matching microeconomic data or long-run model considerations.
+A job-finding probability of 0.4, thus, corresponds to an average unemployment duration of 2.5 quarters or 32.5 weeks.
+\footnote{Note that here we overestimate the average unemployment duration, since agents remain unemployed for at least one quarter.E.g.
+\cite{mukoyama} uses a $\pi_{ue}$ leading to an average duration of 17 weeks, which corresponds to post US 1980 economy data.} The discount factor is set at $\beta = 0.99$, productivity at $z = 1$, the capital share at $\alpha = 0.36$, and the depreciation rate $\delta = 0.025$.
+Finally, the baseline unemployment rate corresponds to  $1- l=0.1$ and the baseline replacement rate is $\mu = 0.15$.
 
@@
 
-When we conducted our prior welfare analysis we found that different groups in society want different policies - namely, the unemployed would prefer to change to higher unemployment benefits and the employed would prefer a change to a less distributive system.
+When we conducted our prior welfare analysis we found that different groups in society want different policies - namely, the unemployed would prefer to change to higher unemployment benefits and the employed would prefer a change to a less redistributive system.
 Fruthermore, we also found that generally agents do not want full unemployment insurance, although this would clearly eliminate idiosyncratic risk.
@@
 \end{figure}
+
+As benefits increase taxes rise to meet the higher demand.
+Moreover, higher insurance decreases idiosyncratic risk and thus, precautionary savings decrease.
+This in turn reduces aggregate capital leading to an increase in the return rate on capital and a decrease in wages.
+The employed, thus, experience a sharp decrease in their net-wage, but profit more from higher return rates on capital.
+The first clearly dominates.\footnote{ (mukoymama working paper.shows that welfare effects are mainly determined by the redistributional effects of higher taxes and higher benefits.
+He, however, considers lump-sum taxes and therefore cannot show a different effect for unemployed and employed.} Consequentially the employed prefer a reduction in benefits compared to the baseline level.
+Contrary to the employed, the unemployed receive benefits and are not directly harmed by the changes in the taxes and wages, however, also profitting from an increase in the return-rates. 
+Therefore, they do prefer an increase in benefits. 
+Corner solutions (i.e.
+0 benefit or the full-insurance case) are both not prefered by either group.
+Note that taxes also affect the future income of the unemployed, since they have a chance to be employed with a certain probability, this thus reduces future income.
+It works the same way for the employed the other way around.
 

### 2017-02-25 Paper/Paper_Eric.tex
version2

@@
 Sections 1 and 2 discuss the model and the welfare analysis, respectively.
-In section 3 a brief summary of the results presented in class is followed by the experiment, which takes changes in the job-finding probability into account.
+In section 3 a brief summary of the results presented in class is followed by the analysis, which takes changes in the job-finding probability into account.
 Finally, section 5 concludes.
@@
 The setup is a basic \cite{aiyagari} model.
+The key component of this model is that agents are subject to uninsurable idiosyncratic risk, which hinders their ability to smooth consumption over time.
+This risk manifests itself in form of a potential income shock agents may experience in each period.
+In order to insure themselves against such risk, agents accumulate precautionary savings in order to build a buffer for potential future income drops.
+\\
+In contrast to the representative agent model, this mechanism generates a heterogeneous distribution of agents, with different asset levels and different employment status.
+The heterogeneity opens the door for a number of questions, which remain salient to its representative counterpart.
+Most importantly, it allows to look at how macroeconomic policy may affect different groups in distinct ways - A policy change may for example be beneficial for the unemployed, while it is harmful for the employed.
+Moreover, the feature of incomplete insurance, enables us to look at insurance policies.
+The combination of these features, thus enables us to examine the welfare implications of changes in the unemployment benefits.\\
+The following following paragraphs describe the model in a more detailed manner.
 
@@
 
-There is a continuum of ex-ante identical infinitely-lived consumers with population 1. Consumers maximize the discounted lifetime utility: 
+There is a continuum of ex-ante identical (all consumers face the same preferences) infinitely-lived consumers, whereby the population is normalized to 1.
+In each period consumers choose $ c_{t}$, consumption at time t, and the asset level next period, $k_{i,t+1}$, to maximize the expected discounted lifetime utility:
 \[ 
- max_{\{{ c_{i,t}, k_{i,t+1} }\}_{t = 0}^{\infty}} {\mathbb{E}} \sum_{i=0}^{\infty} \beta^{t}  u(c_{i,t}) 
+ max_{\{{ c_{i,t}, k_{i,t+1} }\}_{t = 0}^{\infty}} {\mathbb{E}} \sum_{i=0}^{\infty} \beta^{t}  u(c_{i,t}), 
  \]
 
-where $\beta \in (0,1)$ is the discount factor, $ c_{t}$ is consumption at time t and $\mathbb{E[.]}$ is the expectation at time 0.
+where $\beta \in (0,1)$ is the discount factor and $\mathbb{E[\cdot]}$ is the expectation at time 0.
+In each period, the individual expenditure is constrained by the period income.
+Consumers thus face to following budget constraint:
+  \begin{equation}
+  \label{eq:budconstraint}
+  c_{i,t} + k_{i,t+1} = (1 + r_{t} - \delta) k_{i,t} + w_{t} (1 - \tau_{t})  e_{i,t} + \mu w_{t} (1 - e_{i,t}).
+ \end{equation}
 
-Consumers are subject to uninsurable idiosyncratic risk.
-In each period they can either be employed $(e_{i,t}=1)$ or unemployed $(e_{i,t}=0)$ .
-This process is governed by an exogenous transition matrix:
+$r_{t}$ is the interest rate at time t, $\delta$ is the depreciation rate, $w_{t}(1-\tau_{t})$ is the after-tax wage at time t and $e_{i,t}$ is a dummy variable for the employment status - $e_{i,t}=1$ being employed at time t and $ e_{i,t}=0$ unemployed, respectively.
+Unemployed consumers receive benefits in form of a replacement rate,$\mu$.
+Finally, consumers are constrained in their borrowing:
+
+   \begin{equation}
+  \label{eq:borconstraint}
+   k_{i,t + 1} \geq \bar{k}.
+ 	 \end{equation}
+
+$\bar{k}$ denotes the minimum amount of capital consumers are required to hold at each point in time.
+
+The employment shocks are governed by an exogenous transition matrix: 
 \[ \Pi = \begin{bmatrix}
@@
 
-where $\pi_{UE}$ is the probability to find a job next period and $pi_{EU}$ is the layoff probability.
-
-Consumers are allowed to interact on the capital market and accumulate one type of asset: $a_{t}$ to smooth consumption over time and insure for rainy days.
-They are therefore subject to the following budget constraint at each point in time:
-  \[ 
-  c_{i,t} + k_{i,t+1} = (1 + r_{t} - \delta) k_{i,t} + w_{t} (1 - \tau_{t})  e_{i,t} + \mu w_{t} (1 - e_{i,t})
-  \]
- where $r_{t}$ is the interest rate at time t, $\delta$ is the depreciation rate, $w_{t}(1-\tau_{t})$ is the after-tax wage at time t and $\mu_{t}$ are the unemployment benefits, which represent a replacement rate i.e.
-the fraction of the wage unemployed receive.
-
-Finally, consumers are constrained in their borrowing, $k_{min}$ denotes the minimum amount of capital consumers are required to hold at each point in time: 
-   \[
-   k_{i,t + 1} \geq \bar{k}
- 	\]
+where $\pi_{UE}$ is the probability to find a job next period and $\pi_{EU}$ is the layoff probability.
 
@@
 
-Factor prices are obtained by taking the FOC's with respect to the aggregate capital stock and the aggregate labour, respectively: 
+Factor prices are obtained by taking the FOC's with respect to the aggregate capital stock and the aggregate labor, respectively: 
 \[
@@
 
-\subsection{The governement}
+\subsection{The government}
 
-The governement runs a balanced budget:
-\[
+The government runs a balanced budget:
+\begin{equation}
+  \label{eq:balancedbudget}
 \tau_{t}=\mu\frac{1-L_{t}}{L_{t}}
-\]
+\end{equation}
 
 \subsection{General Equilibrium}
+
+	   \begin{equation}
+  \label{eq:ssemployment}
+   L = \frac{\pi_{UE}}{\pi_{UE}+\pi_{EU}}
+ 	 \end{equation}
 
@@
 
-Finally, the aggregated capital and labour must be consistent with aggregate capital and labour used to obtain the factor prices: 
+Finally, the aggregated capital and labor must be consistent with aggregate capital and labor used to obtain the factor prices: 
 \[ \sum_{i}k_{t+1}(e_{i,t},k_{i,t},s_{t})=K_{t+1}(s_{t}), \ \ \ \sum_{i}e_{i,t}=L_{t} 
@@
 Secondly,we need take transitions into account.
-It may be the case that during the transition phase from one steady state to the other, agents loose eventough in the end they are in a preferred steady state and therefore do not prefer the policy change taking the transition into account.
+It may be the case that during the transition phase from one steady state to the other, agents loose even tough in the end they are in a preferred steady state and therefore do not prefer the policy change taking the transition into account.
 
@@
 
-The Cash Equivalent tells you how much cash, as in units of wealth, I have to give to (or take away from) the agent in the first economy, in order for him to be indifferent between the two economies - The two being identical with the exeption of two different benefit policies.
-$U^{1}$ being the livetime utility in the baseline economy with benefit policy one and $U^{2}$ being the livetime utility in the economy with the adjusted policy.
+The Cash Equivalent tells you how much cash, as in units of wealth, I have to give to (or take away from) the agent in the first economy, in order for him to be indifferent between the two economies - The two being identical with the exception of two different benefit policies.
+$U^{1}$ being the lifetime utility in the baseline economy with benefit policy one and $U^{2}$ being the lifetime utility in the economy with the adjusted policy.
 Formally:
@@
 
-In the following section I will analyse the importance of considering job-search effects when considering changes in the unemployment benefits.
+In the following section I will analyze the importance of considering job-search effects when considering changes in the unemployment benefits.
 How does the welfare analysis change when taking into account that the unemployment duration rises in the benefit level?
@@
 In order to provide a more detailed welfare analysis, I will look at both the employed and the unemployed when I compare the two cases.
-Although society on average may clearly favour one particular outcome, it may still be reasonable to implement a certain policy to help the more vulnerable to the detriment of the majority.
+Although society on average may clearly favor one particular outcome, it may still be reasonable to implement a certain policy to help the more vulnerable to the detriment of the majority.
 Typically, the unemployed benefit relatively more from higher benefits than the employed.
@@
 
-When we conducted our prior welfare analysis we found that different groups in society want different policies - namely, the unemployed would prefer to change to higher unemployment benefits and the employed would prefer a change to a less redistributive system.
-Fruthermore, we also found that generally agents do not want full unemployment insurance, although this would clearly eliminate idiosyncratic risk.
-Figure 1 illustrates this well:
+When we conducted our prior welfare analysis we found that different groups in society want different policies - namely, the unemployed would prefer to change to higher unemployment benefits and the employed would prefer a change to a less re-distributive system.
+Furthermore, we also found that generally agents do not want full unemployment insurance, although this would clearly eliminate idiosyncratic risk.
+\ref{baseline_ue_vs_e} illustrates this well.
 
@@
 \centering
-\includegraphics[scale=.7]{Cash_equivalent_baseline}  % width legt Breite der Graphik fest
+\includegraphics[scale=.5]{Cash_equivalent_baseline}  % width legt Breite der Graphik fest
 
@@
 The employed, thus, experience a sharp decrease in their net-wage, but profit more from higher return rates on capital.
-The first clearly dominates.\footnote{ (mukoymama working paper.shows that welfare effects are mainly determined by the redistributional effects of higher taxes and higher benefits.
+The first clearly dominates.\footnote{ (mukoymama working paper.shows that welfare effects are mainly determined by the re-distributional effects of higher taxes and higher benefits.
 He, however, considers lump-sum taxes and therefore cannot show a different effect for unemployed and employed.} Consequentially the employed prefer a reduction in benefits compared to the baseline level.
-Contrary to the employed, the unemployed receive benefits and are not directly harmed by the changes in the taxes and wages, however, also profitting from an increase in the return-rates. 
+Contrary to the employed, the unemployed receive benefits and are not directly harmed by the changes in the taxes and wages.
+Furthermore, the richer unemployed, who were able to accumulate savings, also profit from an increase in the return-rates.
 Therefore, they do prefer an increase in benefits. 
 Corner solutions (i.e.
-0 benefit or the full-insurance case) are both not prefered by either group.
+0 benefit or the full-insurance case) are both not preferred by either group.
 Note that taxes also affect the future income of the unemployed, since they have a chance to be employed with a certain probability, this thus reduces future income.
-It works the same way for the employed the other way around.
+The same is true for higher benefits in the case of the employed.\footnote{Net labor income equals unemployment benefits at a replacement rate of 0.9, higher benefits thus would lead to unemployed being better off compared to the employed, which is rather unrealistic.}
 
-\subsection{Adapting the transition probability}
+\subsection{Endogenizing the job-finding probability}
 
@@
 
-I base my calibration on the empirical literature.
-\citep{decker} summarizes the empirical literature, which considers disincentive and incentive effects with respect to changes in unemployment benefits using different approaches and as well as a variety of US-samples.
-He concludes, that a change of 10 percent-points in benefits leads to a prolongement of the average unemployment duration of 0.5 to 1.5 weeks.
-Thus, I let the job-finding probability such that an 10 percent-point increase of the benefits leads to a prolongement of the average unemployment period of a week.\footnote{Appendix 2 provides a detailed conversion table.}
+I base my calibration on the empirical results.
+\citep{decker} summarizes the empirical literature, which considers disincentive and incentive effects with respect to changes in unemployment benefits using different approaches as well as a variety of US-samples.
+He concludes, that a change of 10 percent-points in benefits leads to an extension of the average unemployment duration of 0.5 to 1.5 weeks.
+Thus, I let the job-finding probability such that an 10 percent-point increase of the benefits leads to a prolongation of the average unemployment period of a week.
+The new job-finding probability is then obtained by the following function:
+\begin{equation}
+	\pi_{ue}=\frac{1}{x} \nonumber
+\end{equation}
+where
+
+\begin{equation}
+	x=\cfrac{32.5+\left(\cfrac{\Delta PP \mu}{10}\right)}{13} \nonumber
+\end{equation}
+is the average unemployment duration in quarters. \\
+
+$32.5$ is the baseline unemployment duration $\Delta PP \mu$ is the percentage point deviation of the unemployment benefits and $\frac{\Delta PP \mu}{10}$ the change in unemployment duration, expressed in weeks.\footnote{Appendix 2 provides a detailed conversion table.} \\
+From equation \eqref{eq:ssemployment} follows that the unemployment rate increases as the unemployment duration increases following an increase in unemployment benefits.
+At the lowest benefit level considered the unemployment rate is at 9.6 percent and the highest benefit the unemployment rate is at 11 percent, with a baseline case of 10 percent.
+The impact of a change in the replacement rate on the unemployment rate is thus rather small.
 
 \subsection{Results}
+
+Figure 2 shows displays the mean and median Cash Equivalent for the unemployed and the employed.
+It clearly shows that all agents prefer lower benefits.
+While the optimum for the employed lies at 0 (or are negative benefits) the unemployed prefer some benefits, but lower than the baseline.
+
 \begin{figure}
@@
 \centering
-\includegraphics[scale=.7]{cash_equivalent(ue_vs_e)}  % width legt Breite der Graphik fest
+\includegraphics[scale=.5]{cash_equivalent(ue_vs_e)}  % width legt Breite der Graphik fest
 
@@
 
-Figure 2 shows displays the mean and median Cash Equivalent for the unemployed and the employed.
-It clearly shows that all agents prefer lower benefits.
-While the optimum for the employed lies at 0 (or are negative benefits) the unemployed prefer some benefits, but lower than the baseline.
 Compared to the previous results all agents prefer lower benefits.\footnote{\cite{KrusellMukoyamaSahin} find similar results, when comparing a standard BHA model with a model including endogenous unemployment.}
@@
 There are therefore less employed who have to pay higher benefits to more unemployed.
-This raises taxes to a higher extent than in the previous case and thus make the employed worse off in the case of a raise in the benefits.
+From equation \eqref{eq:balancedbudget} it follows that taxes will raise to a higher extent than in the previous case since both the unemployment rate and the benefits rise.
+Thus, the employed will be worse off compared to the baseline case.
 This amplifying effect works in both directions.
 As employment increases with lower benefits, the relative taxes decrease faster than in the baseline case and thus, the lowest possible benefits are preferred by the employed.
-While the employed are not directly affected by a change in the transition probabilites, the unemployed's risk of receiving low income increases with an increase in the benefits.
+While the employed are not directly affected by a change in the transition probabilities, the unemployed's risk of receiving low income increases with an increase in the benefits.
 Thus their expected future income decreases as they face larger unemployment spells on average.
-In the present case, this effect seems to be strong enough for the unemployed to prefer to forego some amount of benefits and in turn profit from higher future income prospects on average, as the proability to being employed next period rises.
+In the present case, this effect seems to be strong enough for the unemployed to prefer to forego some amount of benefits and in turn profit from higher future income prospects on average, as the probability to being employed next period rises.
 This effect, however, is not strong enough to completely overcome the benefits of a replacement rate and thus in the present case, the unemployed would prefer a $\mu$ of around 0.7.
-Which also is pareto-optimal, as both, the mean and the median, are maximal at this level of benefits.
+Which also is pareto-optimal, as both, the mean and the median, are maximal at this benefit level.
 
@@
 Clearly, starting from the baseline calibration describing the US economy, it may make sense to propose a higher benefit-scheme in the first case (the foundation of the argument being, unemployed are better of with higher benefits).
-However, taking transitions into account, this line of argumentation clearly fails.
+However, taking job-search rigidities into account, this line of argumentation clearly fails.
+\\
+-> mention that the change in unemployment duration considered is rather small!!! makes result even more astonishing! 
+\\
 Finally, a policy-scheme simply relying on unemployment benefits is limited.
-It may be optimal to combine unemployment benefits with reintegration measures facilitating job search and inducing the unemployed to reintegrate themselfs in the job market.
-Although, the results seem to be similar to those of others, one has to be aware that exogenously determine the transition probability, based on a linear relationship between unemployment duration and unemployment benefits may be limited.
+It may be optimal to combine unemployment benefits with reintegration measures facilitating job search and inducing the unemployed to reintegrate themselves in the job market.
+Although, the results seem to be similar to those of others, one has to be aware that endogenously determine the transition probability, based on a linear relationship between unemployment duration and unemployment benefits may be limited.
 First of all this relationship may not be linear (cite some guy).

### 2017-02-25 welfare_analysis.m

@@ -44,7 +44,7 @@ for i=1:2
             U.one.extrap(t-ceil(T/2),sim.one.e(t,:)==2) = interp1(grid.one.k, U.one.lifetime(2,:), sim.one.k(t,sim.one.e(t,:)==2), 'linear', 'extrap');
         end
     elseif i==2 
-        for ii=7%:size(mu,2) 
+        for ii=1%:size(mu,2) 
             tic
             iteration = ii
             par.mu = mu(ii);

### 2017-02-26 Paper/Paper_Eric.tex
Complete_first_version.

@@
     \emph{53113 Bonn}\\
-   \emph{Stud Nr.: 2849851}\\
+   \emph{Student Number: 2849851}\\
  \emph{M.Sc. Economics}\\
@@
 
-% \tableofcontents   %fuegt Automatisch ein Inhaltsverzeichnis ein
+\tableofcontents   %fuegt Automatisch ein Inhaltsverzeichnis ein
 % 
@@
 \setcounter{page}{1}        % Ruecksetzen des Seitenzahlzaehlers auf 1
-
-\section{\"Uberschrift}
-\label{Kapitel1}
-
-\subsection{Unter\"Uberschrift}
-
-\subsubsection*{UnterUnter\"Uberschrift}
-
-Hier steht mal ein Text. Eine M\"oglichkeit des Zitierens ist, direkt
-im Text die Quelle anzugeben \citep[see][pp.225-369]{key1}.
-Andererseits schreiben \cite{key2}, dass man auch so zitieren kann.
-
-In der Matheumgebung kann der oben (im Latex-Quellcode) genannte Shortcut verwendet
-werden, um aus einem normalen $\beta$ ein fettes $\bs \beta$ zu
-machen. Wichtige Gleichungen, die nochmal verwendet werden, sollten nummeriert werden, z.B.
-\begin{equation}
-\label{eq:ols}
-   b = (x'x)x'y \;.
-\end{equation}
-
-Nebens\"achlicheres, auf das man sich nicht mehr bezieht, bleibt unnummeriert, also 
-\begin{equation*}
-   a = 1\;.
-\end{equation*}
-Nun kann man direkt auf die erste Gleichung als Gleichung~\eqref{eq:ols} verweisen mittels des zugewiesenen labels.
-In gleicher Weise kann man auf die Graphik~\ref{fig:ersteGraphik} bzw.
-Graphik~\ref{fig:andereGraphik} verweisen.
-Die Tilde zwischen \glqq Graphik\grqq{} und \glqq \verb|\ref{fig:andereGraphik}|\grqq{} verhindert, dass bei Zeilenumbr\"uchen die Zahl als erstes alleine in die neue Zeile rutscht.
-Ganz analog f\"ur die Tabelle~\ref{tab:Tabelle}.
+\pagebreak
 
@@
 These shocks are assumed to be independent of the policy itself.
-Furthermore, the unemployment rate, which only depends on the different transition probabilities is so too.
+Furthermore, the unemployment rate, which only depends on the different transition probabilities, is so too.
 In other words, changes of the level of unemployment insurance do not affect the unemployment rate.
 This strongly contradicts empirical literature.\footnote{See \citep{decker} for a review.} The main argument being that higher unemployment benefits will decrease incentives for the workers to look for jobs.
-Furthermore, there is a great deal of theoretical literature, consisting of search-match and moral hazard models suggesting the same.
-(cite some guys)
+Moreover there is a vast theoretical literature concerned with endogenous job creation and job destruction processes.
+\footnote{E.g.
+\cite{diamond1981mobility} or \cite{mortensen1994job}} \citep{KrusellMukoyamaSahin} integrate such mechanisms into an Aiyagari-type model and show that the results from a welfare analysis concerning changes in unemployment benefits substantially vary from those obtained in a simple Aiyagari framework.
 
-In the following paper I will depart from the strong assumption of an exogenous job-finding probability, still using the baseline model.
+In the following paper I will conduct an experiment and depart from the strong assumption of an exogenous job-finding probability, still using the baseline model.
 Based on the results of an empirical estimation of the relationship between changes in the unemployment rate and the job-finding probability I will let the latter fluctuate with the policy changes.
@@
 
-\subsection{Consumer's Problem}
+\subsection{Setup}
 
+\subsubsection*{Consumer's Problem}
 There is a continuum of ex-ante identical (all consumers face the same preferences) infinitely-lived consumers, whereby the population is normalized to 1.
@@
 Finally, consumers are constrained in their borrowing:
-
    \begin{equation}
@@
 
-\subsection{Firm's Problem}
+\subsubsection*{Firm's Problem}
 
-The representative firm maximizes profits 
+The production side of the economy is competitive and modeled as a representative firm maximizing profits. 
 \[ \max_{\substack{K_{t},L_{t}}}F_{t}(K_{t},L_{t})-r_{t}K_{t}-w_{t}L_{t}
@@
 
-Factor prices are obtained by taking the FOC's with respect to the aggregate capital stock and the aggregate labor, respectively: 
-\[
-r_{t} = \frac{\mathrm d F_{t}(K_{t},L_{t})}{\mathrm d K} = \alpha z (\tfrac{L_{t}}{K_{t}})^{1-\alpha} \]
-\[
-w_{t} = \frac{\mathrm d F_{t}(K_{t},L_{t})}{\mathrm d L} =(1-\alpha)z (\tfrac{K_{t}}{L_{t}})^{\alpha}
-\]
+\subsubsection*{The government}
 
-\subsection{The government}
-
-The government runs a balanced budget:
+The government runs a balanced budget and therefore the income taxes of the employed are always equal to the benefits received by the unemployed: 
 \begin{equation}
@@
 
-	   \begin{equation}
-  \label{eq:ssemployment}
-   L = \frac{\pi_{UE}}{\pi_{UE}+\pi_{EU}}
- 	 \end{equation}
+Factor prices are obtained by taking the FOC's with respect to the aggregate capital stock and the aggregate labor, respectively: 
+\[
+r_{t} = \frac{\mathrm d F_{t}(K_{t},L_{t})}{\mathrm d K} 
+\]
+\[
+w_{t} = \frac{\mathrm d F_{t}(K_{t},L_{t})}{\mathrm d L} 
+\]
 
-The euler equation is maximizing the consumer's problem
-\[ 
-c_{i,t}^{- \sigma} \geq \beta (1+r -\delta){\mathbb{E}[c_{i,t+1}^{- \sigma}}]
-\]
 The households take (current and future) factor prices $r_{t} and w_{t}$ as given.
-Their policy functions satisfy the first-order conditions and depend on the employment status, wealth and the aggregate state:
+Their optimal decision rules satisfy the first-order conditions and depend on their employment status, individual wealth and the aggregate state:
 \[ c_{t}(e_{t},k_{t},s_{t}), k_{t+1}(e_{t},k_{t},s_{t})
@@
 
-Finally, the aggregated capital and labor must be consistent with aggregate capital and labor used to obtain the factor prices: 
+Finally, the aggregated capital and employment status obtained from the individual's problem must be consistent with the aggregates used to obtain the factor prices: 
 \[ \sum_{i}k_{t+1}(e_{i,t},k_{i,t},s_{t})=K_{t+1}(s_{t}), \ \ \ \sum_{i}e_{i,t}=L_{t} 
@@
 \section{Welfare analysis}
-We want to compare the utility level of the same agent before and after the policy change.
-There are two challenges to overcome.
-Firstly, utility is a purely ordinal measure and therefore not quantifiable.
+The goal is to determine, whether agents prefer a policy change to the status quo.
+We therefore want to compare the utility level of the same agent before and after the policy change.
+There are two challenges to overcome.Firstly, utility is a purely ordinal measure and therefore not quantifiable.
 Secondly,we need take transitions into account.
-It may be the case that during the transition phase from one steady state to the other, agents loose even tough in the end they are in a preferred steady state and therefore do not prefer the policy change taking the transition into account.
+It may be the case that in the short run, during the transition phase from one steady state to another, agents are worse off, even tough they end up in a preferred steady state.
+Only comparing steady states is therefore insufficient - the losses endured in the short run may be so devastating, that the agent does not prefer a policy change after all.
 
@@
 
-The Cash Equivalent tells you how much cash, as in units of wealth, I have to give to (or take away from) the agent in the first economy, in order for him to be indifferent between the two economies - The two being identical with the exception of two different benefit policies.
+To look at the welfare effect it is easiest to think of two different economies.
+Economy one is the baseline case and economy two describes the state of the economy after the policy change, other than for the different levels of benefits, these economies are driven by the same underlying parameters.\\
+The Cash Equivalent tells you how much cash, as in units of wealth, I have to give to (or take away from) the agent in the first economy, in order for him to be indifferent between the two economies.
 $U^{1}$ being the lifetime utility in the baseline economy with benefit policy one and $U^{2}$ being the lifetime utility in the economy with the adjusted policy.
@@
 
-One has to consider the transitions.
-Approximation used by \cite{KrusellMukoyamaSahin}.
-Instead of calculating full transitions I compare different steady states, placing the agents along with their capital holding and their employment state into the new economy and I then compare the two lifetime utilities.
+In order to incorporate the transition, we follow \cite{KrusellMukoyamaSahin}, who calculate an average of the full transition abstracting from aggregate transitions.\footnote{For an implementation of the full transition see \citep{mukoyama}} Agents from the first economy are placed into the second economy along with their capital holdings $k$ and their employment status $e$ from the baseline economy.
+$U^{1}(e,k)$ is then compared to $U^{2}(e,k)$.
 
@@
 In order to provide a more detailed welfare analysis, I will look at both the employed and the unemployed when I compare the two cases.
-Although society on average may clearly favor one particular outcome, it may still be reasonable to implement a certain policy to help the more vulnerable to the detriment of the majority.
-Typically, the unemployed benefit relatively more from higher benefits than the employed.
-The latter being in the larger majority, thus leads to the result being biased towards them.
+Even if society on average clearly favors one particular outcome, it may still not be unreasonable to implement a contradictory policy to help the more vulnerable to the detriment of the majority.
+Typically, the unemployed benefit relatively more from higher replacement rates than the employed.
+The latter being in the larger majority, thus leads to the averaged result being biased towards them.
 \\ \\
@@
 
-The calibration used here follows \cite{DenHaan20101} is the same as in the presentation, with the small difference, that the transition matrix corresponds to the case with no aggregate risk.
+The calibration used here follows \cite{DenHaan20101} and is the same as in the presentation, with the small difference, that the transition matrix corresponds to the case with no aggregate risk.
 The job-finding probability $\pi_{ue}$ therefore takes is slightly higher and takes on the value 0.4 instead of 0.35, which would correspond to the case of a recession when including aggregate risk.\footnote{Since we were also considering aggregate risk in our presentation, we had to chose between the recession and boom state for the Aiyagari calibration and chose the latter.
@@
 Finally, the baseline unemployment rate corresponds to  $1- l=0.1$ and the baseline replacement rate is $\mu = 0.15$.
+Finally, as in the calibration used for the presentation, I use a risk-aversion parameter, $\sigma$, of 2 instead of 1(as in the original calibration).
 
@@
 The employed, thus, experience a sharp decrease in their net-wage, but profit more from higher return rates on capital.
-The first clearly dominates.\footnote{ (mukoymama working paper.shows that welfare effects are mainly determined by the re-distributional effects of higher taxes and higher benefits.
+The first clearly dominates.\footnote{ mukoymama working paper.shows that welfare effects are mainly determined by the re-distributional effects of higher taxes and higher benefits.
 He, however, considers lump-sum taxes and therefore cannot show a different effect for unemployed and employed.} Consequentially the employed prefer a reduction in benefits compared to the baseline level.
@@
 $32.5$ is the baseline unemployment duration $\Delta PP \mu$ is the percentage point deviation of the unemployment benefits and $\frac{\Delta PP \mu}{10}$ the change in unemployment duration, expressed in weeks.\footnote{Appendix 2 provides a detailed conversion table.} \\
-From equation \eqref{eq:ssemployment} follows that the unemployment rate increases as the unemployment duration increases following an increase in unemployment benefits.
-At the lowest benefit level considered the unemployment rate is at 9.6 percent and the highest benefit the unemployment rate is at 11 percent, with a baseline case of 10 percent.
+Note that in steady state the following equality must hold: $ L = \frac{\pi_{UE}}{\pi_{UE}+\pi_{EU}}$.
+Hence, the unemployment rate increases as the unemployment duration increases following a rise in the benefits.
+At the lowest benefit level considered, the unemployment rate is at 9.6 percent and the highest benefit the unemployment rate is at 11 percent, with a baseline case of 10 percent.
 The impact of a change in the replacement rate on the unemployment rate is thus rather small.
 
-\subsection{Results}
+\subsection{Results with endogenous transitions}
 
@@
 
-Compared to the previous results all agents prefer lower benefits.\footnote{\cite{KrusellMukoyamaSahin} find similar results, when comparing a standard BHA model with a model including endogenous unemployment.}
+Compared to the previous results all agents prefer lower benefits.\footnote{\cite{KrusellMukoyamaSahin} find similar results, when comparing a standard Bewley-Huggett-Aiyagari model with a model including endogenous unemployment.}
 As benefits increase the unemployment rate rises.
 There are therefore less employed who have to pay higher benefits to more unemployed.
-From equation \eqref{eq:balancedbudget} it follows that taxes will raise to a higher extent than in the previous case since both the unemployment rate and the benefits rise.
+From equation \eqref{eq:balancedbudget} it follows that taxes will raise to a higher extent than in the previous case since both, the unemployment rate and the benefits rise.
 Thus, the employed will be worse off compared to the baseline case.
@@
 In the present case, this effect seems to be strong enough for the unemployed to prefer to forego some amount of benefits and in turn profit from higher future income prospects on average, as the probability to being employed next period rises.
-This effect, however, is not strong enough to completely overcome the benefits of a replacement rate and thus in the present case, the unemployed would prefer a $\mu$ of around 0.7.
-Which also is pareto-optimal, as both, the mean and the median, are maximal at this benefit level.
+This effect, however, is not strong enough to completely overcome the benefits of a replacement rate and thus in the present case, the unemployed would prefer a $\mu$ of 4 percent.
+Which also is a pareto-improvement compared to the baseline benefits, as both, the mean and the median, are maximal at this benefit level.
 
@@
 However, taking job-search rigidities into account, this line of argumentation clearly fails.
-\\
--> mention that the change in unemployment duration considered is rather small!!! makes result even more astonishing! 
-\\
-Finally, a policy-scheme simply relying on unemployment benefits is limited.
-It may be optimal to combine unemployment benefits with reintegration measures facilitating job search and inducing the unemployed to reintegrate themselves in the job market.
-Although, the results seem to be similar to those of others, one has to be aware that endogenously determine the transition probability, based on a linear relationship between unemployment duration and unemployment benefits may be limited.
-First of all this relationship may not be linear (cite some guy).
-Secondly, higher unemployment benefits may also impact the job-loss probability (cite some guy), although the literature is less clear on that.
-Finally, I have completely abstracted from a bargaining process, which will also affect the firms side and produce further changes in the wage\citep{mukoyama} for an example.
-These changes may potentially further alter the results.\footnote{In this simple setting, prices and therefore also the wage, entirely depend on the aggregates driven by individual savings.}
+What makes this result even more astonishing is the fact that the changes in unemployment duration considered are relatively small.
+As explained above, the baseline calibration sets the unemployment duration rather high.
+Changes in the job-finding probability, thus, tend to be understated in my analysis.
+Taking these points into consideration, the abstraction of job-search rigidities imposed by the Aiyagari model clearly seems to strong, as for the model to provide final answers for the welfare implications of changes in unemployment benefits.
+At best, one has to be very careful with generic conclusions drawn from studies similar to our baseline analysis.
+A further conclusion one may draw from the above experiment, is that a policy-scheme simply relying on unemployment benefits is limited.
+It may be optimal to combine unemployment benefits with reintegration measures facilitating job search and incentive schemes inducing the unemployed to reintegrate themselves in the job market.
+
+One major limitation of my analysis is the calibration.
+As discussed before, the baseline average unemployment duration is rather high.
+Furthermore, the calibration from \cite{DenHaan20101} was mainly calibrated to study aggregate fluctuations.
+Hence, it is not evident that the experiment above would produce the same results with a calibration reflecting empirical data more accurately.
+It would therefore be interesting to conduct the same experiment with a proper calibration, however, this exceeds the scope of this exercise.
 

### 2017-02-26 parameters.m

@@ -1,7 +1,7 @@
 %% Set parameters
 % consumers
 par.beta = 0.99; % discount factor
-par.sigma = 2; % risk aversion
+par.sigma = 3; % risk aversion
 par.mu = 0.15; % replacement rate of unemployed
 par.k_min = 1e-15; % borrowing constraint as share of capital stock
 

### 2017-02-26 welfare_analysis.m

@@ -44,13 +44,13 @@ for i=1:2
             U.one.extrap(t-ceil(T/2),sim.one.e(t,:)==2) = interp1(grid.one.k, U.one.lifetime(2,:), sim.one.k(t,sim.one.e(t,:)==2), 'linear', 'extrap');
         end
     elseif i==2 
-        for ii=1%:size(mu,2) 
+        for ii=11%:size(mu,2) 
             tic
             iteration = ii
             par.mu = mu(ii);
             par.PI_UE = PI_UE_grid(ii);
-            %method.HH = 'FPend'; % Depending on the mu, you might have to change it to 'FP' or 'FPend' to converge
-            %method.agg = 'bisection'; % Depending on the mu, you might have to change it to 'bisection' or 'bisectio' to converge
+            method.HH = 'FP'; % Depending on the mu, you might have to change it to 'FP' or 'FPend' to converge
+            method.agg = 'bisection'; % Depending on the mu, you might have to change it to 'bisection' or 'bisectio' to converge
             setup % refresh setup for new parameter
             [ k.two, c.two, K.two, sim.two, store.two, mat.two, grid.two ] = aiyagari_solver( par, func, method );
             U.two.guess = func.U(c.two.guess);
@@ -94,7 +94,7 @@ for i=1:2
             keep.k.equivalent_employed_mean = k.equivalent_employed_mean;
             keep.k.equivalent_employed_median = k.equivalent_employed_median;
             keep.K = K.two.guess;
-            filename = ['adapting_transitions_2_mu_' num2str(ii) '.mat'];
+            filename = ['adapting_transitions_sigma3_mu_' num2str(ii) '.mat'];
             %filename = ['adapting_transitions_mu_' num2str(ii) '.mat']; %Changing transitions
             %filename = ['baseline_mu_' num2str(ii) '.mat']; %Baseline
             save (filename, '-struct','keep'); % Save the values
